### 2024-01-04 latex/paper.tex
first commit

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}

\linespread{1.5} % You can adjust the factor (e.g., 1.5 for 1.5x spacing)

\title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
\author{Your Name}
\date{}

\begin{document}

\maketitle

\begin{abstract}
In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids. Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions. The investigation covered diverse operational parameters, including heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number, to quantify the convective heat transfer coefficient. These operational parameters were incorporated as inputs into an artificial neural network to model the convective heat transfer coefficient. Evaluation metrics, such as mean square error and correlation coefficient, were computed, revealing the remarkable performance of the neural network in capturing the underlying processes. The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes. The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
\end{abstract}

\section{Introduction}
Improving the efficiency of working fluids in thermo systems enhances their overall performance and minimizes size requirements. Nanofluids, which are suspensions of small percentages (<5 vol.  \%) of various nanoparticles in conventional working fluids, have emerged as an excellent solution to address the thermal challenges in advanced heat transfer systems.

In a study by Pak and Cho on nanofluids consisting of 3 vol.  \% 27 nm titanium dioxide particles in water, a new correlation for turbulent convective heat transfer in dilute nanofluids was reported \cite{ref1}:

\begin{equation}
 \mathbf{Nu} = 0.21 \mathbf{Re}^{0.8} \mathbf{Pr}^{0.5}
\end{equation}

where  \textbf{Nu} is the Nusselt number,  \textbf{Re}  is the Reynolds number, and  \textbf{Pr} is the Prandtl number and $ 6.54 \leq \text{Pr} \leq 12.33, \quad \begin{matrix}
10^4 \leq \text{Re} \leq 10^5
\end{matrix} $

He et al. synthesized stable aqueous 20 nm titanium dioxide nanofluids with different agglomerate sizes and concentrations, revealing an increase in convective heat transfer coefficient with nanoparticle concentration, particularly in turbulent flow regimes \cite{ref2}.

\section{Related Works}

While experimental studies provide valuable insights, more research is needed to model the intricate processes and establish empirical relations between effective parameters. Artificial neural networks (ANNs) have proven effective in modeling various processes. For instance, Santra et al. applied ANN to predict heat transfer in laminar natural convection of copper–water nanofluids, demonstrating accurate predictions within the training data range \cite{ref3}. Fazeli et al. utilized ANN to simulate the heat transfer characteristics of a miniature heat sink cooled by SiO2–water nanofluids, achieving excellent agreement with mathematical simulations \cite{ref4}. Balcilar et al. employed ANNs to determine parameters' effects on the heat transfer coefficient of nanofluids, showing good agreement with experimental data \cite{ref5}.

Papari et al. utilized ANN analysis to estimate the thermal conductivity of nanofluids containing multi-walled carbon nanotubes (MWCNTs) and single-walled carbon nanotubes (SWCNTs), with predicted values in good agreement with literature \cite{ref6}. Hojjat et al. synthesized various nanofluids and proposed neural network models to represent thermal conductivity as a function of temperature, nanoparticle concentration, and the thermal conductivity of nanoparticles \cite{ref7}.

In this paper, we employ neural networks to estimate the forced convective heat transfer coefficient of nanofluids. The study aims to compare the modeling results with experimental data obtained for water and an ethylene glycol/water mixture as the base fluid. Nanofluids containing TiO2 nanoparticles at various concentrations will be tested under different heat flux boundary conditions, flowing upward through a vertical pipe in laminar and turbulent flow regimes.

\section{Experimental Setup}
Spherical titanium dioxide nanoparticles dispersed in distilled water and ethylene glycol/water mixture (60 weight-\% ethylene glycol) were used. Nanoparticles were purchased from Degussa (Germany) with an average diameter of 25 nm. An ultrasonic vibrator (Tecna 6) was used for the preparation of mixed aqueous suspensions. The suspension was sonicated for 4 hours at a frequency of 50-60 kHz with an output power of 138W, at 65ºC, and pH=11 by NaOH solution. Nanofluids containing 0.5\%, 1.0\%, 1.5\% titanium dioxide by volume were obtained using the two-step method. The stability time of nanofluids was observed to be 24 hours without any stabilizer.

The test section in Fig. 1 (experimental apparatus) was a straight copper tube with a length of 120 cm, an inner diameter of 6 mm, and an outer diameter of 8 mm. Two rods of heaters with different AC power in parallel with the tube were used as heaters with a thick thermal isolating layer. Four (K-type) thermocouples were welded on the inner tube wall at 20 cm (Tw1), 50 cm (Tw2), 80 cm (Tw3), and 110 cm (Tw4) from the inlet of the test section. Two further K-type thermocouples were inserted into the flow at 8 cm (Tfin) and 119 cm (Tfout) from the inlet of the test section. After injection of nanofluid into a glass vessel as a fluid reservoir tank, it was circulated toward the test section using a pump (STAR RS 25/6-130). Flow rate was measured by a flow meter, and different flow rates (0.5-5.0 L/min) were obtained by using a valve before the flow meter. To cool nanofluids, a tube-in-shell type heat exchanger was used.

% Paste this into your TexStudio document

\subsection{Problem Formulation}
The experimental data served as the basis for calculating the convective heat transfer coefficient ($h$) and Nusselt number ($Nu$) using the following equations:

\begin{equation}
q = h \cdot (T_w - T_f) \quad \text{(2)}
\end{equation}

where $q$ is the heat flux, $T_w$ is the measured wall temperature, and $T_f$ is the fluid temperature calculated through the energy balance equation:

\begin{equation}
q = \rho_f \cdot c_f \cdot Q \cdot (T_{\text{fin}} - T_f) \quad \text{(3)}
\end{equation}

Here, $T_{\text{fin}}$ is the measured fluid temperature at the inlet of the test section, $c_f$ is the fluid heat capacity, $\rho_f$ is the fluid density, $S$ is the perimeter of the test tube, and $Q$ is the flow rate. For nanofluids, the value of $\rho c$ was calculated using the equation:

\begin{equation}
\rho c = \rho_f \cdot c_f + \rho_p \cdot c_p \cdot VF \quad \text{(4)}
\end{equation}

Comparing the measured fluid temperature at the outlet of the test section with the theoretical value calculated by Eq. (3) revealed a maximum deviation lower than 12% under the conditions of this study.

The convective heat transfer coefficient, $h$, in Eq. (2), is often expressed in the form of the Nusselt number ($Nu$):

\begin{equation}
Nu = \frac{h \cdot D}{k_f} \quad \text{(5)}
\end{equation}

Here, $D$ is the tube inner diameter, and $k_f$ is the fluid thermal conductivity. For nanofluids, $k_f$ is predicted by the H-C model \cite{ref8}:

\begin{equation}
k_f = k_f \cdot [1 + 2.5 \cdot \phi] \quad \text{(6)}
\end{equation}

where $\phi$ is the volume fraction of nanoparticles. Additionally, the Nusselt number is traditionally related to the Reynolds number ($Re$) and the Prandtl number ($Pr$):

\begin{equation}
Nu = C \cdot Re^m \cdot Pr^n \quad \text{(7)}
\end{equation}

where $C$, $m$, and $n$ are constants. The Reynolds number ($Re$) and the Prandtl number ($Pr$) are defined as:

\begin{equation}
Re = \frac{\rho_f \cdot u \cdot D}{\mu_f} \quad \text{(8)}
\end{equation}

\begin{equation}
Pr = \frac{\mu_f \cdot c_f}{k_f} \quad \text{(9)}
\end{equation}

For nanofluids, the Prandtl number is predicted by the Einstein equation. In Eq. (7), $x$ represents the axial distance from the entrance of the test section.

\section{Modeling}

In this study, an artificial neural network (ANN) program was developed using the MATLAB software environment. A total of 56 experimental datasets, derived from various experiments, were utilized to construct a three-layer feed-forward neural network model. The hyperbolic tangent sigmoid (\texttt{tansig}) transfer function with a back-propagation algorithm at the hidden layer and a linear transfer function (\texttt{purelin}) at the output layer were employed.

To enhance the numerical stability (accuracy index) of the model construction, both inputs and targets were initially normalized to produce data with zero mean and unity standard deviation. Principal component analysis (PCA) was then performed before the training stage. The number of principal components, accounting for 98\% of the variation, equaled the number of original input parameters, indicating no redundancy in the dataset.

Next, the datasets were divided into three sets: a training dataset comprising one-half of the data for training the ANN, a validation dataset with one-quarter of the data for validating the developed ANN, and a testing set with one-quarter of the data for evaluating the ANN. Various learning algorithms were applied to select the best one, followed by optimization between the neuron number and mean squared error (MSE) for the chosen learning algorithm.

Different statistical parameters, such as mean absolute error (MAE), MSE, root mean squared error (RMSE), and determination coefficient ($R^2$), were calculated to assess the accuracy of the modeling process.

\section{Results and Discussion}

\subsection{Learning Algorithm Selection}

To identify the optimal back-propagation learning algorithm, various algorithms were employed. A three-layer feed-forward artificial neural network (ANN) with a hyperbolic tangent sigmoid (\texttt{tansig}) transfer function at the hidden layer and a linear (\texttt{purelin}) transfer function at the output layer was utilized for all back-propagation learning algorithms. Ten neurons were consistently used in the hidden layer for all algorithms. The results are summarized in Table 1.

\begin{table}[ht]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Learning Algorithm} & \textbf{Minimum MSE} \\ \hline
		Levenberg–Marquardt (LM)   & 0.0010              \\ \hline
	\end{tabular}
	\caption{Performance comparison of back-propagation learning algorithms.}
	\label{tab:learning_algorithms}
\end{table}

As evident from Table 1, the Levenberg–Marquardt (LM) algorithm exhibited the lowest Mean Squared Error (MSE) of 0.0010, establishing it as the most effective back-propagation learning algorithm.

\subsection{Optimization of Artificial Neural Network}

The number of hidden layer neurons significantly influences the performance of artificial neural networks (ANNs). Inappropriately low values hinder proper training, while excessively high values lead to overfitting \cite{ref11}. The optimal number of neurons in the hidden layer was determined through trial and error, ranging from 2 to 9 neurons. The relationship between the number of hidden layer neurons and MSE is presented in Table 2. The minimum MSE value of 0.0008 was observed with 6 neurons in the hidden layer. Consequently, the ANN was configured with 6 neurons in the hidden layer.

\begin{table}10ht]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Number of Neurons in Hidden Layer} & \textbf{MSE} \\ \hline
		2                                          & 0.0021      \\ \hline
		4                                          & 0.0015      \\ \hline
		6                                          & 0.0008      \\ \hline
		8                                          & 0.0013      \\ \hline
		9                                          & 0.0016      \\ \hline
	\end{tabular}
	\caption{Optimization of the number of neurons in the hidden layer.}
	\label{tab:hidden_layer_neurons}
\end{table}

\subsection{Convective Heat Transfer Coefficient of Distilled Water}

The experimental system was tested with distilled water at Reynolds numbers of 2960 and 3960. To validate the constant heat flux boundary condition, the experimental data of the convective heat transfer coefficient of distilled water, represented as the Nusselt number (Nu), was compared with the predicted Nu number from the Gnielinski equation \cite{ref9}. The Gnielinski equation for constant heat flux boundary conditions is given by:

\begin{equation}
Nu = \left(0.155 \cdot Re^{0.33}\right) \cdot Pr^{0.33}
\label{eq:gniellinski}
\end{equation}

The experimental and predicted Nu numbers for Reynolds numbers 2960 and 3960 are shown in Figures 2(a) and 2(b). The Gnielinski equation predicts the experimental data with a 4 \% deviation for $Re = 2960$ and a 3 \% deviation for $Re = 3960$. These deviations are attributed to the influence of the entrance on the heat transfer coefficient, not accounted for in Eq.~(\ref{eq:gniellinski}). Therefore, the constant heat flux boundary condition for this study is deemed valid.

\subsection{Effect of Nanoparticle Concentrations on the Convective Heat Transfer Coefficient in Distilled Water}

In Figures 3(a) and 3(b), the experimental results and predicted data from the ANN were compared. The axial profiles of the heat transfer coefficient of nanofluids show an increase with increasing particle concentration. The enhancement is more pronounced at higher Reynolds numbers. For instance, at $Re = 2960$ and $Re = 3960$, the maximum enhancement with 1.50 vol.\% TiO$_2$ nanofluids is about 40\% (see Fig. 3(a)) and more than 52\% (see Fig. 3(b)), respectively. The good agreement between experimental results and predicted data demonstrates the high accuracy of the ANN in predicting this process.

\subsection{Convective Heat Transfer Coefficient of Water/Ethylene Glycol Mixture}

The experimental system was tested with a mixture consisting of 60 weight-\% ethylene glycol and 40 weight-\% distilled water at $Re = 2030$. Figure 4 shows the measured data, comparing it with calculated values from the Shah equation \cite{ref10}. The Shah equation for laminar flows under constant heat flux boundary conditions is given by:

\begin{equation}
Nu = \left(1.86 + \frac{0.86 \cdot Re^{0.5} \cdot Pr^{0.33}}{\left(1 + 0.12 \cdot (Re \cdot Pr)^{0.666}\right)^{0.25}}\right)
\label{eq:shah}
\end{equation}

The Shah equation predicts the experimental data with a 1.5\% deviation for $Re = 2030$.

\subsection{Effect of Nanoparticle Concentration on the Convective Heat Transfer Coefficient in the Mixture of Water and Ethylene Glycol}

Figure 5 shows the axial profiles of the convective heat transfer coefficient of nanofluids with different TiO$_2$ particle concentrations in the mixture consisting of 60 weight-\% ethylene glycol and 40 weight-\% distilled water at $Re = 2030$. The convective heat transfer coefficient was indicated based on experimental data and ANN results. This figure shows that with an increasing particle concentration, the convective heat transfer coefficient of TiO$_2$ increases.

\subsection{Effect of Heat Flux on the Convective Heat Transfer Coefficient of Nanofluid}

Figure 6 shows the enhancement of the convective heat transfer coefficient for power supplies of 440W and 550W based on experimental data and ANN results. In this figure, the convective heat transfer coefficient in distilled water nanofluid increases with an increasing heat flux. Results also show that the improvement of convective heat transfer coefficient of the base fluid due to the addition of nanoparticles seems to be more considerable in turbulent flow regimes and higher heat fluxes. Comparing experimental data and ANN results indicates that the ANN could predict this process better at lower heat flux than at higher heat flux.

\section{Conclusions}

In this study, experimental work has been conducted to investigate the heat transfer behavior of TiO$_2$ nanofluids flowing through a straight vertical pipe under both laminar and turbulent flow conditions. The obtained results were utilized by an Artificial Neural Network (ANN) to model this process. The effects of operational parameters such as nanoparticle concentrations, flow Reynolds number, type of base fluid, and heat flux were investigated. The following conclusions can be drawn from the results of experiments in this study:

\begin{itemize}
	\item Addition of nanoparticles into the base fluid enhances the convective heat transfer coefficient, and the enhancement increases with increasing particle concentration.
	\item The enhancement due to the addition of nanoparticles seems to be more considerable at higher Reynolds numbers.
	\item The convective heat transfer coefficient enhancement for the mixture consisting of 60 weight-\% ethylene glycol and 40 weight-\% distilled water is greater than the nanofluid of distilled water alone.
	\item The use of TiO$_2$ nanoparticles as the dispersed phase in distilled water can significantly enhance the convective heat transfer, and the enhancement increases with increasing heat flux.
	\item Good agreement between experimental data and predicted results of the ANN shows that the ANN can be used to model this process with high accuracy, except for higher heat flux.
\end{itemize}

\bibliographystyle{unsrt}
\bibliography{ref.bib}  % Replace with your actual file name

\appendix

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{fig1}
	\caption{}
	\label{fig:fig1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig2}
	\caption{}
	\label{fig:fig2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig3}
	\caption{}
	\label{fig:fig3}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{fig4}
	\caption{}
	\label{fig:fig4}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{fig5}
	\caption{}
	\label{fig:fig5}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig8}
	\caption{}
	\label{fig:fig8}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{fig6}
	\caption{}
	\label{fig:fig6}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{fig9}
	\caption{}
	\label{fig:fig9}
\end{figure}

\begin{table}[htbp]
	\centering
	\caption{Comparison of various back propagation learning algorithms}
	\begin{tabular}{cccc}
		\hline
		R2 & MSE & Function & Back Propagation Algorithm \\
		\hline
		0.9899 & 0.0099 & trainrp & Resilient backpropagation (Rprop) \\
		0.9969 & 0.0031 & traincgf & Fletcher–Reeves conjugate gradient backpropagation \\
		0.9957 & 0.0042 & traincgp & Polak–Ribi´ere conjugate gradient backpropagation \\
		0.9960 & 0.0039 & traincgb & Powell–Beale conjugate gradient backpropagation \\
		0.9990 & 0.0010 & trainlm & Levenberg–Marquardt backpropagation \\
		0.9944 & 0.0112 & trainscg & Scaled conjugate gradient backpropagation \\
		0.9963 & 0.0037 & trainbfg & BFGS quasi-Newton backpropagation \\
		0.9957 & 0.0042 & trainoss & One step secant backpropagation \\
		0.9910 & 0.0089 & traingd & Batch gradient descent \\
		0.7778 & 0.2186 & traingdx & Variable learning rate backpropagation \\
		0.8963 & 0.1061 & traingdm & Batch gradient descent with momentum \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Number of neurons in hidden layer with related mean square errors.}
	\begin{tabular}{cc}
		\hline
		MSE $\times 10^2$ & Number of Neurons \\
		\hline
		1.69 & 2 \\
		0.31 & 3 \\
		0.23 & 4 \\
		0.17 & 5 \\
		0.08 & 6 \\
		0.20 & 7 \\
		0.11 & 8 \\
		0.15 & 9 \\
		\hline
	\end{tabular}
\end{table}

\end{document}

### 2024-01-04 NN/convert.py

@@ -1,0 +1,30 @@
+import pandas as pd
+import numpy as np
+
+# Load data from CSV file into a DataFrame
+df = pd.read_csv('raw_data.csv')
+# Define a dictionary for mapping long labels to short labels
+label_mapping = {
+    'heat transfer Cofficent':'HTC',
+    'flow rate(m3/s)': 'flow_rate',
+    'concentration of nanoparticle(vol. fraction))': 'conc_nano',
+    'Kfluid(W/mC)': 'Kfluid',
+    'heat flux(W/m2)': 'heat_flux',
+    'X/D': 'X_D',
+    'heat transfer Cofficent (prediction with ANN)1': 'HTC_ANN1',
+    'heat transfer Cofficent (prediction with ANN)2': 'HTC_ANN2',
+}
+
+# Replace non-standard decimal separator and convert to numeric
+for long_label, short_label in label_mapping.items():
+    df[short_label] = pd.to_numeric(df[long_label].astype(str).str.replace('٫', '.'), errors='coerce')
+
+# Drop the original long-label columns
+df = df.drop(columns=list(label_mapping.keys()))
+
+# Drop rows with NaN values
+df = df.dropna()
+# Save the resulting DataFrame to a new CSV file
+df.to_csv('data.csv', index=False)
+
+

### 2024-01-04 NN/model.py

@@ -1,0 +1,168 @@
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+import pandas as pd
+import numpy as np
+
+# Load data from CSV file into a DataFrame
+df = pd.read_csv('data.csv')
+
+# Split and scale the data
+X = df[['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']]
+y = df['HTC'] # heat transfer Cofficent
+
+# Split data to test and train sets
+X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
+
+# Preprocess data
+# Fix scales
+scaler = StandardScaler()
+X_train = torch.tensor(scaler.fit_transform(X_train), dtype=torch.float32)
+X_test = torch.tensor(scaler.transform(X_test), dtype=torch.float32)
+y_train = torch.tensor(y_train.values, dtype=torch.float32).view(-1, 1)
+y_test = torch.tensor(y_test.values, dtype=torch.float32).view(-1, 1)
+
+# Normalize inputs and targets to zero mean and unity standard deviation
+X_train = (X_train - X_train.mean()) / X_train.std()
+X_test = (X_test - X_test.mean()) / X_test.std()
+y_train = (y_train - y_train.mean()) / y_train.std()
+y_test = (y_test - y_test.mean()) / y_test.std()
+
+# Define the neural network
+class RegressionModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 64)
+        self.relu = nn.ReLU()
+        self.fc2 = nn.Linear(64, 32)
+        self.fc3 = nn.Linear(32, 1)
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x = self.relu(x)
+        x = self.fc2(x)
+        x = self.relu(x)
+        x = self.fc3(x)
+        return x
+
+# Define the neural network with ReLU activation function
+class ReLUModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 10)
+        self.relu = nn.ReLU()
+        self.fc2 = nn.Linear(10, 1)
+        self.linear = nn.Identity()
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x = self.relu(x)
+        x = self.fc2(x)
+        x = self.linear(x)
[…]

### 2024-01-05 paper/sn-article-template/sn-article.tex
latex file added

--- 2024-01-04 latex/paper.tex
@@
-\documentclass{article}
-\usepackage{graphicx}
-\usepackage{amsmath}
+%Version 2.1 April 2023
+% See section 11 of the User Manual for version history
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\linespread{1.5} % You can adjust the factor (e.g., 1.5 for 1.5x spacing)
+%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing
 
-\title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
-\author{Your Name}
-\date{}
+%%=======================================================%%
+%% to print line numbers in the margin use lineno option %%
+%%=======================================================%%
+
+%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%======================================================%%
+%% to compile with pdflatex/xelatex use pdflatex option %%
+%%======================================================%%
+
+%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+
+%%Note: the following reference styles support Namedate and Numbered referencing.
+By default the style follows the most common style.
+To switch between the options you can add or remove “Numbered” in the optional parenthesis.
+%%The option is available for: sn-basic.bst, sn-vancouver.bst, sn-chicago.bst, sn-mathphys.bst. %
+
+%%\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
+%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
+\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
+%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
+%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
+%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
+%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
+%%\documentclass[default]{sn-jnl}% Default
+%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout
+
+%%%% Standard Packages
+%%<additional latex packages if required can be included here>
+
+\usepackage{graphicx}%
+\usepackage{multirow}%
+\usepackage{amsmath,amssymb,amsfonts}%
+\usepackage{amsthm}%
+\usepackage{mathrsfs}%
+\usepackage[title]{appendix}%
+\usepackage{xcolor}%
+\usepackage{textcomp}%
+\usepackage{manyfoot}%
+\usepackage{booktabs}%
+\usepackage{algorithm}%
+\usepackage{algorithmicx}%
+\usepackage{algpseudocode}%
+\usepackage{listings}%
+%%%%
+
+%%%%%=============================================================================%%%%
+%%%%  Remarks: This template is provided to aid authors with the preparation
+%%%%  of original research articles intended for submission to journals published 
+%%%%  by Springer Nature. The guidance has been prepared in partnership with 
+%%%%  production teams to conform to Springer Nature technical requirements. 
+%%%%  Editorial and presentation requirements differ among journal portfolios and 
+%%%%  research disciplines. You may find sections in this template are irrelevant 
+%%%%  to your work and are empowered to omit any such section if allowed by the 
+%%%%  journal you intend to submit to. The submission guidelines and policies 
+%%%%  of the journal take precedence. A detailed User Manual is available in the 
+%%%%  template package for technical guidance.
+%%%%%=============================================================================%%%%
+
+%\jyear{2021}%
+
+%% as per the requirement new theorem styles can be included as shown below
+\theoremstyle{thmstyleone}%
+\newtheorem{theorem}{Theorem}%  meant for continuous numbers
+%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
+%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
+\newtheorem{proposition}[theorem]{Proposition}% 
+%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
+
+\theoremstyle{thmstyletwo}%
+\newtheorem{example}{Example}%
+\newtheorem{remark}{Remark}%
+
+\theoremstyle{thmstylethree}%
+\newtheorem{definition}{Definition}%
+
+\raggedbottom
+%%\unnumbered% uncomment this for unnumbered level heads
 
@@
 
+\title[Article Title]{Article Title}
+
+%%=============================================================%%
+%% Prefix	-> \pfx{Dr}
+%% GivenName	-> \fnm{Joergen W.}
+%% Particle	-> \spfx{van der} -> surname prefix
+%% FamilyName	-> \sur{Ploeg}
+%% Suffix	-> \sfx{IV}
+%% NatureName	-> \tanm{Poet Laureate} -> Title after name
+%% Degrees	-> \dgr{MSc, PhD}
+%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate} 
+%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
+%%=============================================================%%
+
+\author*[1,2]{\fnm{First} \sur{Author}}\email{iauthor@gmail.com}
+
+\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
+\equalcont{These authors contributed equally to this work.}
+
+\affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}
+
+\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}
+
+\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}
+
+%%==================================%%
+%% sample for unstructured abstract %%
+%%==================================%%
+
+\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}
+
+%%================================%%
+%% Sample for structured abstract %%
+%%================================%%
+
+% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
+% 
+% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications.
+The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations.
+As a guide the abstract should not exceed 200 words.
+Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}
+
+\keywords{keyword1, Keyword2, Keyword3, Keyword4}
+
+%%\pacs[JEL Classification]{D8, H51}
+
+%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}
+
 \maketitle
-
-\begin{abstract}
-In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids.
-Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions.
-The investigation covered diverse operational parameters, including heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number, to quantify the convective heat transfer coefficient.
-These operational parameters were incorporated as inputs into an artificial neural network to model the convective heat transfer coefficient.
-Evaluation metrics, such as mean square error and correlation coefficient, were computed, revealing the remarkable performance of the neural network in capturing the underlying processes.
-The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes.
-The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
-\end{abstract}
 
@@
 For instance, Santra et al.
-applied ANN to predict heat transfer in laminar natural convection of copper–water nanofluids, demonstrating accurate predictions within the training data range \cite{ref3}.
+applied ANN to predict heat transfer in laminar natural convection of copper?water nanofluids, demonstrating accurate predictions within the training data range \cite{ref3}.
 Fazeli et al.
-utilized ANN to simulate the heat transfer characteristics of a miniature heat sink cooled by SiO2–water nanofluids, achieving excellent agreement with mathematical simulations \cite{ref4}.
+utilized ANN to simulate the heat transfer characteristics of a miniature heat sink cooled by SiO2?water nanofluids, achieving excellent agreement with mathematical simulations \cite{ref4}.
 Balcilar et al.
@@
 An ultrasonic vibrator (Tecna 6) was used for the preparation of mixed aqueous suspensions.
-The suspension was sonicated for 4 hours at a frequency of 50-60 kHz with an output power of 138W, at 65ºC, and pH=11 by NaOH solution.
+The suspension was sonicated for 4 hours at a frequency of 50-60 kHz with an output power of 138W, at 65 C, and pH=11 by NaOH solution.
 Nanofluids containing 0.5\%, 1.0\%, 1.5\% titanium dioxide by volume were obtained using the two-step method.
@@
 \begin{equation}
-q = h \cdot (T_w - T_f) \quad \text{(2)}
+	q = h \cdot (T_{3i} - T_f) \quad \text{(2)}
 \end{equation}
@@
 		\textbf{Learning Algorithm} & \textbf{Minimum MSE} \\ \hline
-		Levenberg–Marquardt (LM)   & 0.0010              \\ \hline
+		Levenberg?Marquardt (LM)   & 0.0010              \\ \hline
 	\end{tabular}
@@
 
-As evident from Table 1, the Levenberg–Marquardt (LM) algorithm exhibited the lowest Mean Squared Error (MSE) of 0.0010, establishing it as the most effective back-propagation learning algorithm.
+As evident from Table 1, the Levenberg?Marquardt (LM) algorithm exhibited the lowest Mean Squared Error (MSE) of 0.0010, establishing it as the most effective back-propagation learning algorithm.
 
@@
 		0.9899 & 0.0099 & trainrp & Resilient backpropagation (Rprop) \\
-		0.9969 & 0.0031 & traincgf & Fletcher–Reeves conjugate gradient backpropagation \\
-		0.9957 & 0.0042 & traincgp & Polak–Ribi´ere conjugate gradient backpropagation \\
-		0.9960 & 0.0039 & traincgb & Powell–Beale conjugate gradient backpropagation \\
-		0.9990 & 0.0010 & trainlm & Levenberg–Marquardt backpropagation \\
+		0.9969 & 0.0031 & traincgf & Fletcher?Reeves conjugate gradient backpropagation \\
+		0.9957 & 0.0042 & traincgp & Polak?Ribiere conjugate gradient backpropagation \\
+		0.9960 & 0.0039 & traincgb & Powell?Beale conjugate gradient backpropagation \\
+		0.9990 & 0.0010 & trainlm & Levenberg?Marquardt backpropagation \\
 		0.9944 & 0.0112 & trainscg & Scaled conjugate gradient backpropagation \\
@@
 
+%%===========================================================================================%%
+%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
+%% system, please include the references within the manuscript file itself. You may do this  %%
+%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
+%% file, and delete the associated \verb+\bibliography+ commands.                            %%
+%%===========================================================================================%%
+
+\bibliography{sn-bibliography}% common bib file
+%% if required, the content of .bbl file can be included here once bbl is generated
+%%\input sn-article.bbl
+
 \end{document}

### 2024-01-05 Matlab/nn.m

@@ -1,0 +1,51 @@
+
+
+% Extract features (X) and target variable (Y)
+X = data(:, 2:6);  % Assuming the first 7 columns are features
+Y = data(:, 1);    % Assuming the 8th column is the target variable
+
+% Split the data into training (80%) and testing (20%) sets
+rng('default');  % For reproducibility
+cv = cvpartition(size(data, 1), 'HoldOut', 0.2);
+idxTrain = training(cv);
+idxTest = test(cv);
+
+X_train = X(idxTrain, :);
+y_train = Y(idxTrain, :);
+
+X_test = X(idxTest, :);
+y_test = Y(idxTest, :);
+
+% Normalize and scale the features if necessary
+% You can use z-score normalization as an example
+mu = mean(X_train);
+sigma = std(X_train);
+
+X_train = (X_train - mu) ./ sigma;
+X_test = (X_test - mu) ./ sigma;
+
+% Now you can use X_train, Y_train for training and X_test, Y_test for testing
+% Your machine learning model training code goes here
+
+
+% Define the neural network architecture
+net = feedforwardnet([10, 5]);
+
+% Load and preprocess your training data (X_train, y_train)
+
+% Set training parameters
+net.trainParam.epochs = 100;
+net.trainParam.lr = 0.01;
+
+
+% Assuming X_train and y_train are tables
+X_train_transposed = rows2vars(X_train);
+y_train_transposed = rows2vars(y_train);
+
+% Assuming net is your neural network
+net = train(net, X_train_transposed, y_train_transposed);
+
+
+% Make predictions on new data
+predictions = net(X_test');
+

### 2024-01-05 latex/paper.tex
dorostesh kardam

@@
 \title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
-\author{Your Name}
+\author{Zeinab pouramini}
 \date{}
@@
 \begin{abstract}
+	Salam
+
 In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids.
@@
 \end{abstract}
+
+Taghirs
 
@@
 Figure 4 shows the measured data, comparing it with calculated values from the Shah equation \cite{ref10}.
-The Shah equation for laminar flows under constant heat flux boundary conditions is given by:
+The Shah equation for laminar flows under constant heat flux boundary conditions is given by
 

### 2024-01-05 latex/paper.tex
FDSFDDS
notebooks

--- 2024-01-04 latex/paper.tex
@@
 \usepackage{amsmath}
+\usepackage{hyperref}
 
@@
 Nanofluids, which are suspensions of small percentages (<5 vol.
-\%) of various nanoparticles in conventional working fluids, have emerged as an excellent solution to address the thermal challenges in advanced heat transfer systems.
+\%) of various nanoparticles in conventional working fluids, have emerged as an excellent solution to address the thermal challenges in advanced heat transfer systems \cite{chen2023}.
 
@@
 
+NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN
+
+The field of nanotechnology, dealing with materials at the nanometer scale, has garnered significant attention from scientists owing to its potential to enhance various material properties [1–4].
+This domain has found widespread applications in thermal engineering, particularly in addressing the critical challenges associated with thermal conductivity (TC) of operating fluids.
+The thermal conductivity of fluids plays a pivotal role in determining the performance of thermal mediums, where higher thermal conductivity is preferred to intensify heat transfer rates.
+Nanofluids, characterized by suspensions of nanoparticles in conventional working fluids, have emerged as a promising approach for enhancing heat transfer, attributed to their heightened thermal conductivity [5–8].
+
+Numerous studies have demonstrated the efficacy of employing nanofluids in thermal mediums such as heat exchangers and heat pipes, resulting in substantial enhancements in thermal performance [9, 10].
+Beyond thermal mediums, the integration of nanofluids has shown potential in improving the efficiency and reliability of different energy-related systems, especially those with low carbon emissions.
+Active techniques, including the use of nanofluids, have been identified as catalysts for heat transfer augmentation, leading to reduced energy consumption and a positive environmental impact.
+For instance, Reddy et al.'s comprehensive review on the applications of nanofluids in solar energy highlighted significant improvements in conversion efficiency compared to pure fluids [ref].
+
+In the realm of clean energy systems, the reliability and efficiency of nanofluid applications have been further underscored.
+For instance, Islam et al.
+[11] investigated the impact of employing nanofluids in the thermal management of a PEM fuel cell, reporting a substantial increase in convective heat transfer, indicating enhanced cooling system reliability.
+Similarly, Zhong et al.
+[12] studied TiO2 nanofluid in a mini channel, observing increased thermal conductivity and viscosity with nanoparticle concentration.
+The altered flow and thermal patterns of nanofluids, compared to traditional fluids, were highlighted, showcasing their potential in diverse applications.
+
+Further investigations by Gravndyan et al.
+[13] delved into the flow of water/TiO2 nanofluids inside a microchannel, considering different aspect ratios of ribs.
+Their findings demonstrated that the addition of nanoparticles increased both friction factor and Performance Evaluation Criteria (PEC), indicating a potential for improved heat transfer performance.
+
+As established in previous studies, the superior heat transfer performance of nanofluids compared to conventional fluids is primarily attributed to their increased thermal conductivity.
+Consequently, several studies have focused on modeling the thermophysical properties of nanofluids [14, 15].
+These modeling efforts have employed various methods, including artificial neural networks (ANN), support vector machines (SVM), and mathematical correlations [16, 17].
+Among these approaches, ANNs have demonstrated their attractiveness due to their ability to accurately predict and forecast complex output modes [18, 19].
+
+Esfe et al.
+[20] applied ANN to estimate the thermal conductivity of Al2O3/EG nanofluid, achieving a maximum deviation of 1.3\%.
+Vakili et al.
+[21] successfully employed ANN to model the thermal conductivity of CuO/water-EG nanofluid, demonstrating accurate predictions with an R-squared value of 0.999.
+Toghraie et al.
+[22] extended the application of ANN to propose a predictive model for the thermal conductivity of SiO2/EG-water nanofluid, showcasing the great reliability of their model with a maximum error value of 0.0125.
+In another study, Esfe et al.
+[23] utilized ANN to estimate the thermal conductivity of Al2O3/water-EG nanofluid, achieving a mean square error (MSE) of around \(2.08 \times 10^{-6}\) under optimal conditions.
+
+Further extending the application of ANN, Esfe et al.
+[24] employed a two-hidden-layer network to predict the Nusselt number and pressure drop of TiO2 nanofluids with varying nanoparticle diameters.
+Their study indicated that an increase in Reynolds number and concentration led to higher Nusselt number and pressure drop, showcasing the potential of nanofluids in diverse heat transfer applications.
+
+Considering the wide-ranging applications of TiO2 nanofluids in energy-related technologies, this paper aims to contribute a comprehensive model for the thermal conductivity of various nanofluids.
+In pursuit of a model applicable to different base fluids, the thermal conductivity of the base fluid is considered as an additional input, along with size, volume fraction, and temperature.
+The comparative performance analysis of ANN-based models utilizes two methods, namely group method of data handling (GMDH) and multi-layer perceptron (MLP).
+This study proposes different models for the thermal conductivity modeling of nanofluids with TiO2 across various base fluids.
+Additionally, two distinct types of networks are assessed to determine the highest accuracy, while varying the architecture of the models to identify the network with the maximum reliability in forecasting the considered output.
+
 \section{Related Works}
+
+Zhang, Y., et al.
+(2021): Investigated the convective heat transfer enhancement of TiO2-water nanofluids in a circular tube, emphasizing the impact of nanoparticle concentration and temperature on heat transfer performance \cite{ref8}.
+
+Wang, J., et al.
+(2022): Explored the influence of particle size and volume fraction on the thermal conductivity of TiO2-based nanofluids, providing insights into their heat transfer characteristics \cite{ref9}.
+
+Li, X., et al.
+(2023): Applied machine learning techniques, including ANN, for predicting heat transfer coefficients in nanofluids with diverse nanoparticle types, revealing the importance of considering particle morphology in modeling \cite{ref10}.
+
+Chen, Z., et al.
+(2023): Investigated the convective heat transfer performance of ethylene glycol-based nanofluids containing TiO2 nanoparticles under turbulent flow conditions, highlighting the impact of flow parameters on heat transfer coefficients \cite{ref11}.
+
+Kim, H., et al.
+(2024): Studied the forced convective heat transfer of TiO2-ethylene glycol nanofluids in a horizontal tube, focusing on the thermal enhancement under varying nanoparticle concentrations and flow velocities \cite{ref12}.Zhang, Y., et al.
+(2021): Investigated the convective heat transfer enhancement of TiO2-water nanofluids in a circular tube, emphasizing the impact of nanoparticle concentration and temperature on heat transfer performance \cite{ref8}.
+
+Wang, J., et al.
+(2022): Explored the influence of particle size and volume fraction on the thermal conductivity of TiO2-based nanofluids, providing insights into their heat transfer characteristics \cite{ref9}.
+
+Li, X., et al.
+(2023): Applied machine learning techniques, including ANN, for predicting heat transfer coefficients in nanofluids with diverse nanoparticle types, revealing the importance of considering particle morphology in modeling \cite{ref10}.
+
+Chen, Z., et al.
+(2023): Investigated the convective heat transfer performance of ethylene glycol-based nanofluids containing TiO2 nanoparticles under turbulent flow conditions, highlighting the impact of flow parameters on heat transfer coefficients \cite{ref11}.
+
+Kim, H., et al.
+(2024): Studied the forced convective heat transfer of TiO2-ethylene glycol nanofluids in a horizontal tube, focusing on the thermal enhancement under varying nanoparticle concentrations and flow velocities \cite{ref12}.
+
+NNNNNNNNNNNNNNNNNNNNNN
+%###############################
 

### 2024-01-05 NN/model.py

@@ -1,3 +1,4 @@
+from matplotlib import pyplot as plt
 import torch
 import torch.nn as nn
 import torch.optim as optim
@@ -5,11 +6,14 @@ from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import StandardScaler
 import pandas as pd
 import numpy as np
+import torch.nn as nn
+from torchviz import make_dot
 
 # Load data from CSV file into a DataFrame
 df = pd.read_csv('data.csv')
 
 # Split and scale the data
+# X = df[['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']]
 X = df[['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']]
 y = df['HTC'] # heat transfer Cofficent
 
@@ -166,3 +170,33 @@ y_test_np = y_test_denormalized.numpy()
 # Calculate R-squared
 r_squared = r2_score(y_test_np, predictions_np)
 print(f'R-squared on Test Set: {r_squared}')
+
+
+
+# Visualize the model
+
+dummy_input = torch.randn(1, input_size)
+
+dot = make_dot(model(dummy_input), params=dict(model.named_parameters()))
+dot.render("mlp_structure", format="png", cleanup=True)
+
+
+# Create a scatter plot
+plt.figure(figsize=(10, 6))
+plt.scatter(y_test_np, predictions_np, alpha=0.5)
+plt.title('Predictions vs. Actual (Test Set)')
+plt.xlabel('Actual Values')
+plt.ylabel('Predicted Values')
+plt.grid(True)
+plt.show()
+
+
+plt.figure(figsize=(10, 6))
+plt.scatter(y_test_np, y_test_np, color='green', label='Actual', alpha=0.5)
+plt.scatter(y_test_np, predictions_np, color='blue', label='Predicted', alpha=0.5)
+plt.title('Actual vs. Predicted Values (Test Set)')
+plt.xlabel('Values')
+plt.ylabel('Values')
+plt.legend()
+plt.grid(True)
+plt.show()

### 2024-01-30 latex/paper.tex
thaghit

@@
 \usepackage{hyperref}
+\usepackage{float}
+\usepackage{booktabs}
 
@@
 \title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
-\author{Zeinab pouramini}
+\author{Zeinab Pouramini, Zohresadat Shahryari, Motahareh Vakili Fathabadi }
 \date{}
@@
 \begin{abstract}
-In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids.
-Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions.
-The investigation covered diverse operational parameters, including heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number, to quantify the convective heat transfer coefficient.
-These operational parameters were incorporated as inputs into an artificial neural network to model the convective heat transfer coefficient.
-Evaluation metrics, such as mean square error and correlation coefficient, were computed, revealing the remarkable performance of the neural network in capturing the underlying processes.
-The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes.
+In this research, a neural network methodology was employed to predict the forced convective heat transfer coefficient of nanofluids, considering various operational parameters such as heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number.
+These parameters served as inputs for the artificial neural network, enabling the modeling of the convective heat transfer coefficient.
+Through the assessment of different parameter combinations, we identified the most influential factors contributing to accurate predictions.
+The evaluation metrics, including mean square error and correlation coefficient, demonstrated the remarkable performance of the neural network in capturing the intricate processes.
 The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
@@
 
+NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN
+The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes.
+
 NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN
+
+Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions.
+
+NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN
 
@@
 Additionally, two distinct types of networks are assessed to determine the highest accuracy, while varying the architecture of the models to identify the network with the maximum reliability in forecasting the considered output.
+In Figrure \ref{fig:scatterplot}
+
+FFFF
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{pics/scatter_plot}
+	\caption{This rere}
+	\label{fig:scatterplot}
+\end{figure}
 
@@
 
+\begin{figure}[th!]
+	\centering
+	\includegraphics[width=0.8\linewidth]{fig2}
+	\caption{}
+	\label{fig:fig2}
+\end{figure}
+
 \section{Modeling}
@@
 \subsection{Optimization of Artificial Neural Network}
+Table \ref{table:myt} shows
+
+\begin{table}
+	\centering
+	\caption{This is table}
+    \label{table:myt}
+\begin{tabular}{c|c|c|cc|}
+	\hline
+	&  &  &  &  \\
+	\hline
+	&  &  &  &  \\
+	\hline
+	& kg & khjk &  &  \\
+
+	&  &  &  &  \\
+	\hline
+\end{tabular}
+
+\end{table}
 
@@
 \subsection{Convective Heat Transfer Coefficient of Distilled Water}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{lcccc}
+		\toprule
+		Algorithm & R2 & MSE & Function \\
+		\midrule
+		Back Propagation (BP) & 0.9899 & 0.0099 & trainrp \\
+		Resilient Backpropagation (Rprop) & 0.9969 & 0.0031 & traincgf \\
+		Fletcher–Reeves Conjugate Gradient & 0.9957 & 0.0042 & traincgp \\
+		Polak–Ribière Conjugate Gradient & 0.9960 & 0.0039 & traincgb \\
+		Powell–Beale Conjugate Gradient BP & 0.9990 & 0.0010 & trainlm \\
+		Levenberg–Marquardt BP & 0.9944 & 0.0112 & trainscg \\
+		Scaled Conjugate Gradient BP & 0.9963 & 0.0037 & trainbfg \\
+		BFGS Quasi-Newton BP & 0.9957 & 0.0042 & trainoss \\
+		One-Step Secant BP & 0.9910 & 0.0089 & traingd \\
+		Batch Gradient Descent & 0.7778 & 0.2186 & traingdx \\
+		Variable Learning Rate BP & & & \\
+		\bottomrule
+	\end{tabular}
+	\caption{Your table caption here.}
+	\label{tab:yourtablelabel}
+\end{table}
 
@@
 	\label{fig:fig1}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{fig2}
-	\caption{}
-	\label{fig:fig2}
 \end{figure}

### 2024-01-30 NN/model.py

@@ -15,6 +15,7 @@ df = pd.read_csv('data.csv')
 # Split and scale the data
 # X = df[['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']]
 X = df[['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']]
+
 y = df['HTC'] # heat transfer Cofficent
 
 # Split data to test and train sets

### 2024-02-01 NN/back1.py
commit

@@ -9,7 +9,6 @@ import numpy as np
 import torch.nn as nn
 from sklearn.metrics import r2_score
 from tabulate import tabulate
-import os
 
 # Define the neural network with ReLU activation function
 class ReLUModel(nn.Module):
@@ -83,8 +82,7 @@ class RegressionModel(nn.Module):
 
 # Function to apply model on data and generate predictions
 # Return predictions, MSE and R-Squared
-def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs, 
-        display_steps=False):
+def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs):
    # Fix scales
     scaler = StandardScaler()
     X_train = torch.tensor(scaler.fit_transform(X_train), dtype=torch.float32)
@@ -99,10 +97,12 @@ def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs,
     y_test_normalized = (y_test - y_test.mean()) / y_test.std()
 
     input_size = X_train.shape[1]
+    print("input size is:", input_size)
+
     # Instantiate the model and define loss function and optimizer
     model = model_class(input_size)
     criterion = nn.MSELoss()
-    optimizer = optim.Adam(model.parameters(), lr=0.01)
+    optimizer = optim.Adam(model.parameters(), lr=0.001)
 
     # Train the model
     for epoch in range(num_epochs):
@@ -113,7 +113,7 @@ def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs,
         loss.backward()
         optimizer.step()
 
-        if (epoch + 1) % 10 == 0 and display_steps:
+        if (epoch + 1) % 10 == 0:
             print(f'Epoch [{epoch+1}/{num_epochs}], Loss: {loss.item()}')
 
     # Evaluate the model on the test set
@@ -131,185 +131,94 @@ def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs,
     y_test_np = y_test.numpy()
 
     # Calculate R-squared
-    r2 = r2_score(y_test_np, predictions_np)
+    r_squared = r2_score(y_test_np, predictions_np)
     # Return predictions, MSE and R-Squared
-    return predictions_np, mse, r2
+    return predictions_np, mse, r_squared
 
 ############################## Plot Resuts #######################
 def plot_results(predictions_np, y_test, title, file_name):
     # Convert predictions and y_test to NumPy arrays
[…]

### 2024-02-01 NN/model.py
commit

@@ -171,7 +171,7 @@ def generate_latax_table(table, caption="table", label=""):
 
 ############################ Feature Selection ####################
 # Selects the best combination of features by removing features one by one
-# Searc about Backward Elimination 
+# Search about Backward Feature Elimination 
 def backward_feature_elimination(model_class, data, inputs, output, num_epochs, random_seed):
     y = data[output] 
     # Remove extra columns
@@ -188,11 +188,13 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs, 
     rows.append({"features": inputs, "R2": round(mean_r2,2)})
     while(True):
         for feature in candidates:
+            # Selet other features except for current feature
             features = [f for f in candidates if f != feature]
             X = data[features]
             mean_r2, _, _, _ = repeat_apply(3, X, y, num_epochs, random_seed)
             results[feature] = mean_r2
             print("---------------------------------------")
+            # Results of removing the feature
             print("Removing:", feature)
             print("Features:", features)
             print("R2:", mean_r2)
@@ -205,7 +207,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs, 
             candidates.remove(max_results_key)
             best_r2 = max_results
             print('=================================')
-            print('step: ' + str(len(candidates)))
+            print('step: ' + str(len(inputs) - len(candidates)))
             print(candidates)
             print('Best R2: ' + str(max_results))
             print('================================')
@@ -224,6 +226,9 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs, 
     return table
 
 # Finds the combinaiton of features that best predict y
+# This method add features one by one
+# Search about Forward Feature Selction
+
 def forward_feature_selection(model_class, data, inputs, output, num_epochs, random_seed):
     y = data[output] 
     # Remove extra columns
@@ -273,6 +278,8 @@ def forward_feature_selection(model_class, data, inputs, output, num_epochs, ran
 
     table = pd.DataFrame(data=rows)
     return table
+
+
 # Repeats an apply_model to get average of results
 def repeat_apply(num_repeats, X, y, num_epochs, random_seed, display_steps=False):
     X_train, X_test, y_train, y_test = train_test_split(X, y, 
@@ -382,15 +389,16 @@ for model_index in selected_models:
             }
     results.append(result)
 
-# Creata a Table for results with two columns
+# Creata a Table for results
[…]

### 2024-02-01 NN/model.py
commit

@@ -11,75 +11,85 @@ from sklearn.metrics import r2_score
 from tabulate import tabulate
 import os
 
-# Define the neural network with ReLU activation function
-class ReLUModel(nn.Module):
+num_epochs = 300 
+num_repeats = 5
+# num_repeats shows the number of times to repeat the experiment to get its average values
+random_seed = 123
+torch.manual_seed(random_seed)
+np.random.seed(random_seed)
+# changing random_seed generates different results for each run 
+# The same random_seed gets the same results in each run
+# Dont change it if you want to reproduce the same results
+
+class Linear1HiddenLayer(nn.Module):
+    activation1 = None
     def __init__(self, input_size):
         super().__init__()
-        self.fc1 = nn.Linear(input_size, 10)
-        self.relu = nn.ReLU()
-        self.fc2 = nn.Linear(10, 1)
-        self.linear = nn.Identity()
+        #   O1
+        #   O2                     O1                  
+        #   ...   40 x 10 edges    ...   10 x 1       O1 ---> y
+        #   ...                    ...                 
+        #   O39                    O10    
+        #   O40
+        #
+        #  input                   hidden1             output 
+        self.input_to_hidden1 = nn.Linear(input_size, 10)
+        self.hidden1_to_output = nn.Linear(10, 1)
 
     def forward(self, x):
-        x = self.fc1(x)
-        x = self.relu(x)
-        x = self.fc2(x)
-        x = self.linear(x)
+        # order of computation
+        x = self.input_to_hidden1(x)
+        if self.activation1 is not None:
+            x = self.activation1(x)
+        x = self.hidden1_to_output(x)
         return x
 
-# Define the neural network with Tanh activation function
-class TanhModel(nn.Module):
+class Linear2HiddenLayer(nn.Module):
+    activation1 = None
+    activation2 = None
     def __init__(self, input_size):
         super().__init__()
-        self.fc1 = nn.Linear(input_size, 10)
-        self.tanh = nn.Tanh()
-        self.fc2 = nn.Linear(10, 1)
-        self.linear = nn.Identity()
+        #   O1
+        #   O2                     O1                O1
+        #   ...   40 x 10 edges    ...   10 x 5      ...  5 x 1     O1 ---> y
+        #   ...                    ...               O5
+        #   O39                    O10    
+        #   O40
+        #
[…]

### 2024-02-01 NN/model.py
commit

@@ -20,21 +20,31 @@ np.random.seed(random_seed)
 # changing random_seed generates different results for each run 
 # The same random_seed gets the same results in each run
 # Dont change it if you want to reproduce the same results
+learning_rate = 0.001
+# The learnign rate used in ANN
+hidden_size1 = 10
+hidden_size2 = 5
+# the number of neurons in hidden layers
 
+# https://alexlenail.me/NN-SVG/
+# use the site above to draw the following network
+#
 class Linear1HiddenLayer(nn.Module):
     activation1 = None
     def __init__(self, input_size):
         super().__init__()
-        #   O1
-        #   O2                     O1                  
-        #   ...   40 x 10 edges    ...   10 x 1       O1 ---> y
-        #   ...                    ...                 
-        #   O39                    O10    
-        #   O40
+        #                          O1
+        #   O1                     O2                  
+        #   ...   5 x 10 edges    ...   10 x 1       O1 ---> y
+        #   ...                   ...                 
+        #   O5                    ...  
+        #                         O10
         #
-        #  input                   hidden1             output 
-        self.input_to_hidden1 = nn.Linear(input_size, 10)
-        self.hidden1_to_output = nn.Linear(10, 1)
+        #  input (5 features)     hidden1           output 
+        #   5 neuron             10 neurons        1 neuron
+        #
+        self.input_to_hidden1 = nn.Linear(input_size, hidden_size1)
+        self.hidden1_to_output = nn.Linear(hidden_size1, 1)
 
     def forward(self, x):
         # order of computation
@@ -49,17 +59,18 @@ class Linear2HiddenLayer(nn.Module):
     activation2 = None
     def __init__(self, input_size):
         super().__init__()
-        #   O1
-        #   O2                     O1                O1
-        #   ...   40 x 10 edges    ...   10 x 5      ...  5 x 1     O1 ---> y
+        #     
+        #   O1                     O1                O1
+        #   ...    5 x 10 edges    ...   10 x 5      ...  5 x 1     O1 ---> y
         #   ...                    ...               O5
-        #   O39                    O10    
-        #   O40
+        #   O5                     O10    
+        #      
         #
-        #  input                   hidden1           hidden2        output 
-        self.input_to_hidden1 = nn.Linear(input_size, 10)
-        self.hidden1_to_hidden2 = nn.Linear(10, 5)
[…]

### 2024-02-01 NN/model.py
commit

@@ -20,7 +20,7 @@ np.random.seed(random_seed)
 # changing random_seed generates different results for each run 
 # The same random_seed gets the same results in each run
 # Dont change it if you want to reproduce the same results
-learning_rate = 0.001
+learning_rate = 0.05
 # The learnign rate used in ANN
 hidden_size1 = 10
 hidden_size2 = 5
@@ -104,7 +104,7 @@ class Relu2HiddenLayer(Linear2HiddenLayer):
 
 # Function to apply model on data and generate predictions
 # Return predictions, MSE and R-Squared
-def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs, 
+def fit_model(model_class, X_train, X_test, y_train, y_test, num_epochs, 
         display_steps=False):
    # Fix scales
     scaler = StandardScaler()
@@ -157,7 +157,7 @@ def apply_model(model_class, X_train, X_test, y_train, y_test, num_epochs,
     return predictions_np, mse, r2
 
 ############################## Plot Resuts #######################
-def plot_results(predictions_np, y_test, title, file_name):
+def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
     # Convert predictions and y_test to NumPy arrays
     y_test_np = y_test.to_numpy()
     # Calculate R-squared
@@ -171,8 +171,8 @@ def plot_results(predictions_np, y_test, title, file_name):
     plt.ylabel('Predicted Values')
     plt.legend()
     plt.grid(True)
-    # Remove comment if you don't want to show the plot
-    # plt.show()
+    if show_plot is True:
+        plt.show()
     # Save the image of plot in images folder
     plt.savefig(os.path.join("images", file_name), format="png")
 
@@ -198,7 +198,9 @@ def backward_feature_elimination(model_class, data, inputs, output):
     # Remove extra columns
     data = data.drop([output, 'HTC_ANN1', 'HTC_ANN2'], axis=1).copy()
     X = data[inputs]
-    mean_r2, _, _, _ = repeat_apply(num_repeats, X, y, num_epochs, random_seed)
+    # it uses num_repeats, num_epochs and random_seed as global variables
+    # use _ for output of repeat_fit_model, which you don't need to use here
+    mean_r2, _, _, _, _,_ = repeat_fit_model(num_repeats, X, y, num_epochs, random_seed)
     best_r2 = mean_r2
     print("Using all features")
     print("Features:", inputs)
@@ -212,8 +214,7 @@ def backward_feature_elimination(model_class, data, inputs, output):
[…]

### 2024-02-01 NN/model.py
commit

@@ -163,18 +163,18 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
     # Calculate R-squared
     r2 = r2_score(y_test_np, predictions_np)
 
-    plt.figure(figsize=(10, 6))
-    plt.scatter(y_test_np, y_test_np, color='green', label='Actual', alpha=0.5)
-    plt.scatter(y_test_np, predictions_np, color='blue', label='Predicted', alpha=0.5)
-    plt.title(title + ' ' +  f' R-Squared:{r2:.2f}')
-    plt.xlabel('Actual Values')
-    plt.ylabel('Predicted Values')
-    plt.legend()
-    plt.grid(True)
+    fig, ax = plt.subplots(figsize=(10, 6))
+    ax.scatter(y_test_np, y_test_np, color='green', label='Actual', alpha=0.5)
+    ax.scatter(y_test_np, predictions_np, color='blue', label='Predicted', alpha=0.5)
+    ax.set_title(title + ' ' +  f' R-Squared:{r2:.2f}')
+    ax.set_xlabel('Actual Values')
+    ax.set_ylabel('Predicted Values')
+    ax.legend()
+    ax.grid(True)
     if show_plot is True:
         plt.show()
     # Save the image of plot in images folder
-    plt.savefig(os.path.join("images", file_name), format="png")
+    fig.savefig(os.path.join("images", file_name), format="png")
 
 ################ Generate Latex Tables
 def generate_latax_table(table, caption="table", label=""):
@@ -439,7 +439,7 @@ X_train, X_test, y_train, y_test = train_test_split(X, y,
 # Show and save the plot for best results
 best_predictions = model_best_predictions[best_model_name] 
 title = "Prediction of " + output + " using " + " ".join(inputs)+" with " + best_model_name 
-file_name = f"R-{best_mean_r2:.2f}-" + best_model_name + "-" + output + "-using-".join(inputs) + ".png"
+file_name = f"R2-{best_r2:.2f}-" + best_model_name + "-" + output + "-using-".join(inputs) + ".png"
 
 print("\n\n")
 print("Plot was saved in images folder")

### 2024-02-02 NN/back.py
commit

@@ -1,14 +1,0 @@
-import matplotlib.pyplot as plt
-
-
-# Get the weights of a specific layer (change 'layer_name' to the name of your layer)
-layer_name = 'fc2'
-layer = dict(model.named_children())[layer_name]
-weights = layer.weight.data.cpu().numpy()
-
-# Visualize the weights
-plt.figure(figsize=(10, 5))
-plt.imshow(weights, cmap='viridis', aspect='auto')
-plt.title(f'Weights of {layer_name}')
-plt.colorbar()
-plt.show()

### 2024-02-02 NN/back/back.py

@@ -1,0 +1,14 @@
+import matplotlib.pyplot as plt
+
+
+# Get the weights of a specific layer (change 'layer_name' to the name of your layer)
+layer_name = 'fc2'
+layer = dict(model.named_children())[layer_name]
+weights = layer.weight.data.cpu().numpy()
+
+# Visualize the weights
+plt.figure(figsize=(10, 5))
+plt.imshow(weights, cmap='viridis', aspect='auto')
+plt.title(f'Weights of {layer_name}')
+plt.colorbar()
+plt.show()

### 2024-02-02 NN/back/back1.py

@@ -1,0 +1,351 @@
+from matplotlib import pyplot as plt
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+import pandas as pd
+import numpy as np
+import torch.nn as nn
+from sklearn.metrics import r2_score
+from tabulate import tabulate
+
+# Define the neural network with ReLU activation function
+class ReLUModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 10)
+        self.relu = nn.ReLU()
+        self.fc2 = nn.Linear(10, 1)
+        self.linear = nn.Identity()
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x = self.relu(x)
+        x = self.fc2(x)
+        x = self.linear(x)
+        return x
+
+# Define the neural network with Tanh activation function
+class TanhModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 10)
+        self.tanh = nn.Tanh()
+        self.fc2 = nn.Linear(10, 1)
+        self.linear = nn.Identity()
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x = self.tanh(x)
+        x = self.fc2(x)
+        x = self.linear(x)
+        return x
+
+# Define the neural network with Tanh activation function
+class ReLUReLUModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 50)
+        self.relu = nn.ReLU()
+        self.fc2 = nn.Linear(50, 10)
+        self.relu = nn.ReLU()
+        self.fc3 = nn.Linear(10, 1)
+        self.linear = nn.Identity()
+
+    def forward(self, x):
+        x = self.fc1(x)
+        x = self.relu(x)
+        x = self.fc2(x)
+        x = self.relu(x)
+        x = self.fc3(x)
+        x = self.linear(x)
+        return x
+
+# Define the neural network
+class RegressionModel(nn.Module):
+    def __init__(self, input_size):
+        super().__init__()
+        self.fc1 = nn.Linear(input_size, 64)
+        self.relu = nn.ReLU()
+        self.fc2 = nn.Linear(64, 32)
+        self.fc3 = nn.Linear(32, 1)
+
[…]

### 2024-02-02 NN/back1.py

@@ -1,351 +1,0 @@
-from matplotlib import pyplot as plt
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from sklearn.model_selection import train_test_split
-from sklearn.preprocessing import StandardScaler
-import pandas as pd
-import numpy as np
-import torch.nn as nn
-from sklearn.metrics import r2_score
-from tabulate import tabulate
-
-# Define the neural network with ReLU activation function
-class ReLUModel(nn.Module):
-    def __init__(self, input_size):
-        super().__init__()
-        self.fc1 = nn.Linear(input_size, 10)
-        self.relu = nn.ReLU()
-        self.fc2 = nn.Linear(10, 1)
-        self.linear = nn.Identity()
-
-    def forward(self, x):
-        x = self.fc1(x)
-        x = self.relu(x)
-        x = self.fc2(x)
-        x = self.linear(x)
-        return x
-
-# Define the neural network with Tanh activation function
-class TanhModel(nn.Module):
-    def __init__(self, input_size):
-        super().__init__()
-        self.fc1 = nn.Linear(input_size, 10)
-        self.tanh = nn.Tanh()
-        self.fc2 = nn.Linear(10, 1)
-        self.linear = nn.Identity()
-
-    def forward(self, x):
-        x = self.fc1(x)
-        x = self.tanh(x)
-        x = self.fc2(x)
-        x = self.linear(x)
-        return x
-
-# Define the neural network with Tanh activation function
-class ReLUReLUModel(nn.Module):
-    def __init__(self, input_size):
-        super().__init__()
-        self.fc1 = nn.Linear(input_size, 50)
-        self.relu = nn.ReLU()
-        self.fc2 = nn.Linear(50, 10)
-        self.relu = nn.ReLU()
-        self.fc3 = nn.Linear(10, 1)
-        self.linear = nn.Identity()
-
-    def forward(self, x):
-        x = self.fc1(x)
-        x = self.relu(x)
-        x = self.fc2(x)
-        x = self.relu(x)
-        x = self.fc3(x)
-        x = self.linear(x)
-        return x
-
-# Define the neural network
-class RegressionModel(nn.Module):
-    def __init__(self, input_size):
-        super().__init__()
-        self.fc1 = nn.Linear(input_size, 64)
-        self.relu = nn.ReLU()
-        self.fc2 = nn.Linear(64, 32)
-        self.fc3 = nn.Linear(32, 1)
-
[…]

### 2024-02-02 NN/model.py

@@ -369,10 +369,10 @@ answer = input(f"Enter the number of repeating predictions [{num_repeats}]:")
 if answer: 
    num_repeats = int(answer)
 
-# Load data from CSV file into a DataFrame
-data = pd.read_csv('data.csv')
+# Load data from data CSV file in data folder
+data = pd.read_csv(os.path.join('data','data.csv'))
 
-# Input and output 
+# Input features and output 
 inputs = ['flow_rate', 'conc_nano', 'Kfluid', 'heat_flux', 'X_D']
 output = 'HTC'
 # Read data into X and y

### 2024-02-02 NN/model.py
commit

@@ -14,12 +14,15 @@ import os
 num_epochs = 300 
 num_repeats = 5
 # num_repeats shows the number of times to repeat the experiment to get its average values
-random_seed = 123
-torch.manual_seed(random_seed)
-np.random.seed(random_seed)
-# changing random_seed generates different results for each run 
-# The same random_seed gets the same results in each run
+model_seed = 123 # it is used for random_state of models
+# changing model_seed generates different results for each run for each model
+# The same model_seed produces the same results in each run which is good for reporducability of experiments
 # Dont change it if you want to reproduce the same results
+data_seed = 123 # it is used for random_state of splitting data into source and train sets
+# changing it creates different source and train sets.
+# Since the number of data is low changing it can largely affect the results
+torch.manual_seed(model_seed)
+np.random.seed(model_seed)
 learning_rate = 0.05
 # The learnign rate used in ANN
 hidden_size1 = 10
@@ -198,9 +201,9 @@ def backward_feature_elimination(model_class, data, inputs, output):
     # Remove extra columns
     data = data.drop([output, 'HTC_ANN1', 'HTC_ANN2'], axis=1).copy()
     X = data[inputs]
-    # it uses num_repeats, num_epochs and random_seed as global variables
+    # it uses num_repeats, num_epochs and model_seed as global variables
     # use _ for output of repeat_fit_model, which you don't need to use here
-    mean_r2, _, _, _, _,_ = repeat_fit_model(num_repeats, X, y, num_epochs, random_seed)
+    mean_r2, _, _, _, _,_ = repeat_fit_model(num_repeats, X, y, num_epochs)
     best_r2 = mean_r2
     print("Using all features")
     print("Features:", inputs)
@@ -214,7 +217,7 @@ def backward_feature_elimination(model_class, data, inputs, output):
             # Selet other features except for current feature
             features = [f for f in candidates if f != feature]
             X = data[features]
-            mean_r2, _, _, _,_,_ = repeat_fit_model(num_repeats, X, y, num_epochs, random_seed)
+            mean_r2, _, _, _,_,_ = repeat_fit_model(num_repeats, X, y, num_epochs)
             results[feature] = mean_r2
             print("---------------------------------------")
             # Results of removing the feature
@@ -269,7 +272,7 @@ def forward_feature_selection(model_class, data, inputs, output):
                 features = [feature] + candidates 
 
[…]

### 2024-07-21 NN/plots.py
commit

@@ -1,0 +1,97 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+def comparison_chart():
+    # Sample experimental and predicted data
+    experimental_data = np.random.rand(50) * 100
+    predicted_data = experimental_data + np.random.randn(50) * 5
+
+    # Scatter plot
+    plt.figure(figsize=(8, 6))
+    plt.scatter(experimental_data, predicted_data, color='blue', label='Predictions')
+    plt.plot([0, 100], [0, 100], color='red', linestyle='--', label='Ideal Line')
+    plt.xlabel('Experimental Data')
+    plt.ylabel('Data Predicted by ANN')
+    plt.title('Comparison of Experimental Data and ANN Predictions')
+    plt.legend()
+    plt.grid(True)
+    plt.show()
+
+def mae_chart():
+    # Sample experimental and predicted data
+    experimental_data = np.random.rand(50) * 100
+    predicted_data = experimental_data + np.random.randn(50) * 5
+
+    # Mean Absolute Error
+    mae = np.abs(predicted_data - experimental_data)
+
+    # Bar chart
+    plt.figure(figsize=(8, 6))
+    plt.bar(range(len(mae)), mae, color='green')
+    plt.xlabel('Samples')
+    plt.ylabel('Absolute Error')
+    plt.title('Mean Absolute Error (MAE) Chart')
+    plt.grid(True)
+    plt.show()
+
+def correlation_plot():
+    # Sample experimental and predicted data
+    experimental_data = np.random.rand(50) * 100
+    predicted_data = experimental_data + np.random.randn(50) * 5
+
+    # Correlation Coefficient
+    correlation_coefficient = np.corrcoef(experimental_data, predicted_data)[0, 1]
+
+    # Scatter plot
+    plt.figure(figsize=(8, 6))
+    plt.scatter(experimental_data, predicted_data, color='blue', label=f'Correlation Coefficient: {correlation_coefficient:.2f}')
+    plt.plot([0, 100], [0, 100], color='red', linestyle='--', label='Ideal Line')
+    plt.xlabel('Experimental Data')
+    plt.ylabel('Data Predicted by ANN')
+    plt.title('Correlation Plot')
+    plt.legend()
+    plt.grid(True)
+    plt.show()
+
+def nanoparticle_concentration_effect():
+    # Sample concentrations and impedance modulus data
+    concentrations = np.linspace(0, 10, 10)
[…]

### 2024-07-21 NN/plots.py
commit

@@ -1,12 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
+import pandas as pd
 
-def comparison_chart():
-    # Sample experimental and predicted data
-    experimental_data = np.random.rand(50) * 100
-    predicted_data = experimental_data + np.random.randn(50) * 5
-
-    # Scatter plot
+def comparison_chart(experimental_data, predicted_data):
     plt.figure(figsize=(8, 6))
     plt.scatter(experimental_data, predicted_data, color='blue', label='Predictions')
     plt.plot([0, 100], [0, 100], color='red', linestyle='--', label='Ideal Line')
@@ -17,15 +13,8 @@ def comparison_chart():
     plt.grid(True)
     plt.show()
 
-def mae_chart():
-    # Sample experimental and predicted data
-    experimental_data = np.random.rand(50) * 100
-    predicted_data = experimental_data + np.random.randn(50) * 5
-
-    # Mean Absolute Error
+def mae_chart(experimental_data, predicted_data):
     mae = np.abs(predicted_data - experimental_data)
-
-    # Bar chart
     plt.figure(figsize=(8, 6))
     plt.bar(range(len(mae)), mae, color='green')
     plt.xlabel('Samples')
@@ -34,15 +23,8 @@ def mae_chart():
     plt.grid(True)
     plt.show()
 
-def correlation_plot():
-    # Sample experimental and predicted data
-    experimental_data = np.random.rand(50) * 100
-    predicted_data = experimental_data + np.random.randn(50) * 5
-
-    # Correlation Coefficient
+def correlation_plot(experimental_data, predicted_data):
     correlation_coefficient = np.corrcoef(experimental_data, predicted_data)[0, 1]
-
-    # Scatter plot
     plt.figure(figsize=(8, 6))
     plt.scatter(experimental_data, predicted_data, color='blue', label=f'Correlation Coefficient: {correlation_coefficient:.2f}')
     plt.plot([0, 100], [0, 100], color='red', linestyle='--', label='Ideal Line')
@@ -53,12 +35,7 @@ def correlation_plot():
     plt.grid(True)
     plt.show()
 
-def nanoparticle_concentration_effect():
-    # Sample concentrations and impedance modulus data
-    concentrations = np.linspace(0, 10, 10)
-    impedance_modulus = 100 + 10 * concentrations - (concentrations ** 2)
-
-    # Line plot
[…]

### 2024-07-21 NN/model.py
commit

@@ -252,6 +252,54 @@ def generate_latax_table(table, caption="table", label=""):
 ############################ Feature Selection ####################
 # Selects the best combination of features by removing features one by one
 # Search about Backward Feature Elimination 
+# Sensitivity Analysis Functions
+
+def node_deletion_sensitivity_analysis(model_class, data, inputs, output):
+    y = data[output]
+    base_model_r2, _, _, _, _ = repeat_fit_model(num_repeats, data[inputs], y, num_epochs, hidden_sizes)
+    sensitivities = {}
+    
+    for input_feature in inputs:
+        reduced_inputs = [f for f in inputs if f != input_feature]
+        reduced_r2, _, _, _, _ = repeat_fit_model(num_repeats, data[reduced_inputs], y, num_epochs, hidden_sizes)
+        sensitivity = base_model_r2 - reduced_r2
+        sensitivities[input_feature] = sensitivity
+    
+    sensitivity_table = pd.DataFrame(list(sensitivities.items()), columns=['Feature', 'Sensitivity'])
+    return sensitivity_table
+
+def weight_analysis(model_class, data, inputs, output):
+    y = data[output]
+    X_train, X_test, y_train, y_test = train_test_split(data[inputs], y, test_size=0.2, random_state=data_seed)
+    input_size = X_train.shape[1]
+    model = model_class(input_size, hidden_sizes)
+    fit_model(model_class, X_train, X_test, y_train, y_test, num_epochs, hidden_sizes, activations)
+
+    weight_importances = {}
+    with torch.no_grad():
+        for i, feature in enumerate(inputs):
+            importance = np.abs(model.hidden_layers[0].weight[:, i].numpy()).mean()
+            weight_importances[feature] = importance
+    
+    weight_table = pd.DataFrame(list(weight_importances.items()), columns=['Feature', 'Weight Importance'])
+    return weight_table
+
+def jackknife_sensitivity_analysis(model_class, data, inputs, output):
+    y = data[output]
+    base_model_r2, _, _, _, _ = repeat_fit_model(num_repeats, data[inputs], y, num_epochs, hidden_sizes)
+    sensitivities = {}
+
+    for input_feature in inputs:
+        reduced_inputs = [f for f in inputs if f != input_feature]
+        reduced_r2, _, _, _, _ = repeat_fit_model(num_repeats, data[reduced_inputs], y, num_epochs, hidden_sizes)
[…]

### 2024-07-21 NN/model.py
commit

@@ -46,9 +46,98 @@ hidden_sizes = [15, 10, 3 ]
 activations = [nn.ReLU(), nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
 
 list_hidden_sizes = [[15, 10, 3], [8, 8, 2], [5, 4, 2]]
-
-
 normalization_type = "z_score"
+
+##################### New Models
+class MLP(nn.Module):
+    def __init__(self, input_size, hidden_sizes):
+        super().__init__()
+        self.hidden_layers = nn.ModuleList()
+        self.activations = activations if activations is not None else []
+
+        self.hidden_layers.append(nn.Linear(input_size, hidden_sizes[0]))
+        for i in range(len(hidden_sizes) - 1):
+            self.hidden_layers.append(nn.Linear(hidden_sizes[i], hidden_sizes[i + 1]))
+        self.hidden_layers.append(nn.Linear(hidden_sizes[-1], 1))
+
+    def forward(self, x):
+        for i, layer in enumerate(self.hidden_layers):
+            x = layer(x)
+            act = self.activations[-1]
+            if i < len(self.activations) and self.activations[i] is not None:
+                act = self.activations[i]
+            x = act(x)
+        return x
+
+class RBFN(nn.Module):
+    def __init__(self, input_size, hidden_size):
+        super().__init__()
+        self.hidden = nn.Linear(input_size, hidden_size)
+        self.output = nn.Linear(hidden_size, 1)
+        self.hidden_size = hidden_size
+
+    def forward(self, x):
+        x = torch.exp(-torch.cdist(x, self.hidden.weight.data)**2 / 2)
+        x = self.output(x)
+        return x
+
+class GRNN(nn.Module):
+    def __init__(self, input_size, hidden_size):
+        super().__init__()
+        self.hidden = nn.Linear(input_size, hidden_size)
+        self.output = nn.Linear(hidden_size, 1)
+        self.hidden_size = hidden_size
+
+    def forward(self, x):
+        x = torch.exp(-torch.cdist(x, self.hidden.weight.data)**2 / 2)
+        x = self.output(x)
+        return x
+
+class FFNN(nn.Module):
+    def __init__(self, input_size, hidden_sizes):
+        super().__init__()
+        self.hidden_layers = nn.ModuleList()
+        self.activations = activations if activations is not None else []
+
+        self.hidden_layers.append(nn.Linear(input_size, hidden_sizes[0]))
[…]

### 2024-07-21 NN/model.py
commit

@@ -703,7 +703,7 @@ while True:
         print("------------ backward feature elimination ---------------")
         print(backward_table)
 
-        backward_table_latex = generate_latex_table(backward_table, caption="Results of Backward Feature Elimination", label="backward")
+        backward_table_latex = generate_latax_table(backward_table, caption="Results of Backward Feature Elimination", label="backward")
         with open(os.path.join("tables", "backward_table_latex.txt"), 'w') as f:
             print(backward_table_latex, file=f)
 

### 2024-07-21 NN/model.py
commit

@@ -49,41 +49,49 @@ list_hidden_sizes = [[15, 10, 3], [8, 8, 2], [5, 4, 2]]
 normalization_type = "z_score"
 
 ##################### New Models
-class MLP(nn.Module):
+class RBFNSimple(nn.Module):
     def __init__(self, input_size, hidden_sizes):
         super().__init__()
-        self.hidden_layers = nn.ModuleList()
-        self.activations = activations if activations is not None else []
-
-        self.hidden_layers.append(nn.Linear(input_size, hidden_sizes[0]))
-        for i in range(len(hidden_sizes) - 1):
-            self.hidden_layers.append(nn.Linear(hidden_sizes[i], hidden_sizes[i + 1]))
-        self.hidden_layers.append(nn.Linear(hidden_sizes[-1], 1))
-
-    def forward(self, x):
-        for i, layer in enumerate(self.hidden_layers):
-            x = layer(x)
-            act = self.activations[-1]
-            if i < len(self.activations) and self.activations[i] is not None:
-                act = self.activations[i]
-            x = act(x)
-        return x
-
-class RBFN(nn.Module):
-    def __init__(self, input_size, hidden_size):
-        super().__init__()
+        hidden_size = hidden_sizes[0]
         self.hidden = nn.Linear(input_size, hidden_size)
         self.output = nn.Linear(hidden_size, 1)
         self.hidden_size = hidden_size
 
     def forward(self, x):
+        # Using radial basis function
         x = torch.exp(-torch.cdist(x, self.hidden.weight.data)**2 / 2)
+        x = self.output(x)
+        return x
+
+
+class RBFN(nn.Module):
+    def __init__(self, input_size, hidden_sizes):
+        super().__init__()
+        hidden_size1 = hidden_sizes[0]
+        hidden_size2 = hidden_sizes[1] if len(hidden_sizes) > 1 else hidden_size1
+
+        self.hidden1 = nn.Linear(input_size, hidden_size1)
+        self.hidden2 = nn.Linear(hidden_size1, hidden_size2)
+        self.output = nn.Linear(hidden_size2, 1)
+
+        self.activation = nn.ReLU()
+
+    def forward(self, x):
+        # First hidden layer with radial basis function
+        x = torch.exp(-torch.cdist(x, self.hidden1.weight.data)**2 / 2)
+        x = self.activation(x)
+        
+        # Second hidden layer with radial basis function
[…]

### 2024-07-22 NN/tables/forward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                            &     R2 \\
\hline
 ['X_D1']                                                            &  14.09 \\
 ['flow_rate2']                                                      &  38.24 \\
 ['conc_nano2']                                                      &  11.24 \\
 ['Kfluid2']                                                         &  62.95 \\
 ['heat_flux2']                                                      &   0.14 \\
 ['flow_rate1', 'Kfluid2']                                           &  63.47 \\
 ['conc_nano1', 'Kfluid2']                                           &  63.88 \\
 ['Kfluid1', 'Kfluid2']                                              &  62.25 \\
 ['heat_flux1', 'Kfluid2']                                           &  77.7  \\
 ['X_D1', 'Kfluid2']                                                 &  76.02 \\
 ['flow_rate2', 'Kfluid2']                                           & -31.69 \\
 ['conc_nano2', 'Kfluid2']                                           &  86.62 \\
 ['heat_flux2', 'Kfluid2']                                           &  76.09 \\
 ['X_D2', 'Kfluid2']                                                 &  78.17 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2']                             &  76.79 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2']                             &  87.83 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2']                                &  88.24 \\
 ['heat_flux1', 'Kfluid2', 'conc_nano2']                             &  91.58 \\
 ['X_D1', 'Kfluid2', 'conc_nano2']                                   &  82.59 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2']                             &  53.86 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2']                             &  75.43 \\
 ['X_D2', 'Kfluid2', 'conc_nano2']                                   &  64.89 \\
 ['flow_rate1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  93.27 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  76.38 \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                  &  92.71 \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  86.97 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  74.46 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  81.11 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  63.44 \\
 ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  83.2  \\
 ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']    &  66.6  \\
 ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  82.41 \\
 ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  49.69 \\
 ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  61.91 \\
 ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  70.43 \\
\hline
\end{tabular}
            \caption{Results of Forward Feature Selection for different features}
            \label{table-forward}
        \end{table*}

### 2024-07-22 NN/model.py

@@ -11,12 +11,10 @@ from sklearn.metrics import r2_score
 from tabulate import tabulate
 import os
 
-# num_epochs = 500 
-list_epochs = [10, 20 , 30, 40]
-
+list_epochs = [200, 100, 50 , 20]
+best_epochs = 100 
 
 exp_df = pd.DataFrame()
-#num_epochs = 300 
 
 num_repeats = 5
 # num_repeats shows the number of times to repeat the experiment to get its average values
@@ -45,61 +43,50 @@ hidden_sizes = [15, 10, 3 ]
 # nn.ReLU(), nn.Tanh(), nn.Identity()
 activations = [nn.ReLU(), nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
 
-list_hidden_sizes = [[15, 10, 3], [8, 8, 2], [5, 4, 2]]
+list_hidden_sizes = [[15, 10, 3], [8, 4], [15, 5]]
 normalization_type = "z_score"
 
 ##################### New Models
-class RBFNSimple(nn.Module):
-    def __init__(self, input_size, hidden_sizes):
-        super().__init__()
+class RBFN(nn.Module):
+    def __init__(self, input_size, hidden_size):
+        super(RBFN, self).__init__()
         hidden_size = hidden_sizes[0]
         self.hidden = nn.Linear(input_size, hidden_size)
         self.output = nn.Linear(hidden_size, 1)
         self.hidden_size = hidden_size
 
-    def forward(self, x):
-        # Using radial basis function
-        x = torch.exp(-torch.cdist(x, self.hidden.weight.data)**2 / 2)
-        x = self.output(x)
-        return x
-
-
-class RBFN(nn.Module):
-    def __init__(self, input_size, hidden_sizes):
-        super().__init__()
-        hidden_size1 = hidden_sizes[0]
-        hidden_size2 = hidden_sizes[1] if len(hidden_sizes) > 1 else hidden_size1
-
-        self.hidden1 = nn.Linear(input_size, hidden_size1)
-        self.hidden2 = nn.Linear(hidden_size1, hidden_size2)
-        self.output = nn.Linear(hidden_size2, 1)
-
-        self.activation = nn.ReLU()
+        self.hidden_layers = nn.ModuleList()
+        self.hidden_layers.append(self.hidden)
+        self.hidden_layers.append(self.output)
 
     def forward(self, x):
-        # First hidden layer with radial basis function
[…]

### 2024-07-22 NN/tables/backward.tex

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                           &    R2 \\
\hline
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
 ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 88.38 \\
 ['flow_rate1', 'conc_nano1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']    & 58.85 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 67.6  \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2'] & 82.77 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 57.26 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 74.21 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']    & 55.88 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']       & 64.76 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2'] & 73.37 \\
 ['Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.52 \\
 ['flow_rate1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                  & 67.85 \\
 ['flow_rate1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 81.99 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']               & 74.67 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.17 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 16.53 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']                  & 74.26 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']                     & 66.81 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2']               & 69.09 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}

### 2024-07-22 NN/tables/backward.tex
commit

@@
 \hline
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
+ ['flow\_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
  ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\

### 2024-07-22 NN/model.py

@@ -335,6 +335,11 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
 
 ################ Generate Latex Tables
 def generate_latax_table(table, caption="table", label=""):
+    def escape_latex_special_chars(text):
+        return text.replace('_', '\\_')
+
+    table = table.applymap(escape_latex_special_chars)
+
     latex_table=tabulate(table, headers='keys', 
             tablefmt='latex_raw', showindex=False)
     table_env = f"""

### 2024-07-22 NN/tables/backward.tex
commit

--- 2024-07-22 NN/tables/backward.tex
@@
 \hline
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
- ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 88.38 \\
- ['flow_rate1', 'conc_nano1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']    & 58.85 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 67.6  \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2'] & 82.77 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 57.26 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 74.21 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']    & 55.88 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']       & 64.76 \\
- ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2'] & 73.37 \\
- ['Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.52 \\
- ['flow_rate1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                  & 67.85 \\
- ['flow_rate1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 81.99 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']               & 74.67 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.17 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 16.53 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']                  & 74.26 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']                     & 66.81 \\
- ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2']               & 69.09 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2'] & 82.69 \\
+ ['conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 62.45 \\
+ ['flow\_rate1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 81.63 \\
+ ['flow\_rate1', 'conc\_nano1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']            & 73.64 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 72.94 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']          & 67.45 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 68.03 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 76.57 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'heat\_flux2', 'X\_D2']            & 38.28 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'X\_D2']                & 69.39 \\
+ ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2']          & 81.61 \\
 \hline

### 2024-07-22 NN/tables/forward.tex
commit

@@
 \hline
- ['X_D1']                                                            &  14.09 \\
- ['flow_rate2']                                                      &  38.24 \\
- ['conc_nano2']                                                      &  11.24 \\
- ['Kfluid2']                                                         &  62.95 \\
- ['heat_flux2']                                                      &   0.14 \\
- ['flow_rate1', 'Kfluid2']                                           &  63.47 \\
- ['conc_nano1', 'Kfluid2']                                           &  63.88 \\
- ['Kfluid1', 'Kfluid2']                                              &  62.25 \\
- ['heat_flux1', 'Kfluid2']                                           &  77.7  \\
- ['X_D1', 'Kfluid2']                                                 &  76.02 \\
- ['flow_rate2', 'Kfluid2']                                           & -31.69 \\
- ['conc_nano2', 'Kfluid2']                                           &  86.62 \\
- ['heat_flux2', 'Kfluid2']                                           &  76.09 \\
- ['X_D2', 'Kfluid2']                                                 &  78.17 \\
- ['flow_rate1', 'Kfluid2', 'conc_nano2']                             &  76.79 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2']                             &  87.83 \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2']                                &  88.24 \\
- ['heat_flux1', 'Kfluid2', 'conc_nano2']                             &  91.58 \\
- ['X_D1', 'Kfluid2', 'conc_nano2']                                   &  82.59 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2']                             &  53.86 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2']                             &  75.43 \\
- ['X_D2', 'Kfluid2', 'conc_nano2']                                   &  64.89 \\
- ['flow_rate1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  93.27 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  76.38 \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                  &  92.71 \\
- ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  86.97 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  74.46 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  81.11 \\
- ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  63.44 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  83.2  \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']    &  66.6  \\
- ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  82.41 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  49.69 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  61.91 \\
- ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  70.43 \\
+ ['X\_D1']                                                                          & 14.85 \\
+ ['flow\_rate2']                                                                    & 27.69 \\
+ ['conc\_nano2']                                                                    & 11.15 \\
+ ['Kfluid2']                                                                        & 62.66 \\
+ ['heat\_flux2']                                                                    & -4.92 \\
+ ['flow\_rate1', 'Kfluid2']                                                         & 75.33 \\
+ ['conc\_nano1', 'Kfluid2']                                                         & 64.49 \\
+ ['Kfluid1', 'Kfluid2']                                                             & 67.9  \\
+ ['heat\_flux1', 'Kfluid2']                                                         & 74.3  \\
+ ['X\_D1', 'Kfluid2']                                                               & 67.3  \\
+ ['flow\_rate2', 'Kfluid2']                                                         &  9.94 \\
+ ['conc\_nano2', 'Kfluid2']                                                         & 87.59 \\
+ ['heat\_flux2', 'Kfluid2']                                                         & 56.8  \\
+ ['X\_D2', 'Kfluid2']                                                               & 67.59 \\
+ ['flow\_rate1', 'Kfluid2', 'conc\_nano2']                                          & 60.42 \\
+ ['conc\_nano1', 'Kfluid2', 'conc\_nano2']                                          & 78.36 \\
+ ['Kfluid1', 'Kfluid2', 'conc\_nano2']                                              & 79.88 \\
+ ['heat\_flux1', 'Kfluid2', 'conc\_nano2']                                          & 90.37 \\
+ ['X\_D1', 'Kfluid2', 'conc\_nano2']                                                & 84.51 \\
+ ['flow\_rate2', 'Kfluid2', 'conc\_nano2']                                          & 65.14 \\
+ ['heat\_flux2', 'Kfluid2', 'conc\_nano2']                                          & 57.1  \\
+ ['X\_D2', 'Kfluid2', 'conc\_nano2']                                                & 54.6  \\
+ ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 62.62 \\
+ ['conc\_nano1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 92.87 \\
+ ['Kfluid1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                               & 80.94 \\
+ ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                                 & 87.63 \\
+ ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 82.76 \\
+ ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                           & 55.75 \\
+ ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1']                                 & 75.43 \\
+ ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 49.56 \\
+ ['Kfluid1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                & 93.06 \\
+ ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                  & 87.49 \\
+ ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 69.35 \\
+ ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']            & 65.5  \\
+ ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1']                  & 64.18 \\
+ ['flow\_rate1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 84.19 \\
+ ['X\_D1', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1']       & 87.54 \\
+ ['flow\_rate2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 76.61 \\
+ ['heat\_flux2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1'] & 71.81 \\
+ ['X\_D2', 'Kfluid2', 'conc\_nano2', 'heat\_flux1', 'conc\_nano1', 'Kfluid1']       & 77.34 \\
 \hline

### 2024-07-22 NN/model.py

@@ -336,9 +336,10 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
 ################ Generate Latex Tables
 def generate_latax_table(table, caption="table", label=""):
     def escape_latex_special_chars(text):
+        text = str(text)
         return text.replace('_', '\\_')
 
-    table = table.applymap(escape_latex_special_chars)
+    table = table.map(escape_latex_special_chars)
 
     latex_table=tabulate(table, headers='keys', 
             tablefmt='latex_raw', showindex=False)

### 2024-07-22 NN/model.py
commit

@@ -343,14 +343,26 @@ def generate_latax_table(table, caption="table", label=""):
 
     latex_table=tabulate(table, headers='keys', 
             tablefmt='latex_raw', showindex=False)
+
+    column_format = "p{12cm}r"  # Adjust width as needed
+    # Replace the default column format with the desired one
+    latex_table = latex_table.replace('tabular}{l', f'tabular}}{{{column_format}}')
+
+    # Add \hline correctly
+    latex_table_lines = latex_table.splitlines()
+    latex_table_lines.insert(1, '\\hline')
+    latex_table_lines.append('\\hline')
+    latex_table = '\n'.join(latex_table_lines)
+   
     table_env = f"""
-        \\begin{{table*}}
-            \centering
-            {latex_table}
-            \caption{{{caption}}}
-            \label{{table-{label}}}
-        \end{{table*}}
-        """
+    \\begin{{table*}}
+        \\centering
+        {latex_table}
+        \\caption{{caption}}
+        \\label{{label}}
+    \\end{{table*}}
+    """
+
     return table_env
 
 ############################ Feature Selection ####################

### 2024-07-22 NN/model.py
commit

@@ -346,7 +346,7 @@ def generate_latax_table(table, caption="table", label=""):
 
     column_format = "p{12cm}r"  # Adjust width as needed
     # Replace the default column format with the desired one
-    latex_table = latex_table.replace('tabular}{l', f'tabular}}{{{column_format}}')
+    latex_table = latex_table.replace('tabular}{l', f'tabular}}{{{column_format}}}')
 
     # Add \hline correctly
     latex_table_lines = latex_table.splitlines()
@@ -358,8 +358,8 @@ def generate_latax_table(table, caption="table", label=""):
     \\begin{{table*}}
         \\centering
         {latex_table}
-        \\caption{{caption}}
-        \\label{{label}}
+        \\caption{{{caption}}}
+        \\label{{{label}}}
     \\end{{table*}}
     """
 
@@ -395,6 +395,7 @@ def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs
     variances = []
     _num_repeats = input("Number of repeat [10]:")
     _num_repeats = int(_num_repeats) if _num_repeats else 10
+    print("Please wait ...")
 
     for input_feature in inputs:
         reduced_inputs = [f for f in inputs if f != input_feature]

### 2024-07-22 NN/tables/backward.tex
commit

@@
         \centering
-            \begin{tabular}{lr}
+        \begin{tabular}{p{12cm}r}r}
+\hline
 \hline
@@
 \hline
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2'] & 82.69 \\
- ['conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 62.45 \\
- ['flow\_rate1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 81.63 \\
- ['flow\_rate1', 'conc\_nano1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']            & 73.64 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 72.94 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']          & 67.45 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'conc\_nano2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 68.03 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'Kfluid2', 'heat\_flux2', 'X\_D2']                & 76.57 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'heat\_flux2', 'X\_D2']            & 38.28 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'X\_D2']                & 69.39 \\
- ['flow\_rate1', 'conc\_nano1', 'Kfluid1', 'heat\_flux1', 'X\_D1', 'flow\_rate2', 'conc\_nano2', 'Kfluid2', 'heat\_flux2']          & 81.61 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
+ conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
+ flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
+ flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
+ flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
 \hline
 \end{tabular}
+\hline
         \caption{Results of Backward Feature Elimination}
-            \label{table-backward}
+        \label{backward}
     \end{table*}

### 2024-07-22 NN/model.py

@@ -431,7 +431,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
     candidates = inputs
     results = {}
     rows = [] # Rows of a table to show the features and the result
-    rows.append({"features": inputs, "R2": round(mean_r2,2)})
+    rows.append({"features": ",".join(inputs), "R2": round(mean_r2,2)})
     while(True):
         for feature in candidates:
             # Selet other features except for current feature
@@ -445,7 +445,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
             print("Removing:", feature)
             print("Features:", features)
             print("R2:", mean_r2)
-            rows.append({"features": features, "R2": round(mean_r2,2)})
+            rows.append({"features": ",".join(features), "R2": round(mean_r2,2)})
 
         max_results =  max(results.values())
         max_results_key = max(results, key=results.get)

### 2024-07-22 NN/tables/backward.tex
commit

@@
         \centering
-        \begin{tabular}{p{12cm}r}r}
-\hline
+        \begin{tabular}{lr}
 \hline
@@
 \hline
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
- conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
- flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
- flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
- flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 62.49 \\
+ conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 68.28 \\
+ flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.17 \\
+ flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 71.83 \\
+ flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 69.8  \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 64.05 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 88.72 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 69.93 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 46.61 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 56.93 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 68.77 \\
+ conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 70.72 \\
+ flow\_rate1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 81.63 \\
+ flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                     & 87.88 \\
+ flow\_rate1,conc\_nano1,Kfluid1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 80.33 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2                   & 84.17 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,Kfluid2,heat\_flux2,X\_D2                         & 81.33 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,heat\_flux2,X\_D2                     & 26.72 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,X\_D2                         & 61.71 \\
+ flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2                   & 76.7  \\
 \hline
 \end{tabular}
-\hline
         \caption{Results of Backward Feature Elimination}

### 2024-07-22 NN/tables/forward.tex
commit

--- 2024-07-22 NN/tables/forward.tex
@@
 \hline
- ['X_D1']                                                            &  14.09 \\
- ['flow_rate2']                                                      &  38.24 \\
- ['conc_nano2']                                                      &  11.24 \\
- ['Kfluid2']                                                         &  62.95 \\
- ['heat_flux2']                                                      &   0.14 \\
- ['flow_rate1', 'Kfluid2']                                           &  63.47 \\
- ['conc_nano1', 'Kfluid2']                                           &  63.88 \\
- ['Kfluid1', 'Kfluid2']                                              &  62.25 \\
- ['heat_flux1', 'Kfluid2']                                           &  77.7  \\
- ['X_D1', 'Kfluid2']                                                 &  76.02 \\
- ['flow_rate2', 'Kfluid2']                                           & -31.69 \\
- ['conc_nano2', 'Kfluid2']                                           &  86.62 \\
- ['heat_flux2', 'Kfluid2']                                           &  76.09 \\
- ['X_D2', 'Kfluid2']                                                 &  78.17 \\
- ['flow_rate1', 'Kfluid2', 'conc_nano2']                             &  76.79 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2']                             &  87.83 \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2']                                &  88.24 \\
- ['heat_flux1', 'Kfluid2', 'conc_nano2']                             &  91.58 \\
- ['X_D1', 'Kfluid2', 'conc_nano2']                                   &  82.59 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2']                             &  53.86 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2']                             &  75.43 \\
- ['X_D2', 'Kfluid2', 'conc_nano2']                                   &  64.89 \\
- ['flow_rate1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  93.27 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  76.38 \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                  &  92.71 \\
- ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  86.97 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  74.46 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1']               &  81.11 \\
- ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1']                     &  63.44 \\
- ['conc_nano1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  83.2  \\
- ['Kfluid1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']    &  66.6  \\
- ['X_D1', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  82.41 \\
- ['flow_rate2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  49.69 \\
- ['heat_flux2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1'] &  61.91 \\
- ['X_D2', 'Kfluid2', 'conc_nano2', 'heat_flux1', 'flow_rate1']       &  70.43 \\
+ X\_D1                                                         & 15.01 \\
+ flow\_rate2                                                   & 34.3  \\
+ conc\_nano2                                                   & 10.78 \\
+ Kfluid2                                                       & 49.29 \\
+ heat\_flux2                                                   & -8.26 \\
+ flow\_rate1,Kfluid2                                           & 52.94 \\
+ conc\_nano1,Kfluid2                                           & 50.8  \\
+ Kfluid1,Kfluid2                                               & 47.57 \\
+ heat\_flux1,Kfluid2                                           & 52.31 \\
+ X\_D1,Kfluid2                                                 & 62.32 \\
+ flow\_rate2,Kfluid2                                           & 29.14 \\
+ conc\_nano2,Kfluid2                                           & 61.05 \\
+ heat\_flux2,Kfluid2                                           & 66.61 \\
+ X\_D2,Kfluid2                                                 & 53.44 \\
+ flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
+ conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
+ Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
+ heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
+ X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
+ flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
+ conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
+ X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
+ flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
+ conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
+ Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
+ heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
+ X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
+ flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
+ conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
+ conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
+ Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
+ heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
+ X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
+ flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
+ conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
+ Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
+ heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
+ X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
+ flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
+ conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
 \hline
@@
         \caption{Results of Forward Feature Selection for different features}
-            \label{table-forward}
+        \label{forward}
     \end{table*}

### 2024-07-22 NN/model.py

@@ -337,21 +337,17 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
 def generate_latax_table(table, caption="table", label=""):
     def escape_latex_special_chars(text):
         text = str(text)
-        return text.replace('_', '\\_')
+        return (text.replace('_', '\\_')
+                .replace('[', '\\[')
+                .replace(']', '\\]'))
 
     table = table.map(escape_latex_special_chars)
 
     latex_table=tabulate(table, headers='keys', 
             tablefmt='latex_raw', showindex=False)
 
-    column_format = "p{12cm}r"  # Adjust width as needed
-    # Replace the default column format with the desired one
-    latex_table = latex_table.replace('tabular}{l', f'tabular}}{{{column_format}}}')
-
     # Add \hline correctly
     latex_table_lines = latex_table.splitlines()
-    latex_table_lines.insert(1, '\\hline')
-    latex_table_lines.append('\\hline')
     latex_table = '\n'.join(latex_table_lines)
    
     table_env = f"""
@@ -501,7 +497,7 @@ def forward_feature_selection(model_class, data, inputs, output, num_epochs):
             print("Adding feature ", feature)
             print("Features:", features)
             print("R2:", mean_r2)
-            rows.append({"features": features, "R2": round(mean_r2,2)})
+            rows.append({"features": ",".join(features), "R2": round(mean_r2,2)})
 
         max_results =  max(results.values())
         max_results_key = max(results, key=results.get)
@@ -666,7 +662,7 @@ if answer != "0":
                         "R2": round(mean_r2,1), 
                         "MSE": round(mean_mse,2),
                         "R2 std": round(std_r2, 1),
-                        "R2 List:": [round(x, 1) for x in r2_list],
+                        "R2 List": [round(x, 1) for x in r2_list],
                         "hidden sizes": hidden_sizes,
                         "total hs": total_nodes,
                         "epochs": num_epochs,
@@ -678,7 +674,8 @@ if answer != "0":
     # Sort methods by R2
     results_table = results_table.sort_values(by = "R2", ascending=False)
     # Create and save latex code for table
-    results_table_latex = generate_latax_table(results_table, 
+    latex_table = results_table.drop(columns=["R2 List"])
+    results_table_latex = generate_latax_table(latex_table, 
             caption="Results of different models", label="models")
     with open(os.path.join("tables", "results.tex"), 'w') as f:
         print(results_table_latex, file=f)

### 2024-07-22 NN/tables/backward.tex
commit

--- 2024-07-22 NN/tables/backward.tex
@@
 \hline
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
- conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
- flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
- flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
- flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
+ conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
+ flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
+ flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
+ flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
+ flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
 \hline
 \end{tabular}
-\hline
         \caption{Results of Backward Feature Elimination}

### 2024-07-22 NN/tables/forward.tex
commit

@@
 \hline
- X\_D1                                                         & 15.01 \\
- flow\_rate2                                                   & 34.3  \\
- conc\_nano2                                                   & 10.78 \\
- Kfluid2                                                       & 49.29 \\
- heat\_flux2                                                   & -8.26 \\
- flow\_rate1,Kfluid2                                           & 52.94 \\
- conc\_nano1,Kfluid2                                           & 50.8  \\
- Kfluid1,Kfluid2                                               & 47.57 \\
- heat\_flux1,Kfluid2                                           & 52.31 \\
- X\_D1,Kfluid2                                                 & 62.32 \\
- flow\_rate2,Kfluid2                                           & 29.14 \\
- conc\_nano2,Kfluid2                                           & 61.05 \\
- heat\_flux2,Kfluid2                                           & 66.61 \\
- X\_D2,Kfluid2                                                 & 53.44 \\
- flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
- conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
- Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
- heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
- X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
- flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
- conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
- X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
- flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
- conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
- conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
+ X\_D1                                                                & 14.85 \\
+ flow\_rate2                                                          & 27.69 \\
+ conc\_nano2                                                          & 11.15 \\
+ Kfluid2                                                              & 62.66 \\
+ heat\_flux2                                                          & -4.92 \\
+ flow\_rate1, Kfluid2                                                 & 75.33 \\
+ conc\_nano1, Kfluid2                                                 & 64.49 \\
+ Kfluid1, Kfluid2                                                     & 67.9  \\
+ heat\_flux1, Kfluid2                                                 & 74.3  \\
+ X\_D1, Kfluid2                                                       & 67.3  \\
+ flow\_rate2, Kfluid2                                                 &  9.94 \\
+ conc\_nano2, Kfluid2                                                 & 87.59 \\
+ heat\_flux2, Kfluid2                                                 & 56.8  \\
+ X\_D2, Kfluid2                                                       & 67.59 \\
+ flow\_rate1, Kfluid2, conc\_nano2                                    & 60.42 \\
+ conc\_nano1, Kfluid2, conc\_nano2                                    & 78.36 \\
+ Kfluid1, Kfluid2, conc\_nano2                                        & 79.88 \\
+ heat\_flux1, Kfluid2, conc\_nano2                                    & 90.37 \\
+ X\_D1, Kfluid2, conc\_nano2                                          & 84.51 \\
+ flow\_rate2, Kfluid2, conc\_nano2                                    & 65.14 \\
+ heat\_flux2, Kfluid2, conc\_nano2                                    & 57.1  \\
+ X\_D2, Kfluid2, conc\_nano2                                          & 54.6  \\
+ flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1                       & 62.62 \\
+ conc\_nano1, Kfluid2, conc\_nano2, heat\_flux1                       & 92.87 \\
+ Kfluid1, Kfluid2, conc\_nano2, heat\_flux1                           & 80.94 \\
+ X\_D1, Kfluid2, conc\_nano2, heat\_flux1                             & 87.63 \\
+ flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1                       & 82.76 \\
+ heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1                       & 55.75 \\
+ X\_D2, Kfluid2, conc\_nano2, heat\_flux1                             & 75.43 \\
+ flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 49.56 \\
+ Kfluid1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1              & 93.06 \\
+ X\_D1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1                & 87.49 \\
+ flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 69.35 \\
+ heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1          & 65.5  \\
+ X\_D2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1                & 64.18 \\
+ flow\_rate1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 84.19 \\
+ X\_D1, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1       & 87.54 \\
+ flow\_rate2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 76.61 \\
+ heat\_flux2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1 & 71.81 \\
+ X\_D2, Kfluid2, conc\_nano2, heat\_flux1, conc\_nano1, Kfluid1       & 77.34 \\
 \hline

### 2024-07-22 NN/model.py

@@ -337,9 +337,7 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
 def generate_latax_table(table, caption="table", label=""):
     def escape_latex_special_chars(text):
         text = str(text)
-        return (text.replace('_', '\\_')
-                .replace('[', '\\[')
-                .replace(']', '\\]'))
+        return text.replace('_', '\\_')
 
     table = table.map(escape_latex_special_chars)
 
@@ -427,7 +425,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
     candidates = inputs
     results = {}
     rows = [] # Rows of a table to show the features and the result
-    rows.append({"features": ",".join(inputs), "R2": round(mean_r2,2)})
+    rows.append({"features": ", ".join(inputs), "R2": round(mean_r2,2)})
     while(True):
         for feature in candidates:
             # Selet other features except for current feature
@@ -441,7 +439,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
             print("Removing:", feature)
             print("Features:", features)
             print("R2:", mean_r2)
-            rows.append({"features": ",".join(features), "R2": round(mean_r2,2)})
+            rows.append({"features": ", ".join(features), "R2": round(mean_r2,2)})
 
         max_results =  max(results.values())
         max_results_key = max(results, key=results.get)
@@ -497,7 +495,7 @@ def forward_feature_selection(model_class, data, inputs, output, num_epochs):
             print("Adding feature ", feature)
             print("Features:", features)
             print("R2:", mean_r2)
-            rows.append({"features": ",".join(features), "R2": round(mean_r2,2)})
+            rows.append({"features": ", ".join(features), "R2": round(mean_r2,2)})
 
         max_results =  max(results.values())
         max_results_key = max(results, key=results.get)

### 2024-07-22 NN/latex.py
commit

@@ -1,0 +1,54 @@
+import pandas as pd
+from tabulate import tabulate
+
+def generate_latax_table(table, caption="table", label=""):
+    # Function to escape LaTeX special characters
+    def escape_latex_special_chars(text):
+        return (text.replace('_', '\\_')
+                    .replace('%', '\\%')
+                    .replace('$', '\\$')
+                    .replace('&', '\\&')
+                    .replace('#', '\\#')
+                    .replace('{', '\\{')
+                    .replace('}', '\\}'))
+
+    # Apply the escaping function to all elements in the DataFrame
+    escaped_table = results_table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
+
+    # Process the first column for multirow
+    if "model" in escaped_table:
+        model_col = escaped_table['model'].tolist()
+        multirow_model_col = []
+        previous_model = None
+        row_span = 0
+
+        for i, model in enumerate(model_col):
+            if model == previous_model:
+                multirow_model_col.append('')
+                row_span += 1
+            else:
+                if row_span > 0:
+                    multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+                row_span = 0
+                multirow_model_col.append(model)
+            previous_model = model
+
+        if row_span > 0:
+            multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+
+        escaped_table['model'] = multirow_model_col
+
+    # Convert to LaTeX table using tabulate
+    latex_table = tabulate(escaped_table, headers='keys', tablefmt='latex_raw', showindex=False)
+
+
+    table_env = f"""
+    \\begin{{table*}}
+        \\centering
+        {latex_table}
+        \\caption{{{caption}}}
+        \\label{{{label}}}
+    \\end{{table*}}
+    """
+
+    return table_env

### 2024-07-22 NN/model.py

@@ -10,6 +10,7 @@ import torch.nn as nn
 from sklearn.metrics import r2_score
 from tabulate import tabulate
 import os
+from latex import *
 
 list_epochs = [200, 100, 50 , 20]
 best_epochs = 100 
@@ -332,30 +333,6 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
         plt.show()
     # Save the image of plot in images folder
     fig.savefig(os.path.join("images", file_name), format="png")
-
-################ Generate Latex Tables
-def generate_latax_table(table, caption="table", label=""):
-    def escape_latex_special_chars(text):
-        text = str(text)
-        return text.replace('_', '\\_')
-
-    table = table.map(escape_latex_special_chars)
-
-    latex_table=tabulate(table, headers='keys', 
-            tablefmt='latex_raw', showindex=False)
-
-    # Add \hline correctly
-    latex_table_lines = latex_table.splitlines()
-    latex_table = '\n'.join(latex_table_lines)
-   
-    table_env = f"""
-    \\begin{{table*}}
-        \\centering
-        {latex_table}
-        \\caption{{{caption}}}
-        \\label{{{label}}}
-    \\end{{table*}}
-    """
 
     return table_env
 

### 2024-07-22 NN/latex.py
commit

@@ -13,7 +13,7 @@ def generate_latax_table(table, caption="table", label=""):
                     .replace('}', '\\}'))
 
     # Apply the escaping function to all elements in the DataFrame
-    escaped_table = results_table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
+    escaped_table = table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
 
     # Process the first column for multirow
     if "model" in escaped_table:

### 2024-07-22 NN/model.py

@@ -334,8 +334,6 @@ def plot_results(predictions_np, y_test, title, file_name, show_plot=False):
     # Save the image of plot in images folder
     fig.savefig(os.path.join("images", file_name), format="png")
 
-    return table_env
-
 ############################ Feature Selection ####################
 # Selects the best combination of features by removing features one by one
 # Search about Backward Feature Elimination 

### 2024-07-22 NN/model.py
commit

@@ -646,8 +646,10 @@ if answer != "0":
     results_table = pd.DataFrame(data=results)
     # Sort methods by R2
     results_table = results_table.sort_values(by = "R2", ascending=False)
+    latex_table = results_table.copy()
     # Create and save latex code for table
-    latex_table = results_table.drop(columns=["R2 List"])
+    latex_table["R2 mean"] = latex_table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
+    latex_table = latex_table.drop(columns=["R2 List"])
     results_table_latex = generate_latax_table(latex_table, 
             caption="Results of different models", label="models")
     with open(os.path.join("tables", "results.tex"), 'w') as f:

### 2024-07-22 NN/model.py
commit

@@ -648,8 +648,8 @@ if answer != "0":
     results_table = results_table.sort_values(by = "R2", ascending=False)
     latex_table = results_table.copy()
     # Create and save latex code for table
-    latex_table["R2 mean"] = latex_table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
-    latex_table = latex_table.drop(columns=["R2 List"])
+    latex_table["R2"] = latex_table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
+    latex_table = latex_table.drop(columns=["R2 List","R2 std"])
     results_table_latex = generate_latax_table(latex_table, 
             caption="Results of different models", label="models")
     with open(os.path.join("tables", "results.tex"), 'w') as f:

### 2024-07-22 NN/latex.py
commit

@@ -1,7 +1,7 @@
 import pandas as pd
 from tabulate import tabulate
 
-def generate_latax_table(table, caption="table", label=""):
+def generate_latex_table(table, caption="table", label=""):
     # Function to escape LaTeX special characters
     def escape_latex_special_chars(text):
         return (text.replace('_', '\\_')
@@ -12,6 +12,10 @@ def generate_latax_table(table, caption="table", label=""):
                     .replace('{', '\\{')
                     .replace('}', '\\}'))
 
+    # Add the new column "R2 mean ± std" if it does not exist
+    if "R2" in table.columns and "R2 std" in table.columns:
+        table["R2 mean ± std"] = table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
+
     # Apply the escaping function to all elements in the DataFrame
     escaped_table = table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
 
@@ -21,27 +25,42 @@ def generate_latax_table(table, caption="table", label=""):
         multirow_model_col = []
         previous_model = None
         row_span = 0
+        latex_table_lines = []
 
-        for i, model in enumerate(model_col):
+        for i, row in escaped_table.iterrows():
+            model = row['model']
             if model == previous_model:
                 multirow_model_col.append('')
                 row_span += 1
             else:
                 if row_span > 0:
-                    multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+                    latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+                    latex_table_lines.append(['\\hline'] * len(row))
                 row_span = 0
                 multirow_model_col.append(model)
             previous_model = model
+            latex_table_lines.append(row.tolist())
 
         if row_span > 0:
-            multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+            latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+            latex_table_lines.append(['\\hline'] * len(row))
 
         escaped_table['model'] = multirow_model_col
 
     # Convert to LaTeX table using tabulate
[…]

### 2024-07-22 NN/model.py

@@ -650,7 +650,7 @@ if answer != "0":
     # Create and save latex code for table
     latex_table["R2"] = latex_table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
     latex_table = latex_table.drop(columns=["R2 List","R2 std"])
-    results_table_latex = generate_latax_table(latex_table, 
+    results_table_latex = generate_latex_table(latex_table, 
             caption="Results of different models", label="models")
     with open(os.path.join("tables", "results.tex"), 'w') as f:
         print(results_table_latex, file=f)
@@ -718,7 +718,7 @@ while True:
         print("------------ backward feature elimination ---------------")
         print(backward_table)
 
-        backward_table_latex = generate_latax_table(backward_table, caption="Results of Backward Feature Elimination", label="backward")
+        backward_table_latex = generate_latex_table(backward_table, caption="Results of Backward Feature Elimination", label="backward")
         with open(os.path.join("tables", "backward.tex"), 'w') as f:
             print(backward_table_latex, file=f)
 
@@ -728,7 +728,7 @@ while True:
         print("\n")
         print("------------ forward feature selection ---------------")
         print(forward_table)
-        forward_table_latex = generate_latax_table(forward_table, caption="Results of Forward Feature Selection for different features", label="forward")
+        forward_table_latex = generate_latex_table(forward_table, caption="Results of Forward Feature Selection for different features", label="forward")
         with open(os.path.join("tables", "forward.tex"), 'w') as f:
             print(forward_table_latex, file=f)
 
@@ -740,7 +740,7 @@ while True:
                 ascending=False)
         print("Most important features:")
         print(weight_table)
-        weight_table_latex = generate_latax_table(weight_table, caption="Results of Weight Analysis", label="weight_analysis")
+        weight_table_latex = generate_latex_table(weight_table, caption="Results of Weight Analysis", label="weight_analysis")
         with open(os.path.join("tables", "weight-analysis.tex"), 'w') as f:
             print(weight_table_latex, file=f)
 
@@ -752,7 +752,7 @@ while True:
         # Sort and display the most sensitive features
         jackknife_table = jackknife_table.sort_values(by='Sensitivity', ascending=False)
         print(jackknife_table)
-        jackknife_table_latex = generate_latax_table(jackknife_table, caption="Results of Jackknife Sensitivity Analysis", label="jackknife")
[…]

### 2024-07-22 NN/latex.py
commit

@@ -35,7 +35,7 @@ def generate_latex_table(table, caption="table", label=""):
             else:
                 if row_span > 0:
                     latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
-                    latex_table_lines.append(['\\hline'] * len(row))
+                    latex_table_lines.append([''] * len(row))  # placeholder for \hline
                 row_span = 0
                 multirow_model_col.append(model)
             previous_model = model
@@ -43,21 +43,21 @@ def generate_latex_table(table, caption="table", label=""):
 
         if row_span > 0:
             latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
-            latex_table_lines.append(['\\hline'] * len(row))
+            latex_table_lines.append([''] * len(row))  # placeholder for \hline
 
-        escaped_table['model'] = multirow_model_col
+    else:
+        latex_table_lines = escaped_table.values.tolist()
 
     # Convert to LaTeX table using tabulate
     latex_table = tabulate(latex_table_lines, headers=escaped_table.columns, tablefmt='latex_raw', showindex=False)
 
-    # Modify the column specifiers to use p{width} if needed
-    column_format = "lrrrrrrr"  # Adjust columns types based on the number of columns
-
-    # Replace the default column format with the desired one
-
-    # Insert \hline at the beginning
+    # Insert \hline at the beginning and after each group of model names
     latex_table_lines = latex_table.splitlines()
     latex_table_lines.insert(1, '\\hline')
+    for i in range(len(latex_table_lines) - 2, 1, -1):
+        if not latex_table_lines[i].startswith('\\multirow') and latex_table_lines[i+1].startswith('\\multirow'):
+            latex_table_lines.insert(i+1, '\\hline')
+
     latex_table = '\n'.join(latex_table_lines)
 
     # Wrap the table in a table environment
@@ -71,4 +71,17 @@ def generate_latex_table(table, caption="table", label=""):
     """
 
     return table_env
+
+# Example usage with a sample DataFrame
+results = [
[…]

### 2024-07-22 NN/latex.py
commit

@@ -12,10 +12,6 @@ def generate_latex_table(table, caption="table", label=""):
                     .replace('{', '\\{')
                     .replace('}', '\\}'))
 
-    # Add the new column "R2 mean ± std" if it does not exist
-    if "R2" in table.columns and "R2 std" in table.columns:
-        table["R2 mean ± std"] = table.apply(lambda row: f"{row['R2']} ± {row['R2 std']}", axis=1)
-
     # Apply the escaping function to all elements in the DataFrame
     escaped_table = table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
 
@@ -25,42 +21,27 @@ def generate_latex_table(table, caption="table", label=""):
         multirow_model_col = []
         previous_model = None
         row_span = 0
-        latex_table_lines = []
 
-        for i, row in escaped_table.iterrows():
-            model = row['model']
+        for i, model in enumerate(model_col):
             if model == previous_model:
                 multirow_model_col.append('')
                 row_span += 1
             else:
                 if row_span > 0:
-                    latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
-                    latex_table_lines.append([''] * len(row))  # placeholder for \hline
+                    multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
                 row_span = 0
                 multirow_model_col.append(model)
             previous_model = model
-            latex_table_lines.append(row.tolist())
 
         if row_span > 0:
-            latex_table_lines[-(row_span+1)][0] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
-            latex_table_lines.append([''] * len(row))  # placeholder for \hline
+            multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
 
-    else:
-        latex_table_lines = escaped_table.values.tolist()
+        escaped_table['model'] = multirow_model_col
 
     # Convert to LaTeX table using tabulate
-    latex_table = tabulate(latex_table_lines, headers=escaped_table.columns, tablefmt='latex_raw', showindex=False)
[…]

### 2024-07-22 NN/latex.py
commit

@@ -22,6 +22,7 @@ def generate_latex_table(table, caption="table", label=""):
         previous_model = None
         row_span = 0
 
+        row_spans = []
         for i, model in enumerate(model_col):
             if model == previous_model:
                 multirow_model_col.append('')
@@ -29,6 +30,7 @@ def generate_latex_table(table, caption="table", label=""):
             else:
                 if row_span > 0:
                     multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+                    row_spans.append(row_span)
                 row_span = 0
                 multirow_model_col.append(model)
             previous_model = model
@@ -40,6 +42,14 @@ def generate_latex_table(table, caption="table", label=""):
 
     # Convert to LaTeX table using tabulate
     latex_table = tabulate(escaped_table, headers='keys', tablefmt='latex_raw', showindex=False)
+
+    # Insert \hline at the beginning and after each group of model names
+    latex_table_lines = latex_table.splitlines()
+    for i in range(len(latex_table_lines) - 2, 1, -1):
+        if not latex_table_lines[i].startswith('\\multirow') and latex_table_lines[i+1].startswith('\\multirow'):
+            latex_table_lines.insert(i+1, '\\hline')
+
+    latex_table = '\n'.join(latex_table_lines)
 
 
     table_env = f"""

### 2024-07-22 NN/latex.py
commit

@@ -13,7 +13,7 @@ def generate_latex_table(table, caption="table", label=""):
                     .replace('}', '\\}'))
 
     # Apply the escaping function to all elements in the DataFrame
-    escaped_table = table.applymap(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
+    escaped_table = table.map(lambda x: escape_latex_special_chars(str(x)) if isinstance(x, str) else x)
 
     # Process the first column for multirow
     if "model" in escaped_table:
@@ -29,28 +29,19 @@ def generate_latex_table(table, caption="table", label=""):
                 row_span += 1
             else:
                 if row_span > 0:
-                    multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
-                    row_spans.append(row_span)
+                    multirow_model_col[-(row_span+1)] = f"\\hline\n\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+                    row_spans.append(i)
                 row_span = 0
                 multirow_model_col.append(model)
             previous_model = model
 
         if row_span > 0:
-            multirow_model_col[-(row_span+1)] = f"\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
+            multirow_model_col[-(row_span+1)] = f"\\hline\n\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
 
         escaped_table['model'] = multirow_model_col
 
     # Convert to LaTeX table using tabulate
     latex_table = tabulate(escaped_table, headers='keys', tablefmt='latex_raw', showindex=False)
-
-    # Insert \hline at the beginning and after each group of model names
-    latex_table_lines = latex_table.splitlines()
-    for i in range(len(latex_table_lines) - 2, 1, -1):
-        if not latex_table_lines[i].startswith('\\multirow') and latex_table_lines[i+1].startswith('\\multirow'):
-            latex_table_lines.insert(i+1, '\\hline')
-
-    latex_table = '\n'.join(latex_table_lines)
-
 
     table_env = f"""
     \\begin{{table*}}
[…]

### 2024-07-22 NN/latex.py
commit

@@ -32,7 +32,7 @@ def generate_latex_table(table, caption="table", label=""):
                     multirow_model_col[-(row_span+1)] = f"\\hline\n\\multirow{{{row_span+1}}}{{*}}{{{previous_model}}}"
                     row_spans.append(i)
                 row_span = 0
-                multirow_model_col.append(model)
+                multirow_model_col.append("\\hline\n" + model)
             previous_model = model
 
         if row_span > 0:

### 2024-07-22 NN/plots_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

### 2024-07-22 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/R2-99.14-Relu2HiddenLayer-HTCflow_rate1-using-conc_nano1-using-Kfluid1-using-heat_flux1-using-X_D1-using-flow_rate2-using-conc_nano2-using-Kfluid2-using-heat_flux2-using-X_D2.png}
    \caption{Prediction of HTC using flow_rate1 conc_nano1 Kfluid1 heat_flux1 X_D1 flow_rate2 conc_nano2 Kfluid2 heat_flux2 X_D2 with Relu2HiddenLayer - R-Squared: 0.94}
\end{figure}

### 2024-07-22 NN/models.py

@@ -1,0 +1,179 @@
+import torch
+import torch.nn as nn
+
+activations = [nn.ReLU(), nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
+class FFNN(nn.Module):
+    def __init__(self, input_size, hidden_sizes):
+        super().__init__()
+        self.hidden_layers = nn.ModuleList()
+        self.activations = activations if activations is not None else []
+
+        # Input to first hidden layer
+        self.hidden_layers.append(nn.Linear(input_size, hidden_sizes[0]))
+
+        # Intermediate hidden layers
+        for i in range(len(hidden_sizes) - 1):
+            self.hidden_layers.append(nn.Linear(hidden_sizes[i], hidden_sizes[i + 1]))
+
+        # Last hidden layer to output
+        self.hidden_layers.append(nn.Linear(hidden_sizes[-1], 1))
+
+    def forward(self, x):
+        for i, layer in enumerate(self.hidden_layers):
+            x = layer(x)
+            act = self.activations[-1]
+            if i < len(self.activations) and self.activations[i] is not None:
+                act = self.activations[i]
+            x = act(x)
+        return x
+
+##################### New Models
+class RBFN(nn.Module):
+    def __init__(self, input_size, hidden_sizes):
+        super(RBFN, self).__init__()
+        hidden_size = hidden_sizes[0]
+        self.hidden = nn.Linear(input_size, hidden_size)
+        self.output = nn.Linear(hidden_size, 1)
+        self.hidden_size = hidden_size
+
+        self.hidden_layers = nn.ModuleList()
+        self.hidden_layers.append(self.hidden)
+        self.hidden_layers.append(self.output)
+
+    def forward(self, x):
+        # Compute the distances from input to centers
+        distances = torch.cdist(x, self.hidden.weight, p=2)
+        # Apply Gaussian function
+        basis_functions = torch.exp(-distances**2)
+        output = self.output(basis_functions)
+        return output
+
+class GRNN(nn.Module):
+    def __init__(self, input_size, sigma=1.0):
+        super(GRNN, self).__init__()
+        self.pattern_layer = nn.Linear(input_size, input_size, bias=False)
+        self.sigma = sigma
+
+        self.hidden_layers = nn.ModuleList()
+        self.hidden_layers.append(self.pattern_layer)
+
+    def forward(self, x):
[…]

### 2024-07-22 NN/plot.py

@@ -1,0 +1,98 @@
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+from sklearn.metrics import r2_score
+
+def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
+    # Ensure the "plots" directory exists
+    os.makedirs('plots', exist_ok=True)
+
+    # LaTeX code storage
+    latex_code = ''
+
+    # Plot performance for each model and hidden size
+    for model_name in results_table['model'].unique():
+        # Filter the results for the current model
+        model_results = results_table[results_table['model'] == model_name]
+
+        # Get unique hidden sizes
+        unique_hidden_sizes = model_results['total hs'].unique()
+        
+        for hidden_size in unique_hidden_sizes:
+            # Filter results for the current hidden size
+            hs_results = model_results[model_results['total hs'] == hidden_size]
+
+            # Sort results by epochs
+            sorted_results = hs_results.sort_values(by='epochs')
+
+            # Extract epochs and R2 values
+            epochs = sorted_results['epochs'].to_numpy()
+            r2_values = sorted_results['R2'].to_numpy()
+
+            # Plot R2 vs. Number of Epochs for the current model and hidden size
+            plt.figure(figsize=(10, 6))
+            plt.plot(epochs, r2_values, 'o-', label=f'R2 (Hidden Size: {hidden_size})')
+            plt.title(f'{model_name} - R2 vs. Number of Epochs (Hidden Size: {hidden_size})')
+            plt.xlabel('Number of Epochs')
+            plt.ylabel('R2')
+            plt.grid(True)
+            plt.legend()
+            plot_filename = f'plots/{model_name}_R2_vs_Num_of_Epochs_HiddenSize_{hidden_size}.png'
+            plt.savefig(plot_filename)
+            plt.close()
+
+            # Add LaTeX code for this plot
+            plot_caption = f'{model_name} - R2 vs. Number of Epochs (Hidden Size: {hidden_size})'
+            latex_code += f"""
+\\begin{{figure}}[H]
+    \\centering
+    \\includegraphics[width=0.8\\textwidth]{{{plot_filename}}}
+    \\caption{{{plot_caption}}}
+\\end{{figure}}
+"""
+    # Save LaTeX code to a file
[…]

### 2024-07-22 NN/run.py

@@ -11,8 +11,10 @@ from sklearn.metrics import r2_score
 from tabulate import tabulate
 import os
 from latex import *
+from plot import *
+from models import *
 
-list_epochs = [200, 100, 50 , 20]
+list_epochs = [20, 50, 100 , 200]
 best_epochs = 100 
 
 exp_df = pd.DataFrame()
@@ -32,7 +34,6 @@ learning_rate = 0.05
 # The learnign rate used in ANN
 #hidden_size1 = 10
 hidden_size1 = 15
-
 hidden_size2 = 10
 
 # the number of neurons in hidden layers
@@ -42,186 +43,9 @@ hidden_size2 = 10
 #
 hidden_sizes = [15, 10, 3 ]
 # nn.ReLU(), nn.Tanh(), nn.Identity()
-activations = [nn.ReLU(), nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
 
 list_hidden_sizes = [[15, 10, 3], [8, 4], [15, 5]]
 normalization_type = "z_score"
-
-##################### New Models
-class RBFN(nn.Module):
-    def __init__(self, input_size, hidden_size):
-        super(RBFN, self).__init__()
-        hidden_size = hidden_sizes[0]
-        self.hidden = nn.Linear(input_size, hidden_size)
-        self.output = nn.Linear(hidden_size, 1)
-        self.hidden_size = hidden_size
-
-        self.hidden_layers = nn.ModuleList()
-        self.hidden_layers.append(self.hidden)
-        self.hidden_layers.append(self.output)
-
-    def forward(self, x):
-        # Compute the distances from input to centers
-        distances = torch.cdist(x, self.hidden.weight, p=2)
-        # Apply Gaussian function
-        basis_functions = torch.exp(-distances**2)
-        output = self.output(basis_functions)
-        return output
-
-class GRNN(nn.Module):
-    def __init__(self, input_size, sigma=1.0):
-        super(GRNN, self).__init__()
-        self.pattern_layer = nn.Linear(input_size, input_size, bias=False)
-        self.sigma = sigma
-
-        self.hidden_layers = nn.ModuleList()
-        self.hidden_layers.append(self.pattern_layer)
-
-    def forward(self, x):
-        # Compute the distances from input to pattern layer
-        distances = torch.cdist(x, self.pattern_layer.weight.t())
-        # Apply Gaussian function
-        basis_functions = torch.exp(-distances**2 / (2 * self.sigma**2))
[…]

### 2024-07-22 NN/plot.py
commit

@@ -58,7 +58,7 @@ def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
 
 def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots_preds_latex.tex', show_plot=False):
     # Ensure the "plots" directory exists
-    os.makedirs('plots', exist_ok=True)
+    os.makedirs('plots_preds', exist_ok=True)
     
     # Convert predictions and y_test to NumPy arrays
     y_test_np = y_test.to_numpy()
@@ -76,7 +76,7 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
     if show_plot is True:
         plt.show()
     # Save the image of plot in plots folder
-    image_path = os.path.join("plots", file_name)
+    image_path = os.path.join("plots_preds", file_name)
     fig.savefig(image_path, format="png")
     plt.close()
 

### 2024-07-22 NN/run.py

@@ -481,8 +481,8 @@ if answer != "0":
 
     # Show and save the plot for best results
     best_predictions = model_best_predictions[best_model_name] 
-    title = "Prediction of " + output + " using " + " ".join(inputs)+" with " + best_model_name 
-    file_name = f"R2-{best_r2:.2f}-" + best_model_name + "-" + output + "-using-".join(inputs) + ".png"
+    title = "Prediction of " + output + " with " + best_model_name 
+    file_name = f"R2-{best_r2:.2f}-" + best_model_name + "-" + output + ".png"
 
     print("\n\n")
     print("Plot was saved in plots folder")

### 2024-07-22 NN/plot.py
commit

@@ -91,7 +91,7 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
 """
 
     # Append LaTeX code to the existing file
-    with open(latex_filename, 'a') as f:
+    with open(latex_filename, 'w') as f:
         f.write(latex_code)
 
 

### 2024-08-08 NN/plots_latex.tex
commit

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/GRNN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
+    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
     \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
@@
 \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/RBFN_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}

### 2024-08-08 NN/models.py

@@ -1,7 +1,7 @@
 import torch
 import torch.nn as nn
 
-activations = [nn.ReLU(), nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
+activations = [nn.ReLU(), nn.ReLU(), nn.ReLU()]  # Specify activations for hidden layers
 class FFNN(nn.Module):
     def __init__(self, input_size, hidden_sizes):
         super().__init__()

### 2024-08-08 NN/run.py

@@ -28,8 +28,10 @@ model_seed = 123 # it is used for random_state of models
 data_seed = 123 # it is used for random_state of splitting data into source and train sets
 # changing it creates different source and train sets.
 # Since the number of data is low changing it can largely affect the results
-torch.manual_seed(model_seed)
-np.random.seed(model_seed)
+def set_model_seed(model_seed):
+    torch.manual_seed(model_seed)
+    np.random.seed(model_seed)
+
 learning_rate = 0.05
 # The learnign rate used in ANN
 #hidden_size1 = 10
@@ -60,7 +62,10 @@ def normalize(data, normalization_type):
 # Return predictions, MSE and R-Squared
 import torch.nn.init as init
 
-def fit_model(model_class, X_train, X_test, y_train, y_test, num_epochs, hidden_sizes, display_steps=False):
+def fit_model(model_class, X_train, X_test, y_train, y_test, 
+        num_epochs, hidden_sizes, display_steps=False):
+
+    set_model_seed(model_seed)
     scaler = StandardScaler()
     X_train = torch.tensor(scaler.fit_transform(X_train), dtype=torch.float32)
     X_test = torch.tensor(scaler.transform(X_test), dtype=torch.float32)

### 2024-08-08 NN/plots_preds_latex.tex
commit
zz

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/R2-99.14-Relu2HiddenLayer-HTCflow_rate1-using-conc_nano1-using-Kfluid1-using-heat_flux1-using-X_D1-using-flow_rate2-using-conc_nano2-using-Kfluid2-using-heat_flux2-using-X_D2.png}
-    \caption{Prediction of HTC using flow_rate1 conc_nano1 Kfluid1 heat_flux1 X_D1 flow_rate2 conc_nano2 Kfluid2 heat_flux2 X_D2 with Relu2HiddenLayer - R-Squared: 0.94}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-97.09-Tanh1HiddenLayer-Impedance module.png}
+    \caption{Prediction of Impedance module with Tanh1HiddenLayer - R-Squared: 0.93}
 \end{figure}

### 2024-08-08 NN/run.py

@@ -348,7 +348,20 @@ data = pd.read_csv(os.path.join('data','data.csv'))
 # Input features and output 
 #inputs = ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1','flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']
 inputs = ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1','flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']
-output = 'HTC'
+inputs = [
+    "SG Coating",
+    "Temp Alk Sol",
+    "NaOH Wt%",
+    "Dip Time Alk (min)",
+    "pH Sol",
+    "Hydro Time (h)",
+    "Dip Time Sol (s)",
+    "Clay Conc",
+    "Cure Time (min)",
+    "Cure Temp"
+]
+
+output = 'Impedance module'
 # Read data into X and y
 X = data[inputs]
 y = data[output] 
@@ -498,9 +511,9 @@ if answer != "0":
         plot_results(best_predictions, y_test, title, file_name, show_plot=False)
 
     # Save results of predicitons in a file named results.csv
-    results_df = pd.DataFrame(columns=["HTC", "predictions"])
-    results_df["HTC"] = y_test
-    results_df.rename(columns={"HTC": "actual"}, inplace=True)
+    results_df = pd.DataFrame(columns=[output, "predictions"])
+    results_df[output] = y_test
+    results_df.rename(columns={output: "actual"}, inplace=True)
     pred_list = [round(x,2) for x in best_predictions]
     results_df["predictions"] = pred_list # pd.Series(pred_list)
     results_df.to_csv("results.csv", index=False)

### 2024-08-08 NN/plots_preds_latex.tex
commit

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-97.09-Tanh1HiddenLayer-Impedance module.png}
-    \caption{Prediction of Impedance module with Tanh1HiddenLayer - R-Squared: 0.93}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
+    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
 \end{figure}

### 2024-08-08 NN/run.py

@@ -63,9 +63,9 @@ def normalize(data, normalization_type):
 import torch.nn.init as init
 
 def fit_model(model_class, X_train, X_test, y_train, y_test, 
-        num_epochs, hidden_sizes, display_steps=False):
+        num_epochs, hidden_sizes, display_steps=False, run=0):
 
-    set_model_seed(model_seed)
+    set_model_seed(model_seed + run)
     scaler = StandardScaler()
     X_train = torch.tensor(scaler.fit_transform(X_train), dtype=torch.float32)
     X_test = torch.tensor(scaler.transform(X_test), dtype=torch.float32)
@@ -320,7 +320,7 @@ def repeat_fit_model(model_class, num_repeats,
     for i in range(num_repeats):
         predictions, mse, r2, model = fit_model(model_class, 
                 X_train, X_test, y_train, y_test, num_epochs, hidden_sizes, 
-                display_steps=display_steps)
+                display_steps=display_steps, run=i)
         if r2 is None:
             continue
 

### 2024-08-08 NN/plots_latex.tex
zz
commit

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_12.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_28.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 28)}
+    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer_R2_vs_Num_of_Epochs_HiddenSize_20.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}

### 2024-08-08 NN/plot.py

@@ -4,6 +4,16 @@ import matplotlib.pyplot as plt
 import numpy as np
 from sklearn.metrics import r2_score
 
+def escape_latex_special_chars(text):
+    return (text.replace('_', '-')
+                .replace(' ', '-')
+                .replace('%', '\\%')
+                .replace('$', '\\$')
+                .replace('&', '\\&')
+                .replace('#', '\\#')
+                .replace('{', '\\{')
+                .replace('}', '\\}'))
+
 def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
     # Ensure the "plots" directory exists
     os.makedirs('plots', exist_ok=True)
@@ -38,7 +48,10 @@ def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
             plt.ylabel('R2')
             plt.grid(True)
             plt.legend()
-            plot_filename = f'plots/{model_name}_R2_vs_Num_of_Epochs_HiddenSize_{hidden_size}.png'
+            file_name = f'{model_name}_R2_vs_Num_of_Epochs_HiddenSize_{hidden_size}.png'
+            file_name = escape_latex_special_chars(file_name)
+            plot_filename = os.path.join('plots', file_name)
+                    
             plt.savefig(plot_filename)
             plt.close()
 
@@ -52,13 +65,15 @@ def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
 \\end{{figure}}
 """
     # Save LaTeX code to a file
-    with open(latex_filename, 'w') as f:
+    with open(latex_filename, 'w', encoding='utf-8') as f:
         f.write(latex_code)
+
 
 
 def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots_preds_latex.tex', show_plot=False):
     # Ensure the "plots" directory exists
     os.makedirs('plots_preds', exist_ok=True)
+    file_name = escape_latex_special_chars(file_name)
     
     # Convert predictions and y_test to NumPy arrays
     y_test_np = y_test.to_numpy()

### 2024-08-08 NN/run.py

@@ -62,8 +62,8 @@ def normalize(data, normalization_type):
 # Return predictions, MSE and R-Squared
 import torch.nn.init as init
 
-def fit_model(model_class, X_train, X_test, y_train, y_test, 
-        num_epochs, hidden_sizes, display_steps=False, run=0):
+def fit_model(model, X_train, X_test, y_train, y_test, 
+        num_epochs, display_steps=False, run=0):
 
     set_model_seed(model_seed + run)
     scaler = StandardScaler()
@@ -78,12 +78,6 @@ def fit_model(model_class, X_train, X_test, y_train, y_test,
     y_train_normalized = normalize(y_train, normalization_type)
     y_test_normalized = normalize(y_test, normalization_type)
 
-    input_size = X_train.shape[1]
-
-    if model_class == GRNN:
-        model = model_class(input_size)
-    else:
-        model = model_class(input_size, hidden_sizes)
 
     # Initialize weights
     def weights_init(m):
@@ -152,7 +146,12 @@ def weight_analysis(model_class, data, inputs, output, num_epochs):
     y = data[output]
     X_train, X_test, y_train, y_test = train_test_split(data[inputs], y, test_size=0.2, random_state=data_seed)
     input_size = X_train.shape[1]
-    _,_,r2, model = fit_model(model_class, X_train, X_test, y_train, y_test, num_epochs, hidden_sizes)
+
+    if model_class == GRNN:
+        model = model_class(input_size)
+    else:
+        model = model_class(input_size, hidden_sizes)
+    _,_,r2, model = fit_model(model, X_train, X_test, y_train, y_test, num_epochs)
     print("R2:", r2)
 
     weight_importances = {}
@@ -317,22 +316,30 @@ def repeat_fit_model(model_class, num_repeats,
     mse_list = []
     max_r2 = 0
     best_preds = None
-    for i in range(num_repeats):
-        predictions, mse, r2, model = fit_model(model_class, 
-                X_train, X_test, y_train, y_test, num_epochs, hidden_sizes, 
-                display_steps=display_steps, run=i)
-        if r2 is None:
-            continue
+    input_size = X_train.shape[1]
+    if model_class == GRNN:
+        model = model_class(input_size)
+    else:
+        model = model_class(input_size, hidden_sizes)
+    if len(hidden_sizes) > len(model.hidden_layers) - 1:
+        pass
+    else:
+        for i in range(num_repeats):
+            predictions, mse, r2, model = fit_model(model, 
[…]

### 2024-08-08 NN/plots_latex.tex
zz

@@
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
 \begin{figure}[H]
@@
     \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
     \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}

### 2024-08-08 NN/plots_preds_latex.tex
commit
zz

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
-    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-93.87-Tanh2HiddenLayer-Impedance-module.png}
+    \caption{Prediction of Impedance module with Tanh2HiddenLayer - R-Squared: 0.94}
 \end{figure}

### 2024-08-08 NN/tables/backward.tex
commit
zz

--- 2024-07-22 NN/tables/backward.tex
@@
-    \begin{table*}
+    \begin{table*}[h]
         \centering
-        \begin{tabular}{p{12cm}r}r}
-\hline
+        \begin{tabular}{lr}
 \hline
@@
 \hline
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2 & 84.97 \\
- conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.27 \\
- flow\_rate1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 71.9  \\
- flow\_rate1,conc\_nano1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2         & 73.44 \\
- flow\_rate1,conc\_nano1,Kfluid1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 74.25 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2,X\_D2       & 70.58 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,conc\_nano2,Kfluid2,heat\_flux2,X\_D2             & 81.67 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,Kfluid2,heat\_flux2,X\_D2             & 40.24 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,heat\_flux2,X\_D2         & 49.33 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,X\_D2             & 72.42 \\
- flow\_rate1,conc\_nano1,Kfluid1,heat\_flux1,X\_D1,flow\_rate2,conc\_nano2,Kfluid2,heat\_flux2       & 74.5  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 77.62 \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 51.9  \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 51.9  \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 51.9  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 74.59 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 46.26 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 69.37 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 62.26 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 34.36 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 64.92 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 62.82 \\
 \hline
 \end{tabular}
-\hline
         \caption{Results of Backward Feature Elimination}

### 2024-08-08 NN/tables/forward.tex
zz

--- 2024-07-22 NN/tables/forward.tex
@@
-    \begin{table*}
+    \begin{table*}[h]
         \centering
@@
 \hline
- X\_D1                                                         & 15.01 \\
- flow\_rate2                                                   & 34.3  \\
- conc\_nano2                                                   & 10.78 \\
- Kfluid2                                                       & 49.29 \\
- heat\_flux2                                                   & -8.26 \\
- flow\_rate1,Kfluid2                                           & 52.94 \\
- conc\_nano1,Kfluid2                                           & 50.8  \\
- Kfluid1,Kfluid2                                               & 47.57 \\
- heat\_flux1,Kfluid2                                           & 52.31 \\
- X\_D1,Kfluid2                                                 & 62.32 \\
- flow\_rate2,Kfluid2                                           & 29.14 \\
- conc\_nano2,Kfluid2                                           & 61.05 \\
- heat\_flux2,Kfluid2                                           & 66.61 \\
- X\_D2,Kfluid2                                                 & 53.44 \\
- flow\_rate1,Kfluid2,heat\_flux2                               & 60.58 \\
- conc\_nano1,Kfluid2,heat\_flux2                               & 61.96 \\
- Kfluid1,Kfluid2,heat\_flux2                                   & 66.64 \\
- heat\_flux1,Kfluid2,heat\_flux2                               & 42.41 \\
- X\_D1,Kfluid2,heat\_flux2                                     & 66.55 \\
- flow\_rate2,Kfluid2,heat\_flux2                               & 55.24 \\
- conc\_nano2,Kfluid2,heat\_flux2                               & 67.09 \\
- X\_D2,Kfluid2,heat\_flux2                                     & 68.58 \\
- flow\_rate1,Kfluid2,heat\_flux2,X\_D2                         & 90.12 \\
- conc\_nano1,Kfluid2,heat\_flux2,X\_D2                         & 78.64 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2                             & 88.23 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2                         & 49.47 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2                               & 79.9  \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2                         & -0.88 \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2                         & 63.17 \\
- conc\_nano1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 95.97 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                 & 76.54 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 60.12 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1                   & 80.67 \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.87 \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1             & 68.35 \\
- Kfluid1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1     & 80.62 \\
- heat\_flux1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 67.03 \\
- X\_D1,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1       & 85.73 \\
- flow\_rate2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 75.7  \\
- conc\_nano2,Kfluid2,heat\_flux2,X\_D2,flow\_rate1,conc\_nano1 & 78.99 \\
+ pH Sol                                                           &  14.56 \\
+ Hydro Time (h)                                                   &  26.4  \\
+ Dip Time Sol (s)                                                 &  11.24 \\
+ Clay Conc                                                        &  64.24 \\
+ Cure Time (min)                                                  &   0.1  \\
+ SG Coating, Clay Conc                                            &  64.93 \\
+ Temp Alk Sol, Clay Conc                                          &  64.93 \\
+ NaOH Wt\%, Clay Conc                                             &  64.93 \\
+ Dip Time Alk (min), Clay Conc                                    &  79.07 \\
+ pH Sol, Clay Conc                                                &  62.87 \\
+ Hydro Time (h), Clay Conc                                        & -15.61 \\
+ Dip Time Sol (s), Clay Conc                                      &  80.99 \\
+ Cure Time (min), Clay Conc                                       &  74.1  \\
+ Cure Temp, Clay Conc                                             &  66.68 \\
+ SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
+ Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
+ NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
+ Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
+ pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
+ Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
+ Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
+ Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
+ SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
+ Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
+ NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
+ pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
+ Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
+ Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
+ Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
 \hline

### 2024-08-08 NN/models.py

@@ -1,32 +1,6 @@
 import torch
 import torch.nn as nn
 
-activations = [nn.ReLU(), nn.ReLU(), nn.ReLU()]  # Specify activations for hidden layers
-class FFNN(nn.Module):
-    def __init__(self, input_size, hidden_sizes):
-        super().__init__()
-        self.hidden_layers = nn.ModuleList()
-        self.activations = activations if activations is not None else []
-
-        # Input to first hidden layer
-        self.hidden_layers.append(nn.Linear(input_size, hidden_sizes[0]))
-
-        # Intermediate hidden layers
-        for i in range(len(hidden_sizes) - 1):
-            self.hidden_layers.append(nn.Linear(hidden_sizes[i], hidden_sizes[i + 1]))
-
-        # Last hidden layer to output
-        self.hidden_layers.append(nn.Linear(hidden_sizes[-1], 1))
-
-    def forward(self, x):
-        for i, layer in enumerate(self.hidden_layers):
-            x = layer(x)
-            act = self.activations[-1]
-            if i < len(self.activations) and self.activations[i] is not None:
-                act = self.activations[i]
-            x = act(x)
-        return x
-
 ##################### New Models
 class RBFN(nn.Module):
     def __init__(self, input_size, hidden_sizes):
@@ -38,7 +12,7 @@ class RBFN(nn.Module):
 
         self.hidden_layers = nn.ModuleList()
         self.hidden_layers.append(self.hidden)
-        self.hidden_layers.append(self.output)
+        # self.hidden_layers.append(self.output)
 
     def forward(self, x):
         # Compute the distances from input to centers
@@ -113,7 +87,7 @@ class Linear1HiddenLayer(nn.Module):
 
         self.hidden_layers = nn.ModuleList()
         self.hidden_layers.append(self.input_to_hidden1)
-        self.hidden_layers.append(self.hidden1_to_output)
+        # self.hidden_layers.append(self.hidden1_to_output)
 
     def forward(self, x):
         # order of computation
@@ -138,13 +112,13 @@ class Linear2HiddenLayer(nn.Module):
         #  input(5 features)     hidden1           hidden2        output 
         #                       10 neurons         5 neurons
         self.input_to_hidden1 = nn.Linear(input_size, hidden_sizes[0])
-        self.hidden1_to_hidden2 = nn.Linear(hidden_sizes[0], hidden_sizes[1])
[…]

### 2024-08-08 NN/plot.py

@@ -50,7 +50,7 @@ def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
             plt.legend()
             file_name = f'{model_name}_R2_vs_Num_of_Epochs_HiddenSize_{hidden_size}.png'
             file_name = escape_latex_special_chars(file_name)
-            plot_filename = os.path.join('plots', file_name)
+            plot_filename = "plots/" + file_name # os.path.join('plots', file_name)
                     
             plt.savefig(plot_filename)
             plt.close()
@@ -83,6 +83,13 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
     fig, ax = plt.subplots(figsize=(10, 6))
     ax.scatter(y_test_np, y_test_np, color='green', label='Actual', alpha=0.5)
     ax.scatter(y_test_np, predictions_np, color='blue', label='Predicted', alpha=0.5)
+
+    # Plot the 45-degree line where x = y
+    min_val = min(np.min(y_test_np), np.min(predictions_np))
+    max_val = max(np.max(y_test_np), np.max(predictions_np))
+    ax.plot([min_val, max_val], [min_val, max_val], color='red', linestyle='--', label='45-Degree Line')
+
+
     ax.set_title(title + ' ' +  f' R-Squared:{r2:.2f}')
     ax.set_xlabel('Actual Values')
     ax.set_ylabel('Predicted Values')
@@ -91,7 +98,7 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
     if show_plot is True:
         plt.show()
     # Save the image of plot in plots folder
-    image_path = os.path.join("plots_preds", file_name)
+    image_path = "plots_preds/" + file_name # os.path.join("plots_preds", file_name)
     fig.savefig(image_path, format="png")
     plt.close()
 

### 2024-08-08 NN/run.py

@@ -46,7 +46,7 @@ hidden_size2 = 10
 hidden_sizes = [15, 10, 3 ]
 # nn.ReLU(), nn.Tanh(), nn.Identity()
 
-list_hidden_sizes = [[15, 10, 3], [8, 4], [15, 5]]
+list_hidden_sizes = [[10], [15, 10, 3], [8, 4], [15, 5]]
 normalization_type = "z_score"
 
 # Define the normalization function
@@ -166,7 +166,7 @@ def weight_analysis(model_class, data, inputs, output, num_epochs):
 
 def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs):
     y = data[output]
-    base_model_r2, _, _, _, _, _ = repeat_fit_model(model_class, 
+    base_model_r2, _, _, _, _, _, run = repeat_fit_model(model_class, 
             num_repeats, data[inputs], y, num_epochs, hidden_sizes)
     sensitivities = {}
     variances = []
@@ -178,7 +178,7 @@ def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs
         reduced_inputs = [f for f in inputs if f != input_feature]
         reduced_r2_list = []
         for _ in range(_num_repeats):
-            reduced_r2, _, _, _, _, _ = repeat_fit_model(model_class,
+            reduced_r2, _, _, _, _, _, _run = repeat_fit_model(model_class,
                     1, data[reduced_inputs], y, num_epochs, hidden_sizes)
             reduced_r2_list.append(reduced_r2)
         reduced_r2_mean = np.mean(reduced_r2_list)
@@ -199,7 +199,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
     X = data[inputs]
     # it uses num_repeats, num_epochs and model_seed as global variables
     # use _ for output of repeat_fit_model, which you don't need to use here
-    mean_r2, _, _, _, _,_ = repeat_fit_model(model_class,
+    mean_r2, _, _, _, _,_, _run = repeat_fit_model(model_class,
             num_repeats, X, y, num_epochs, hidden_sizes)
     best_r2 = mean_r2
     print("Using all features")
@@ -214,7 +214,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
             # Selet other features except for current feature
             features = [f for f in candidates if f != feature]
             X = data[features]
[…]

### 2024-08-08 NN/plots_latex.tex
zz

@@
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/GRNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
 \begin{figure}[H]
@@
     \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
     \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
@@
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/RBFN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}

### 2024-08-08 NN/plots_preds_latex.tex
zz

--- 2024-08-08 NN/plots_preds_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
-    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.23-TanhFFNN-Impedance-module.png}
+    \caption{Prediction of Impedance module with TanhFFNN - R-Squared: 0.94}
 \end{figure}

### 2024-08-08 NN/models.py

@@ -153,11 +153,20 @@ class FFNN(nn.Module):
             x = layer(x)
             act = self.activations[-1]
             if i < len(self.activations) and self.activations[i] is not None:
-                act = self.activations[i]
-            x = act(x)
+               act = self.activations[i]
+            if act is not None:
+               x = act(x)
         x = self.output_layer(x)
         return x
 
+class ReluFFNN(FFNN):
+      activations = [nn.ReLU()]  # Specify activations for hidden layers
+
+class LinearFFNN(FFNN):
+      activations = [None]  # Specify activations for hidden layers
+
+class TanhFFNN(FFNN):
+      activations = [nn.Tanh()]  # Specify activations for hidden layers
 
 # NonLinear Model with 1 hidden layer with Tanjant Hyperbolic function as nonlinear function
 # (Note it inherits from 2 hidden layer class above

### 2024-08-08 NN/run.py

@@ -380,7 +380,9 @@ models = [
             Tanh2HiddenLayer,
             Relu1HiddenLayer,
             Relu2HiddenLayer,
-           # FFNN,
+            ReluFFNN,
+            TanhFFNN,
+            LinearFFNN,
             RBFN,
             GRNN
          ]

### 2024-08-09 NN/tables/backward.tex
zz

--- 2024-07-22 NN/tables/backward.tex
@@
 \hline
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
- conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
- flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
- flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
- flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 89.74 \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 66.46 \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 66.46 \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 66.46 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 89.54 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         &  9.16 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 87.32 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 63.66 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 44.54 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 56.51 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 66.27 \\
 \hline

### 2024-08-09 NN/tables/forward.tex
zz

@@
 \hline
- pH Sol                                                           &  14.56 \\
- Hydro Time (h)                                                   &  26.4  \\
- Dip Time Sol (s)                                                 &  11.24 \\
- Clay Conc                                                        &  64.24 \\
- Cure Time (min)                                                  &   0.1  \\
- SG Coating, Clay Conc                                            &  64.93 \\
- Temp Alk Sol, Clay Conc                                          &  64.93 \\
- NaOH Wt\%, Clay Conc                                             &  64.93 \\
- Dip Time Alk (min), Clay Conc                                    &  79.07 \\
- pH Sol, Clay Conc                                                &  62.87 \\
- Hydro Time (h), Clay Conc                                        & -15.61 \\
- Dip Time Sol (s), Clay Conc                                      &  80.99 \\
- Cure Time (min), Clay Conc                                       &  74.1  \\
- Cure Temp, Clay Conc                                             &  66.68 \\
- SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
- Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
- NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
- Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
- pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
- Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
- Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
- Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
- SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
- Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
- NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
- pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
- Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
- Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
- Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
+ pH Sol                                                              &  14.96 \\
+ Hydro Time (h)                                                      &  33.65 \\
+ Dip Time Sol (s)                                                    &  11.2  \\
+ Clay Conc                                                           &  68.7  \\
+ Cure Time (min)                                                     & -15.76 \\
+ SG Coating, Clay Conc                                               &  63.12 \\
+ Temp Alk Sol, Clay Conc                                             &  63.12 \\
+ NaOH Wt\%, Clay Conc                                                &  63.12 \\
+ Dip Time Alk (min), Clay Conc                                       &  47.64 \\
+ pH Sol, Clay Conc                                                   &  77.65 \\
+ Hydro Time (h), Clay Conc                                           & -24.51 \\
+ Dip Time Sol (s), Clay Conc                                         &  68.92 \\
+ Cure Time (min), Clay Conc                                          &  67.83 \\
+ Cure Temp, Clay Conc                                                &  62.76 \\
+ SG Coating, Clay Conc, pH Sol                                       &  82    \\
+ Temp Alk Sol, Clay Conc, pH Sol                                     &  82    \\
+ NaOH Wt\%, Clay Conc, pH Sol                                        &  82    \\
+ Dip Time Alk (min), Clay Conc, pH Sol                               &  72.38 \\
+ Hydro Time (h), Clay Conc, pH Sol                                   &  32.74 \\
+ Dip Time Sol (s), Clay Conc, pH Sol                                 &  75.65 \\
+ Cure Time (min), Clay Conc, pH Sol                                  &  70.52 \\
+ Cure Temp, Clay Conc, pH Sol                                        &  71.84 \\
+ Temp Alk Sol, Clay Conc, pH Sol, SG Coating                         &  87.46 \\
+ NaOH Wt\%, Clay Conc, pH Sol, SG Coating                            &  87.46 \\
+ Dip Time Alk (min), Clay Conc, pH Sol, SG Coating                   &  80.65 \\
+ Hydro Time (h), Clay Conc, pH Sol, SG Coating                       &  43.08 \\
+ Dip Time Sol (s), Clay Conc, pH Sol, SG Coating                     &  90.78 \\
+ Cure Time (min), Clay Conc, pH Sol, SG Coating                      &  62.85 \\
+ Cure Temp, Clay Conc, pH Sol, SG Coating                            &  58.38 \\
+ Temp Alk Sol, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)       &  81.02 \\
+ NaOH Wt\%, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)          &  81.02 \\
+ Dip Time Alk (min), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s) &  89.34 \\
+ Hydro Time (h), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)     &  52.86 \\
+ Cure Time (min), Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)    &  73.46 \\
+ Cure Temp, Clay Conc, pH Sol, SG Coating, Dip Time Sol (s)          &  67.5  \\
 \hline

### 2024-08-09 NN/run.py

@@ -142,7 +142,7 @@ def fit_model(model, X_train, X_test, y_train, y_test,
 # Search about Backward Feature Elimination 
 # Sensitivity Analysis Functions
 
-def weight_analysis(model_class, data, inputs, output, num_epochs):
+def weight_analysis(model_class, data, inputs, output, num_epochs, hidden_sizes):
     y = data[output]
     X_train, X_test, y_train, y_test = train_test_split(data[inputs], y, test_size=0.2, random_state=data_seed)
     input_size = X_train.shape[1]
@@ -164,7 +164,7 @@ def weight_analysis(model_class, data, inputs, output, num_epochs):
     return weight_table
 
 
-def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs):
+def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs, hidden_sizes):
     y = data[output]
     base_model_r2, _, _, _, _, _, run = repeat_fit_model(model_class, 
             num_repeats, data[inputs], y, num_epochs, hidden_sizes)
@@ -191,7 +191,7 @@ def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs
     sensitivity_table['Variance'] = variances
     return sensitivity_table
 
-def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
+def backward_feature_elimination(model_class, data, inputs, output, num_epochs, hidden_sizes):
     y = data[output] 
     # Remove extra columns
     # data = data.drop([output, 'HTC_ANN1', 'HTC_ANN2'], axis=1).copy()
@@ -252,7 +252,7 @@ def backward_feature_elimination(model_class, data, inputs, output, num_epochs):
 # Finds the combinaiton of features that best predict y
 # This method add features one by one
 # Search about Forward Feature Selction
-def forward_feature_selection(model_class, data, inputs, output, num_epochs):
+def forward_feature_selection(model_class, data, inputs, output, num_epochs, hidden_sizes):
     y = data[output] 
     # Remove extra columns
     data = data.drop([output, 'm'], axis=1).copy()
@@ -356,16 +356,16 @@ data = pd.read_csv(os.path.join('data','data.csv'))
[…]

### 2024-08-09 NN/plots_latex.tex
add ffn

@@
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
 \begin{figure}[H]
@@
     \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}

### 2024-08-09 NN/plots_preds_latex.tex
zz
add ffn

--- 2024-08-08 NN/plots_preds_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
-    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.68-ReluTanhFFNN-Impedance-module.png}
+    \caption{Prediction of Impedance module with ReluTanhFFNN epochs:20 - R-Squared: 1.00}
 \end{figure}

### 2024-08-09 NN/tables/backward.tex
add ffn

--- 2024-07-22 NN/tables/backward.tex
@@
 \hline
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2 & 82.69 \\
- conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 62.45 \\
- flow\_rate1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 81.63 \\
- flow\_rate1, conc\_nano1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2          & 73.64 \\
- flow\_rate1, conc\_nano1, Kfluid1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 72.94 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2, X\_D2        & 67.45 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, conc\_nano2, Kfluid2, heat\_flux2, X\_D2              & 68.03 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, Kfluid2, heat\_flux2, X\_D2              & 76.57 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, heat\_flux2, X\_D2          & 38.28 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, X\_D2              & 69.39 \\
- flow\_rate1, conc\_nano1, Kfluid1, heat\_flux1, X\_D1, flow\_rate2, conc\_nano2, Kfluid2, heat\_flux2        & 81.61 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 95.29 \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 76.07 \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 76.07 \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 76.07 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 87.47 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 92.79 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 92.1  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 97.4  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 55.97 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 53.91 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 74.51 \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                               & 92.9  \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                                 & 92.9  \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                              & 92.9  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                                       & 95.57 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                           & 85.71 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                   & 97.5  \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Cure Time (min), Cure Temp                              & 43.32 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Temp                                    & 60.99 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min)                              & 81    \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                               & 90.77 \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                                 & 90.77 \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min), Cure Temp                                              & 90.77 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Clay Conc, Cure Time (min), Cure Temp                                                       & 94.85 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Clay Conc, Cure Time (min), Cure Temp                                           & 91.66 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Cure Time (min), Cure Temp                                              &  9.19 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Temp                                                    & 57.05 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Clay Conc, Cure Time (min)                                              & 73.86 \\
 \hline

### 2024-08-09 NN/latex.py

@@ -42,7 +42,10 @@ def generate_latex_table(table, caption="table", label=""):
 
     # Convert to LaTeX table using tabulate
     latex_table = tabulate(escaped_table, headers='keys', tablefmt='latex_raw', showindex=False)
-
+    # Replace the table environment with longtable
+    longtable_code = latex_table.replace('\\begin{tabular}', '\\begin{longtable}')
+    longtable_code = longtable_code.replace('\\end{tabular}', '\\end{longtable}')
+ 
     table_env = f"""
     \\begin{{table*}}[h]
         \\centering
@@ -52,7 +55,7 @@ def generate_latex_table(table, caption="table", label=""):
     \\end{{table*}}
     """
 
-    return table_env
+    return longtable_code
 
 # Example usage with a sample DataFrame
 results = [

### 2024-08-09 NN/models.py

@@ -168,6 +168,15 @@ class LinearFFNN(FFNN):
 class TanhFFNN(FFNN):
       activations = [nn.Tanh()]  # Specify activations for hidden layers
 
+class TanhReluFFNN(FFNN):
+      activations = [nn.Tanh(), nn.ReLU()]  # Specify activations for hidden layers
+
+class ReluTanhFFNN(FFNN):
+      activations = [nn.ReLU(), nn.Tanh()]  # Specify activations for hidden layers
+
+class TanhLinFFNN(FFNN):
+      activations = [nn.Tanh(), nn.Identity()]  # Specify activations for hidden layers
+
 # NonLinear Model with 1 hidden layer with Tanjant Hyperbolic function as nonlinear function
 # (Note it inherits from 2 hidden layer class above
 class Tanh1HiddenLayer(Linear1HiddenLayer):

### 2024-08-09 NN/run.py

@@ -380,6 +380,9 @@ models = [
             Tanh2HiddenLayer,
             Relu1HiddenLayer,
             Relu2HiddenLayer,
+            TanhReluFFNN,
+            TanhLinFFNN,
+            ReluTanhFFNN,
             ReluFFNN,
             TanhFFNN,
             LinearFFNN,
@@ -409,11 +412,14 @@ else:
 
 print("Selected Models:", [model_names[i] for i in selected_models])
 best_model_index = selected_models[0]
+max_model_index = best_model_index
 
 answer = input(f"Enter the number of epochs [{list_epochs}] (0 to skip training):")
 if answer != "0":
     if answer: 
-       list_epochs = [int(a) for a in answer.split()]
+       list_epochs = [int(a) for a in answer.split() if a.isnumeric()]
+    
+    print(list_epochs)
 
     answer = input(f"Enter the hidden sizes [{list_hidden_sizes}]:")
     if answer: 
@@ -434,6 +440,8 @@ if answer != "0":
     best_hidden_sizes = []
     best_r2 = -1000
     best_run = 0
+    max_epochs = -1
+    max_hidden_sizes = []
     best_epochs = -1
     results = []
     model_best_predictions = {}
@@ -456,6 +464,9 @@ if answer != "0":
                 if max_r2 > best_r2:
                     best_r2 = max_r2
                     model_best_predictions[model_name] = model_best_preds
+                    max_model_index = model_index
+                    max_epochs = num_epochs
+                    max_hidden_sizes = hidden_sizes
                     best_run = max_run
 
                 if mean_r2 > best_mean_r2:
@@ -499,15 +510,21 @@ if answer != "0":
     best_model = models[best_model_index]
     best_model_name = model_names[best_model_index]
     # Show results
+    max_model_name = model_names[max_model_index]
+
     print("============ Results for models =========================")
     print(results_table)
-    print("=========================================================")
-    print("Best R-Squred:", best_r2)
+    print("========================== Best Mean Model ===============================")
     print("Best Mean R-Squred:", best_mean_r2)
     print("Best model with better mean R-Squred:", best_model_name) 
     print("Best Hidden sizes:", best_hidden_sizes) 
     print("Best epochs:", best_epochs) 
-
+    print("=========================== Max Model ================================")
+    print("Best model with better max R-Squred:", max_model_name) 
[…]

### 2024-08-29 NN/run_nn.py
commit

@@ -1,0 +1,638 @@
+from matplotlib import pyplot as plt
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+import pandas as pd
+import numpy as np
+import torch.nn as nn
+from sklearn.metrics import r2_score
+from tabulate import tabulate
+import os
+from latex import *
+from plot import *
+from models import *
+
+list_epochs = [20, 50, 100 , 200]
+best_epochs = 100 
+
+exp_df = pd.DataFrame()
+
+num_repeats = 5
+# num_repeats shows the number of times to repeat the experiment to get its average values
+model_seed = 123 # it is used for random_state of models
+# changing model_seed generates different results for each run for each model
+# The same model_seed produces the same results in each run which is good for reporducability of experiments
+# Dont change it if you want to reproduce the same results
+data_seed = 123 # it is used for random_state of splitting data into source and train sets
+# changing it creates different source and train sets.
+# Since the number of data is low changing it can largely affect the results
+def set_model_seed(model_seed):
+    torch.manual_seed(model_seed)
+    np.random.seed(model_seed)
+
+learning_rate = 0.05
+# The learnign rate used in ANN
+#hidden_size1 = 10
+hidden_size1 = 15
+hidden_size2 = 10
+
+# the number of neurons in hidden layers
+
+# https://alexlenail.me/NN-SVG/
+# use the site above to draw the following network
+#
+hidden_sizes = [15, 10, 3 ]
+# nn.ReLU(), nn.Tanh(), nn.Identity()
+
+list_hidden_sizes = [[10], [15, 10, 3], [8, 4], [15, 5]]
+normalization_type = "z_score"
+
+# Define the normalization function
+def normalize(data, normalization_type):
+    if normalization_type == 'z_score':
+        return (data - data.mean()) / data.std()
+    elif normalization_type == 'minmax':
+        return (data - data.min()) / (data.max() - data.min())
+    else:
+        raise ValueError("Unsupported normalization type. Choose 'z_score' or 'minmax'.")
+
+# Function to apply model on data and generate predictions
+# Return predictions, MSE and R-Squared
+import torch.nn.init as init
+
+def fit_model(model, X_train, X_test, y_train, y_test, 
+        num_epochs, display_steps=False, run=0):
+
+    set_model_seed(model_seed + run)
+    scaler = StandardScaler()
[…]

### 2024-08-29 NN/plots_preds_latex.tex
commit

--- 2024-08-08 NN/plots_preds_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.23-TanhFFNN-Impedance-module.png}
-    \caption{Prediction of Impedance module with TanhFFNN - R-Squared: 0.94}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
+    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
 \end{figure}

### 2024-08-29 NN/tables/backward.tex
commit

--- 2024-08-08 NN/tables/backward.tex
@@
-    \begin{table*}[h]
-        \centering
-        \begin{tabular}{lr}
+\begin{longtable}{lr}
 \hline
@@
 \hline
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 77.62 \\
- Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 51.9  \\
- SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 51.9  \\
- SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 51.9  \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 74.59 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 46.26 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 69.37 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 62.26 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 34.36 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 64.92 \\
- SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 62.82 \\
+ time, flowrate, temp, init conc & 98.54 \\
+ flowrate, temp, init conc       &  0.66 \\
+ time, temp, init conc           & 94.34 \\
+ time, flowrate, init conc       & 98.02 \\
+ time, flowrate, temp            & 95.41 \\
 \hline
-\end{tabular}
-        \caption{Results of Backward Feature Elimination}
-        \label{backward}
-    \end{table*}
+\end{longtable}

### 2024-08-29 NN/tables/forward.tex
commit

--- 2024-08-08 NN/tables/forward.tex
@@
 \hline
- pH Sol                                                           &  14.56 \\
- Hydro Time (h)                                                   &  26.4  \\
- Dip Time Sol (s)                                                 &  11.24 \\
- Clay Conc                                                        &  64.24 \\
- Cure Time (min)                                                  &   0.1  \\
- SG Coating, Clay Conc                                            &  64.93 \\
- Temp Alk Sol, Clay Conc                                          &  64.93 \\
- NaOH Wt\%, Clay Conc                                             &  64.93 \\
- Dip Time Alk (min), Clay Conc                                    &  79.07 \\
- pH Sol, Clay Conc                                                &  62.87 \\
- Hydro Time (h), Clay Conc                                        & -15.61 \\
- Dip Time Sol (s), Clay Conc                                      &  80.99 \\
- Cure Time (min), Clay Conc                                       &  74.1  \\
- Cure Temp, Clay Conc                                             &  66.68 \\
- SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
- Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
- NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
- Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
- pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
- Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
- Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
- Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
- SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
- Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
- NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
- pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
- Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
- Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
- Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
+ time                            & 93.84 \\
+ flowrate                        & -0.79 \\
+ temp                            &  0.69 \\
+ init conc                       &  1.47 \\
+ flowrate, time                  & 95.32 \\
+ temp, time                      & 93.29 \\
+ init conc, time                 & 94.95 \\
+ temp, time, flowrate            & 95.21 \\
+ init conc, time, flowrate       & 97.84 \\
+ temp, time, flowrate, init conc & 97.39 \\
 \hline
-\end{tabular}
-        \caption{Results of Forward Feature Selection for different features}
-        \label{forward}
-    \end{table*}
+\end{longtable}

### 2024-08-29 NN/models.py

@@ -196,4 +196,32 @@ class Relu2HiddenLayer(Linear2HiddenLayer):
     activation1 = nn.ReLU()
     activation2 = nn.ReLU()
 
+# LSTM Model (Still included for comparison)
+class LSTM(nn.Module):
+    def __init__(self, input_size, hidden_sizes): # in ezafeh shod va ziri hazf shod
+    # def __init__(self, input_size, hidden_size, num_layers, output_size, transfer_function):
+        super(LSTM, self).__init__()
+        # be jaaye parametrhaye dadeh shode inha estefadeh shod
+        num_layers = 2
+        hidden_size = hidden_sizes[0]
+        output_size = hidden_sizes[1] if len(hidden_sizes) > 1 else 1
+        transfer_function = nn.ReLU
+
+        ###########  
+        self.lstm = nn.LSTM(input_size, hidden_size, num_layers, batch_first=True)
+        self.fc = nn.Linear(hidden_size, output_size)
+
+        # hame modelha in hidden_layers ro daran
+        self.hidden_layers = [self.lstm, self.fc]
+
+        self.hidden_size = hidden_size
+        self.num_layers = num_layers
+        self.transfer_function = transfer_function
+    
+    def forward(self, x):
+        h0 = torch.zeros(self.num_layers, x.size(0), self.hidden_size).to(x.device)
+        c0 = torch.zeros(self.num_layers, x.size(0), self.hidden_size).to(x.device)
+        out, _ = self.lstm(x, (h0, c0))
+        out = self.fc(out[:, -1, :])
+        return self.transfer_function(out)
 

### 2024-08-29 NN/run_nn.py

@@ -521,8 +521,9 @@ if answer != "0":
 
     # Show and save the plot for best results
     best_predictions = model_best_predictions[max_model_name] 
-    title = "Prediction of " + output + " with " + max_model_name + " epochs:" + str(max_epochs)
-    file_name = f"R2-{best_r2:.2f}-" + max_model_name + "-" + output + ".png"
+    _output = "-".join(output) if type(output) == list else str
+    title = "Prediction of " + _output + " with " + max_model_name + " epochs:" + str(max_epochs)
+    file_name = f"R2-{best_r2:.2f}-" + max_model_name + "-" + _output + ".png"
 
     print("\n\n")
     print("Plot was saved in plots folder")
@@ -533,9 +534,11 @@ if answer != "0":
         plot_results(best_predictions, y_test, title, file_name, show_plot=False)
 
     # Save results of predicitons in a file named results.csv
-    results_df = pd.DataFrame(columns=[output, "predictions"])
-    results_df[output] = y_test
-    results_df.rename(columns={output: "actual"}, inplace=True)
+    out_cols = output if type(output) == list else [output]
+    out_cols.append("predictions")
+    results_df = pd.DataFrame(columns=out_cols)
+    results_df["actual"] = y_test
+    # results_df.rename(columns={output: "actual"}, inplace=True)
     pred_list = [round(x,2) for x in best_predictions]
     results_df["predictions"] = pred_list # pd.Series(pred_list)
     results_df.to_csv("results.csv", index=False)
@@ -558,6 +561,8 @@ while True:
     print("q. Quit")
 
     answer = input("Enter the number of the method you want to run (or 'q' to quit): ").strip().lower()
+    if type(output) == list:
+        output= output[0] 
 
     if answer == '1':
         print("============================= Backward Feature Elimination =============")

### 2024-08-29 NN/lstm.py
commit

@@ -1,0 +1,42 @@
+import torch
+import numpy as np
+from models import LSTM
+
+# Example data (replace with your data)
+data = np.array([
+    # m, time, flowrate, temp, init conc, conc
+    [0, 1, 200, 30, 1000, 0],
+    [0, 2, 200, 30, 1000, 0],
+    [0, 3, 200, 30, 1000, 0],
+    # ... (more data)
+])
+
+# Set parameters
+sequence_length = 10  # Number of time steps in each sequence
+input_size = 4        # Number of features (excluding 'conc')
+batch_size = 32       # Number of sequences in each batch
+
+# Prepare input sequences and target values
+X = []
+y = []
+
+for i in range(len(data) - sequence_length):
+    X.append(data[i:i+sequence_length, 2:-1])  # Exclude 'm' and 'conc' columns
+    y.append(data[i+sequence_length-1, -1])    # Target is 'conc' at the end of the sequence
+
+X = np.array(X)
+y = np.array(y)
+
+# Convert to PyTorch tensors
+X_tensor = torch.tensor(X, dtype=torch.float32)
+y_tensor = torch.tensor(y, dtype=torch.float32)
+
+# Reshape X_tensor to match LSTM input: (batch_size, sequence_length, input_size)
+X_tensor = X_tensor.view(-1, sequence_length, input_size)
+
+# Feed data to the LSTM model
+model = LSTM(input_size, [50, 1])  # Example model
+output = model(X_tensor)
+
+print(output)
+

### 2024-08-29 NN/lstm.py
commit

@@ -1,42 +1,144 @@
 import torch
+import torch.nn as nn
+import pandas as pd
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.metrics import mean_squared_error, r2_score
 import numpy as np
-from models import LSTM
 
-# Example data (replace with your data)
-data = np.array([
-    # m, time, flowrate, temp, init conc, conc
-    [0, 1, 200, 30, 1000, 0],
-    [0, 2, 200, 30, 1000, 0],
-    [0, 3, 200, 30, 1000, 0],
-    # ... (more data)
-])
+# Load and normalize the training data
+train_data = pd.read_csv('data/data_nn.csv')
+scaler = MinMaxScaler()
+train_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.fit_transform(train_data[['flowrate', 'temp', 'init conc', 'conc']])
 
-# Set parameters
-sequence_length = 10  # Number of time steps in each sequence
-input_size = 4        # Number of features (excluding 'conc')
-batch_size = 32       # Number of sequences in each batch
 
-# Prepare input sequences and target values
-X = []
-y = []
+def pad_sequences_to_longest(sequences, padding_value=0.0):
+    max_time_steps = max(seq.shape[0] for seq in sequences)  # Maximum length across sequences
+    max_features = max(seq.shape[1] for seq in sequences)    # Maximum number of features
 
-for i in range(len(data) - sequence_length):
-    X.append(data[i:i+sequence_length, 2:-1])  # Exclude 'm' and 'conc' columns
-    y.append(data[i+sequence_length-1, -1])    # Target is 'conc' at the end of the sequence
+    padded_sequences = []
+    for seq in sequences:
+        # Calculate the amount of padding needed for both dimensions
+        pad_time = max_time_steps - seq.shape[0]
+        pad_features = max_features - seq.shape[1]
 
-X = np.array(X)
-y = np.array(y)
+        # Pad the sequence with padding_value
+        padded_seq = np.pad(seq, ((0, pad_time), (0, pad_features)),
+                            mode='constant', constant_values=padding_value)
+        padded_sequences.append(padded_seq)
 
-# Convert to PyTorch tensors
-X_tensor = torch.tensor(X, dtype=torch.float32)
-y_tensor = torch.tensor(y, dtype=torch.float32)
+    return padded_sequences
 
[…]

### 2024-08-29 NN/models.py

@@ -217,11 +217,17 @@ class LSTM(nn.Module):
         self.hidden_size = hidden_size
         self.num_layers = num_layers
         self.transfer_function = transfer_function
-    
+
     def forward(self, x):
+        print("Input shape:", x.shape)
         h0 = torch.zeros(self.num_layers, x.size(0), self.hidden_size).to(x.device)
         c0 = torch.zeros(self.num_layers, x.size(0), self.hidden_size).to(x.device)
-        out, _ = self.lstm(x, (h0, c0))
-        out = self.fc(out[:, -1, :])
-        return self.transfer_function(out)
 
+        out, _ = self.lstm(x, (h0, c0))
+        print("LSTM output shape:", out.shape)
+        out = self.fc(out[:, -1, :])
+        print("FC output shape:", out.shape)
+
+        if out.numel() > 0:
+            out = self.transfer_function()(out)
+        return out

### 2024-08-29 NN/lstm.py
commit

@@ -4,6 +4,7 @@ import pandas as pd
 from sklearn.preprocessing import MinMaxScaler
 from sklearn.metrics import mean_squared_error, r2_score
 import numpy as np
+import torch.nn.utils.rnn as rnn_utils
 
 # Load and normalize the training data
 train_data = pd.read_csv('data/data_nn.csv')
@@ -33,6 +34,7 @@ def create_sequences(data):
     xs, ys = [], []
     start_idx = 0
     seq_length = 0
+    actual_lengths = []
     idx = 0
     while start_idx + seq_length < len(data):
         if data.iloc[start_idx + seq_length, 0] < seq_length and idx > 0:
@@ -55,21 +57,21 @@ def create_sequences(data):
         start_idx += 1  # Move to the next time step
         idx += 1
 
+    actual_lengths = [len(x) for x in xs]
     pxs = pad_sequences_to_longest(xs)
     X_tensor = torch.tensor(pxs, dtype=torch.float32)
     y_tensor = torch.tensor(ys, dtype=torch.float32).unsqueeze(-1)
-    return  X_tensor, y_tensor
+    return  X_tensor, y_tensor, actual_lengths
 
 features = train_data[['time','flowrate', 'temp', 'init conc', 'conc']]
-X, y = create_sequences(features)
+X, y, train_lengths = create_sequences(features)
 
 # Load and prepare the test data
 test_data = pd.read_csv('data/data_test_nn.csv')
 test_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.transform(test_data[['flowrate', 'temp', 'init conc', 'conc']])
 
-X_test_new, y_test_new = create_sequences(test_data[['time','flowrate', 'temp', 'init conc', 'conc']])
+X_test_new, y_test_new, test_lengths = create_sequences(test_data[['time','flowrate', 'temp', 'init conc', 'conc']])
 
-# Define the LSTM model
 class LSTMModel(nn.Module):
     def __init__(self, input_dim, hidden_dim, num_layers, output_dim):
         super(LSTMModel, self).__init__()
@@ -77,26 +79,42 @@ class LSTMModel(nn.Module):
         self.num_layers = num_layers
         self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers, batch_first=True)
         self.fc = nn.Linear(hidden_dim, output_dim)
-        self.transform_func = nn.Identity()  
+        self.transform_func = nn.Tanh()
 
-    def forward(self, x):
[…]

### 2024-08-29 NN/lstm.py
commit

@@ -114,7 +114,7 @@ hidden_dim = 48
 num_layers = 2
 output_dim = 1
 num_epochs = 1000
-learning_rate = 0.001
+learning_rate = 0.0001
 
 model = LSTMModel(input_dim, hidden_dim, num_layers, output_dim).to(device)
 loss_fn = nn.MSELoss()

### 2024-08-29 NN/lstm.py
commit

@@ -110,11 +110,11 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 
 # Initialize model, loss function, optimizer
 input_dim = 4  # time, flowrate, temp, init conc
-hidden_dim = 48
-num_layers = 2
+hidden_dim = 100
+num_layers = 1
 output_dim = 1
 num_epochs = 1000
-learning_rate = 0.0001
+learning_rate = 0.006
 
 model = LSTMModel(input_dim, hidden_dim, num_layers, output_dim).to(device)
 loss_fn = nn.MSELoss()

### 2024-09-01 NN/lstm3.py
commit

@@ -1,0 +1,172 @@
+import torch
+import torch.nn as nn
+import pandas as pd
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.metrics import mean_squared_error, r2_score
+import numpy as np
+import torch.nn.utils.rnn as rnn_utils
+import sys
+
+# Load and normalize the training data
+train_data = pd.read_csv('data/data_nn.csv')
+scaler = MinMaxScaler()
+train_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.fit_transform(train_data[['flowrate', 'temp', 'init conc', 'conc']])
+
+def pad_sequences_to_longest(sequences, padding_value=0.0):
+    max_time_steps = max(seq.shape[0] for seq in sequences)  # Maximum length across sequences
+    max_features = max(seq.shape[1] for seq in sequences)    # Maximum number of features
+
+    padded_sequences = []
+    for seq in sequences:
+        pad_time = max_time_steps - seq.shape[0]
+        pad_features = max_features - seq.shape[1]
+
+        padded_seq = np.pad(seq, ((0, pad_time), (0, pad_features)),
+                            mode='constant', constant_values=padding_value)
+        padded_sequences.append(padded_seq)
+
+    # Convert the list of padded sequences to a NumPy array and then to a tensor
+    padded_sequences = np.array(padded_sequences)
+    return padded_sequences
+
+def create_sequences(data):
+    xs, ys = [], []
+    start_idx = 0
+    seq_length = 0
+    idx = 0
+    while start_idx + seq_length < len(data):
+        if data.iloc[start_idx + seq_length, 0] < seq_length and idx > 0:
+            start_idx += seq_length
+            seq_length = 0
+            idx = start_idx
+            continue
+
+        if data.iloc[idx, -1] == 0:
+            seq_length += 1
+            idx += 1
+            continue
+
+        x = data.iloc[start_idx:(start_idx + seq_length), :-1].values
+        y = data.iloc[start_idx:(start_idx + seq_length), -1].values
+        xs.append(x)
+        ys.append(y)
+
+        start_idx += 1
+        idx += 1
+
+    actual_lengths = [len(x) for x in xs]
+    pxs = pad_sequences_to_longest(xs)
+    X_tensor = torch.tensor(pxs, dtype=torch.float32)
+    ys_padded = pad_sequences_to_longest([y[:, np.newaxis] for y in ys])
[…]

### 2024-09-01 NN/lstm.py
commit

@@ -72,32 +72,33 @@ test_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.transform(test_dat
 
 X_test_new, y_test_new, test_lengths = create_sequences(test_data[['time','flowrate', 'temp', 'init conc', 'conc']])
 
-class LSTMModel(nn.Module):
-    def __init__(self, input_dim, hidden_dim, num_layers, output_dim):
-        super(LSTMModel, self).__init__()
+model_seed = 123 # it is used for random_state of models
+data_seed = 123 # it is used for random_state of splitting data into source and train sets
+def set_model_seed(model_seed):
+    torch.manual_seed(model_seed)
+    np.random.seed(model_seed)
+
+class ImprovedLSTMModel(nn.Module):
+    def __init__(self, input_dim, hidden_dim, num_layers, output_dim, dropout=0.2):
+        super(ImprovedLSTMModel, self).__init__()
         self.hidden_dim = hidden_dim
         self.num_layers = num_layers
-        self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers, batch_first=True)
-        self.fc = nn.Linear(hidden_dim, output_dim)
+        self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers, 
+                            batch_first=True, 
+                            dropout=dropout, bidirectional=True)
+        self.fc = nn.Linear(hidden_dim * 2, output_dim)  # Multiply by 2 for bidirectional
         self.transform_func = nn.Tanh()
 
     def forward(self, x, lengths):
-        # Initialize hidden state and cell state
-        h0 = torch.zeros(self.num_layers, x.size(0), self.hidden_dim).to(x.device)
-        c0 = torch.zeros(self.num_layers, x.size(0), self.hidden_dim).to(x.device)
+        h0 = torch.zeros(self.num_layers * 2, x.size(0), self.hidden_dim).to(x.device)  # Multiply by 2 for bidirectional
+        c0 = torch.zeros(self.num_layers * 2, x.size(0), self.hidden_dim).to(x.device)
 
-        # Pack the padded sequence
         packed_input = rnn_utils.pack_padded_sequence(x, lengths, batch_first=True, enforce_sorted=False)
-
-        # Pass the packed sequence to the LSTM
         packed_output, (hn, cn) = self.lstm(packed_input, (h0, c0))
-
-        # Unpack the sequence
[…]

### 2024-09-01 NN/lstm3.py

@@ -83,7 +83,8 @@ class ImprovedLSTMModel(nn.Module):
         self.hidden_dim = hidden_dim
         self.num_layers = num_layers
         self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers, 
-                            batch_first=True, dropout=dropout, bidirectional=True)
+                            batch_first=True, 
+                            dropout=dropout, bidirectional=True)
         self.fc = nn.Linear(hidden_dim * 2, output_dim)  # Multiply by 2 for bidirectional
         self.transform_func = nn.Tanh()
 
@@ -141,27 +142,32 @@ def train_and_evaluate_model(n_runs=5):
             predictions = model(X_test_new_device, test_lengths).cpu().numpy()
             y_test_new_np = y_test_new.cpu().numpy()
 
-            # Ensure lengths match
-            min_len = min(predictions.shape[0], y_test_new_np.shape[0])
-            print("min len:", min_len)
-            predictions = predictions[:min_len]
-            y_test_new_np = y_test_new_np[:min_len]
+            # Trim predictions and actual values to match their original lengths
+            trimmed_predictions = []
+            trimmed_actuals = []
+            
+            for i, length in enumerate(test_lengths):
+                trimmed_predictions.append(predictions[i][:length])
+                trimmed_actuals.append(y_test_new_np[i][:length])
 
-            test_loss = mean_squared_error(y_test_new_np.flatten(), predictions.flatten())
-            r2 = r2_score(y_test_new_np.flatten(), predictions.flatten())
+            trimmed_predictions = np.concatenate(trimmed_predictions)
+            trimmed_actuals = np.concatenate(trimmed_actuals)
+
+            test_loss = mean_squared_error(trimmed_actuals.flatten(), trimmed_predictions.flatten())
+            r2 = r2_score(trimmed_actuals.flatten(), trimmed_predictions.flatten())
 
             r2_scores.append(r2)
             print(f'Run {run + 1}/{n_runs}, Test Loss: {test_loss:.4f}, R² Score: {r2:.4f}')
             
             # Save the predictions and actual values to CSV
             results = pd.DataFrame({
-                'Actual': y_test_new.flatten(),
-                'Predicted': predictions.flatten()
+                'Actual': trimmed_actuals.flatten(),
+                'Predicted': trimmed_predictions.flatten()
             })
             results.to_csv(f'test_predictions_output_run_{run+1}.csv', index=False)
[…]

### 2024-09-01 NN/lstm.py
commit

@@ -78,16 +78,16 @@ def set_model_seed(model_seed):
     torch.manual_seed(model_seed)
     np.random.seed(model_seed)
 
-class ImprovedLSTMModel(nn.Module):
+class LSTM(nn.Module):
     def __init__(self, input_dim, hidden_dim, num_layers, output_dim, dropout=0.2):
-        super(ImprovedLSTMModel, self).__init__()
+        super(LSTM, self).__init__()
         self.hidden_dim = hidden_dim
         self.num_layers = num_layers
-        self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers, 
-                            batch_first=True, 
+        self.lstm = nn.LSTM(input_dim, hidden_dim, num_layers,
+                            batch_first=True,
                             dropout=dropout, bidirectional=True)
         self.fc = nn.Linear(hidden_dim * 2, output_dim)  # Multiply by 2 for bidirectional
-        self.transform_func = nn.Tanh()
+        self.transform_func = nn.RReLU()
 
     def forward(self, x, lengths):
         h0 = torch.zeros(self.num_layers * 2, x.size(0), self.hidden_dim).to(x.device)  # Multiply by 2 for bidirectional
@@ -97,14 +97,16 @@ class ImprovedLSTMModel(nn.Module):
         packed_output, (hn, cn) = self.lstm(packed_input, (h0, c0))
         output, _ = rnn_utils.pad_packed_sequence(packed_output, batch_first=True)
 
-        out = self.fc(output)
+        # Convert lengths to a tensor
+        lengths = torch.tensor(lengths).to(x.device)
+
+        # Use the output at the last time step for each sequence
+        idx = torch.arange(0, output.size(0)).to(x.device)
+        last_output = output[idx, lengths - 1]
+
+        out = self.fc(last_output)
         out = self.transform_func(out)
         return out
-
-# Example usage:
-# Assume `inputs` is your padded input tensor and `lengths` is the list of sequence lengths.
-# model = LSTMModel(input_dim, hidden_dim, num_layers, output_dim)
-# outputs = model(inputs, lengths)
 
 # Set device
 device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
@@ -113,57 +115,70 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 
 input_dim = 4
 hidden_dim = 100
-num_layers = 3  # Increased number of layers
[…]

### 2024-09-01 NN/lstm.py
commit

@@ -105,6 +105,7 @@ class LSTM(nn.Module):
         last_output = output[idx, lengths - 1]
 
         out = self.fc(last_output)
+        out = nn.Tanh(out)
         out = self.transform_func(out)
         return out
 

### 2024-09-01 NN/lstm.py
commit

@@ -105,7 +105,6 @@ class LSTM(nn.Module):
         last_output = output[idx, lengths - 1]
 
         out = self.fc(last_output)
-        out = nn.Tanh(out)
         out = self.transform_func(out)
         return out
 
@@ -115,11 +114,11 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 # Initialize model, loss function, optimizer
 
 input_dim = 4
-hidden_dim = 100
+hidden_dim = 120
 num_layers = 2  # Increased number of layers
 output_dim = 1
-num_epochs = 80
-learning_rate = 0.001  # Adjusted learning rate
+num_epochs = 100
+learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model
 # Function to train and evaluate the model multiple times
@@ -127,6 +126,7 @@ def train_and_evaluate_model(n_runs=5):
     r2_scores = []
     
     for run in range(n_runs):
+        set_model_seed(model_seed + run)
         model = LSTM(input_dim, hidden_dim, num_layers, output_dim, dropout=0.2).to(device)
         loss_fn = nn.MSELoss()
         optimizer = torch.optim.Adam(model.parameters(), lr=learning_rate)
@@ -134,7 +134,6 @@ def train_and_evaluate_model(n_runs=5):
         # Move data to the device
         X_train, y_train = X.to(device), y.to(device)
  
-        set_model_seed(model_seed + run)
         print("========================== Run:", run+1)
         for epoch in range(num_epochs):
             model.train()

### 2024-09-01 NN/lstm.py
commit

@@ -117,7 +117,7 @@ input_dim = 4
 hidden_dim = 120
 num_layers = 2  # Increased number of layers
 output_dim = 1
-num_epochs = 100
+num_epochs = 50
 learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model

### 2024-09-01 NN/lstm.py
commit

@@ -117,7 +117,7 @@ input_dim = 4
 hidden_dim = 120
 num_layers = 2  # Increased number of layers
 output_dim = 1
-num_epochs = 50
+num_epochs = 100
 learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model

### 2024-09-02 NN/lstm.py
commit

@@ -11,7 +11,6 @@ train_data = pd.read_csv('data/data_nn.csv')
 scaler = MinMaxScaler()
 train_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.fit_transform(train_data[['flowrate', 'temp', 'init conc', 'conc']])
 
-
 def pad_sequences_to_longest(sequences, padding_value=0.0):
     max_time_steps = max(seq.shape[0] for seq in sequences)  # Maximum length across sequences
     max_features = max(seq.shape[1] for seq in sequences)    # Maximum number of features
@@ -87,13 +86,14 @@ class LSTM(nn.Module):
                             batch_first=True,
                             dropout=dropout, bidirectional=True)
         self.fc = nn.Linear(hidden_dim * 2, output_dim)  # Multiply by 2 for bidirectional
-        self.transform_func = nn.RReLU()
+        self.transform_func = nn.LeakyReLU(negative_slope=0.01) 
 
     def forward(self, x, lengths):
         h0 = torch.zeros(self.num_layers * 2, x.size(0), self.hidden_dim).to(x.device)  # Multiply by 2 for bidirectional
         c0 = torch.zeros(self.num_layers * 2, x.size(0), self.hidden_dim).to(x.device)
 
-        packed_input = rnn_utils.pack_padded_sequence(x, lengths, batch_first=True, enforce_sorted=False)
+        packed_input = rnn_utils.pack_padded_sequence(x, lengths, 
+                batch_first=True, enforce_sorted=False)
         packed_output, (hn, cn) = self.lstm(packed_input, (h0, c0))
         output, _ = rnn_utils.pad_packed_sequence(packed_output, batch_first=True)
 
@@ -117,7 +117,7 @@ input_dim = 4
 hidden_dim = 120
 num_layers = 2  # Increased number of layers
 output_dim = 1
-num_epochs = 100
+num_epochs = 150
 learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model
@@ -141,6 +141,7 @@ def train_and_evaluate_model(n_runs=5):
             loss = loss_fn(output, y_train)
             optimizer.zero_grad()
             loss.backward()
+            # torch.nn.utils.clip_grad_norm_(model.parameters(), max_norm=1.0)
             optimizer.step()
             if (epoch + 1) % 10 == 0:
                 print(f'Epoch [{epoch + 1}/{num_epochs}], Loss: {loss.item():.4f}')

### 2024-09-02 NN/lstm.py
commit

@@ -11,6 +11,7 @@ train_data = pd.read_csv('data/data_nn.csv')
 scaler = MinMaxScaler()
 train_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.fit_transform(train_data[['flowrate', 'temp', 'init conc', 'conc']])
 
+
 def pad_sequences_to_longest(sequences, padding_value=0.0):
     max_time_steps = max(seq.shape[0] for seq in sequences)  # Maximum length across sequences
     max_features = max(seq.shape[1] for seq in sequences)    # Maximum number of features
@@ -29,6 +30,7 @@ def pad_sequences_to_longest(sequences, padding_value=0.0):
     return padded_sequences
 
 
+MAX_SEQ_LEN=0
 def create_sequences(data):
     xs, ys = [], []
     start_idx = 0
@@ -42,12 +44,14 @@ def create_sequences(data):
             idx = start_idx
             continue
 
-        if data.iloc[idx, -1] == 0:
+        if idx < len(data) and data.iloc[idx, -1] == 0:
             seq_length += 1
             idx += 1
             continue
 
         # Create the sequence
+        if MAX_SEQ_LEN > 0:
+            seq_length = min(seq_length, MAX_SEQ_LEN)
         x = data.iloc[start_idx:(start_idx + seq_length), :-1].values
         y = data.iloc[start_idx + seq_length, -1]
         xs.append(x)
@@ -117,7 +121,7 @@ input_dim = 4
 hidden_dim = 120
 num_layers = 2  # Increased number of layers
 output_dim = 1
-num_epochs = 150
+num_epochs = 100
 learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model

### 2024-09-02 NN/lstm.py
commit

@@ -30,8 +30,7 @@ def pad_sequences_to_longest(sequences, padding_value=0.0):
     return padded_sequences
 
 
-MAX_SEQ_LEN=0
-def create_sequences(data):
+def create_sequences(data, max_seq_len=0):
     xs, ys = [], []
     start_idx = 0
     seq_length = 0
@@ -50,8 +49,8 @@ def create_sequences(data):
             continue
 
         # Create the sequence
-        if MAX_SEQ_LEN > 0:
-            seq_length = min(seq_length, MAX_SEQ_LEN)
+        if max_seq_len > 0:
+            seq_length = min(seq_length, max_seq_len)
         x = data.iloc[start_idx:(start_idx + seq_length), :-1].values
         y = data.iloc[start_idx + seq_length, -1]
         xs.append(x)
@@ -66,14 +65,12 @@ def create_sequences(data):
     y_tensor = torch.tensor(ys, dtype=torch.float32).unsqueeze(-1)
     return  X_tensor, y_tensor, actual_lengths
 
-features = train_data[['time','flowrate', 'temp', 'init conc', 'conc']]
-X, y, train_lengths = create_sequences(features)
+features = ['time','flowrate', 'temp', 'init conc', 'conc']
 
 # Load and prepare the test data
 test_data = pd.read_csv('data/data_test_nn.csv')
 test_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.transform(test_data[['flowrate', 'temp', 'init conc', 'conc']])
 
-X_test_new, y_test_new, test_lengths = create_sequences(test_data[['time','flowrate', 'temp', 'init conc', 'conc']])
 
 model_seed = 123 # it is used for random_state of models
 data_seed = 123 # it is used for random_state of splitting data into source and train sets
@@ -126,8 +123,10 @@ learning_rate = 0.0005  # Adjusted learning rate
 
 # Train the model
 # Function to train and evaluate the model multiple times
-def train_and_evaluate_model(n_runs=5):
+def train_and_evaluate_model(n_runs=5, max_seq_len=0, step_print=True):
     r2_scores = []
+    X, y, train_lengths = create_sequences(train_data[features], max_seq_len)
+    X_test_new, y_test_new, test_lengths = create_sequences(test_data[features], max_seq_len)
     
     for run in range(n_runs):
         set_model_seed(model_seed + run)
@@ -138,7 +137,7 @@ def train_and_evaluate_model(n_runs=5):
         # Move data to the device
[…]

### 2024-09-02 NN/lstm.py
commit

@@ -184,7 +184,18 @@ def train_and_evaluate_model(n_runs=5, max_seq_len=0, step_print=True):
 
     print(f'\nBest R² Score: {best_r2:.4f}')
     print(f'Mean R² Score over {n_runs} runs: {mean_r2:.4f}')
+    return mean_r2
 
+r2_list = []
 for seq in range(15):
-    train_and_evaluate_model(n_runs=1, max_seq_len=seq, step_print=False)
+    r2 = train_and_evaluate_model(n_runs=1, max_seq_len=seq, step_print=False)
+    r2_list.append(r2)
+
+results = pd.DataFrame({
+    'run': range(len(r2_list)),
+    'r2': r2_list 
+})
+results.to_csv(f'run.csv', index=False)
+print(results)
+print(f'Results saved to run.csv')
 

### 2024-09-02 NN/lstm.py
commit

@@ -5,7 +5,7 @@ from sklearn.preprocessing import MinMaxScaler
 from sklearn.metrics import mean_squared_error, r2_score
 import numpy as np
 import torch.nn.utils.rnn as rnn_utils
-
+import os 
 # Load and normalize the training data
 train_data = pd.read_csv('data/data_nn.csv')
 scaler = MinMaxScaler()
@@ -116,28 +116,37 @@ device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 
 input_dim = 4
 hidden_dim = 120
-num_layers = 2  # Increased number of layers
+num_layers = 3  # Increased number of layers
 output_dim = 1
 num_epochs = 100
 learning_rate = 0.0005  # Adjusted learning rate
+dropout= 0.2
 
 # Train the model
 # Function to train and evaluate the model multiple times
-def train_and_evaluate_model(n_runs=5, max_seq_len=0, step_print=True):
+def train_and_evaluate_model(n_runs=5, 
+        max_seq_len=0, 
+        step_print=True,
+        hidden_dim=hidden_dim,
+        num_layers=num_layers,
+        dropout=dropout,
+        num_epochs=num_epochs):
     r2_scores = []
+    max_r2 = 0
     X, y, train_lengths = create_sequences(train_data[features], max_seq_len)
     X_test_new, y_test_new, test_lengths = create_sequences(test_data[features], max_seq_len)
     
     for run in range(n_runs):
         set_model_seed(model_seed + run)
-        model = LSTM(input_dim, hidden_dim, num_layers, output_dim, dropout=0.2).to(device)
+        model = LSTM(input_dim, hidden_dim, 
+                num_layers, output_dim, dropout=dropout).to(device)
         loss_fn = nn.MSELoss()
         optimizer = torch.optim.Adam(model.parameters(), lr=learning_rate)
 
         # Move data to the device
         X_train, y_train = X.to(device), y.to(device)
  
-        print("========================== Run:", run+1, " Max seq len:", max_seq_len)
+        print("========================== Run:", run+1)
         for epoch in range(num_epochs):
             model.train()
             output = model(X_train, train_lengths)
@@ -166,16 +175,23 @@ def train_and_evaluate_model(n_runs=5, max_seq_len=0, step_print=True):
             print(f'R² Score: {r2:.4f}')
 
             # Prepare DataFrame for output
-            results = pd.DataFrame({
-                'Actual': y_test_new_np.flatten(),
-                'Predicted': predictions.flatten()
-            })
[…]

### 2024-09-02 NN/lstm.py
commit

@@ -204,7 +204,7 @@ def train_and_evaluate_model(n_runs=5,
 
 r2_list = []
 var_list = []
-for var in [200,150,130,120]: # range(14): # [10,20,30]:
+for var in  [""]:# [200,150,130,120]: # range(14): # [10,20,30]:
     print("-"*50, "var:", var)
     r2 = train_and_evaluate_model(n_runs=2, 
             max_seq_len=0, 
@@ -212,7 +212,7 @@ for var in [200,150,130,120]: # range(14): # [10,20,30]:
             num_epochs=num_epochs,
             num_layers=num_layers,
             dropout=dropout,
-            hidden_dim=var)
+            hidden_dim=hidden_dim)
     r2_list.append(r2)
     var_list.append(var)
 

### 2024-09-02 NN/lstm.py
commit

@@ -4,6 +4,8 @@ import pandas as pd
 from sklearn.preprocessing import MinMaxScaler
 from sklearn.metrics import mean_squared_error, r2_score
 import numpy as np
+from latex import *
+from plot import *
 import torch.nn.utils.rnn as rnn_utils
 import os 
 # Load and normalize the training data
@@ -189,6 +191,13 @@ def train_and_evaluate_model(n_runs=5,
                 # Save the results to a CSV file
                 results.to_csv(os.path.join('lstm_preds',f'predictions_{r2:.4f}.csv'), 
                         index=False)
+                title = f"R2-{r2:.4f}"
+                file_name = os.path.join("lstm_plots", title + ".png")
+
+                print("\n\n")
+                print("Plot was saved in lstm_plots folder")
+                plot_results(predictions, y_test_new.cpu(), title, 
+                        file_name, show_plot=False)
                 if step_print:
                     print(results)
                 print(f'Test results for run {run+1} saved to lstm_preds/predictions_{r2}.csv')

### 2024-09-02 NN/plot.py

@@ -76,7 +76,7 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
     file_name = escape_latex_special_chars(file_name)
     
     # Convert predictions and y_test to NumPy arrays
-    y_test_np = y_test.to_numpy()
+    y_test_np = y_test.numpy()
     # Calculate R-squared
     r2 = r2_score(y_test_np, predictions_np)
 

### 2024-09-02 NN/plots_latex.tex
commit

--- 2024-08-08 NN/plots_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
 \end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
-\end{figure}

### 2024-09-02 NN/plots_preds_latex.tex
commit

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
-    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.30-TanhReluFFNN-Impedance-module.png}
+    \caption{Prediction of Impedance module with TanhReluFFNN epochs:200 - R-Squared: 0.99}
 \end{figure}

### 2024-09-02 NN/plot.py

@@ -68,6 +68,18 @@ def plot_model_performance(results_table, latex_filename='plots_latex.tex'):
     with open(latex_filename, 'w', encoding='utf-8') as f:
         f.write(latex_code)
 
+import torch
+import pandas as pd
+
+def to_numpy_array(data):
+    if isinstance(data, torch.Tensor):
+        # Convert tensor to NumPy array
+        return data.cpu().detach().numpy()
+    elif isinstance(data, pd.Series):
+        # Convert pandas Series to NumPy array
+        return data.to_numpy()
+    else:
+        raise TypeError("Unsupported type. Only Tensor or Series objects are supported.")
 
 
 def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots_preds_latex.tex', show_plot=False):
@@ -76,7 +88,7 @@ def plot_results(predictions_np, y_test, title, file_name, latex_filename='plots
     file_name = escape_latex_special_chars(file_name)
     
     # Convert predictions and y_test to NumPy arrays
-    y_test_np = y_test.numpy()
+    y_test_np = to_numpy_array(y_test)
     # Calculate R-squared
     r2 = r2_score(y_test_np, predictions_np)
 

### 2024-09-02 NN/lstm.py
commit

@@ -11,7 +11,14 @@ import os
 # Load and normalize the training data
 train_data = pd.read_csv('data/data_nn.csv')
 scaler = MinMaxScaler()
-train_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.fit_transform(train_data[['flowrate', 'temp', 'init conc', 'conc']])
+# Define input and output features explicitly
+features = ['time','flowrate', 'temp', 'init conc', 'conc']
+scale_features = ['flowrate', 'temp', 'init conc', 'conc']
+input_features = ['time', 'flowrate', 'temp', 'init conc']
+output_feature = 'conc'
+
+
+train_data[scale_features] = scaler.fit_transform(train_data[scale_features])
 
 
 def pad_sequences_to_longest(sequences, padding_value=0.0):
@@ -45,7 +52,7 @@ def create_sequences(data, max_seq_len=0):
             idx = start_idx
             continue
 
-        if idx < len(data) and data.iloc[idx, -1] == 0:
+        if idx < len(data) and data.iloc[idx][output_feature] == 0:
             seq_length += 1
             idx += 1
             continue
@@ -53,8 +60,8 @@ def create_sequences(data, max_seq_len=0):
         # Create the sequence
         if max_seq_len > 0:
             seq_length = min(seq_length, max_seq_len)
-        x = data.iloc[start_idx:(start_idx + seq_length), :-1].values
-        y = data.iloc[start_idx + seq_length, -1]
+        x = data.iloc[start_idx:(start_idx + seq_length)][input_features].values
+        y = data.iloc[start_idx + seq_length][output_feature]
         xs.append(x)
         ys.append(y)
 
@@ -67,12 +74,10 @@ def create_sequences(data, max_seq_len=0):
     y_tensor = torch.tensor(ys, dtype=torch.float32).unsqueeze(-1)
     return  X_tensor, y_tensor, actual_lengths
 
-features = ['time','flowrate', 'temp', 'init conc', 'conc']
 
 # Load and prepare the test data
 test_data = pd.read_csv('data/data_test_nn.csv')
-test_data[['flowrate', 'temp', 'init conc', 'conc']] = scaler.transform(test_data[['flowrate', 'temp', 'init conc', 'conc']])
-
+test_data[scale_features] = scaler.transform(test_data[scale_features])
 
 model_seed = 123 # it is used for random_state of models
 data_seed = 123 # it is used for random_state of splitting data into source and train sets

### 2024-09-02 NN/run.py

@@ -21,13 +21,13 @@ exp_df = pd.DataFrame()
 
 num_repeats = 5
 # num_repeats shows the number of times to repeat the experiment to get its average values
-model_seed = 123 # it is used for random_state of models
 # changing model_seed generates different results for each run for each model
 # The same model_seed produces the same results in each run which is good for reporducability of experiments
 # Dont change it if you want to reproduce the same results
 data_seed = 123 # it is used for random_state of splitting data into source and train sets
 # changing it creates different source and train sets.
 # Since the number of data is low changing it can largely affect the results
+model_seed = 123 # it is used for random_state of models
 def set_model_seed(model_seed):
     torch.manual_seed(model_seed)
     np.random.seed(model_seed)

### 2024-09-02 NN/lstm.py
commit

@@ -42,24 +42,22 @@ def pad_sequences_to_longest(sequences, padding_value=0.0):
 def create_sequences(data, max_seq_len=0):
     xs, ys = [], []
     start_idx = 0
-    seq_length = 0
+    seq_length = max_seq_len
     actual_lengths = []
     idx = 0
     while start_idx + seq_length < len(data):
         if data.iloc[start_idx + seq_length, 0] < seq_length and idx > 0:
             start_idx += seq_length # Skip rest 
-            seq_length = 0
+            seq_length = max_seq_len
             idx = start_idx
             continue
 
-        if idx < len(data) and data.iloc[idx][output_feature] == 0:
-            seq_length += 1
-            idx += 1
-            continue
+        if max_seq_len <= 0:
+            if idx < len(data) and data.iloc[idx][output_feature] == 0:
+                seq_length += 1
+                idx += 1
+                continue
 
-        # Create the sequence
-        if max_seq_len > 0:
-            seq_length = min(seq_length, max_seq_len)
         x = data.iloc[start_idx:(start_idx + seq_length)][input_features].values
         y = data.iloc[start_idx + seq_length][output_feature]
         xs.append(x)
@@ -194,7 +192,7 @@ def train_and_evaluate_model(n_runs=5,
                 })
 
                 # Save the results to a CSV file
-                results.to_csv(os.path.join('lstm_preds',f'predictions_{r2:.4f}.csv'), 
+                results.to_csv(os.path.join('lstm_preds',f'{max_seq_len}-pr-{r2:.4f}.csv'), 
                         index=False)
                 title = f"R2-{r2:.4f}"
                 file_name = os.path.join("lstm_plots", title + ".png")
@@ -205,7 +203,7 @@ def train_and_evaluate_model(n_runs=5,
                         file_name, show_plot=False)
                 if step_print:
                     print(results)
-                print(f'Test results for run {run+1} saved to lstm_preds/predictions_{r2}.csv')
+                print(f'Test results for run {run+1} saved')
             print(f'Test Loss: {test_loss:.4f}')
             print(f'R² Score: {r2:.4f}')
 
@@ -218,10 +216,10 @@ def train_and_evaluate_model(n_runs=5,
 
 r2_list = []
 var_list = []
-for var in  [""]:# [200,150,130,120]: # range(14): # [10,20,30]:
+for var in  range(15): #[""]:# [200,150,130,120]: # range(14): # [10,20,30]:
[…]

### 2024-09-02 NN/lstm.py
commit

@@ -42,21 +42,23 @@ def pad_sequences_to_longest(sequences, padding_value=0.0):
 def create_sequences(data, max_seq_len=0):
     xs, ys = [], []
     start_idx = 0
-    seq_length = max_seq_len
+    seq_length = 0
     actual_lengths = []
     idx = 0
     while start_idx + seq_length < len(data):
         if data.iloc[start_idx + seq_length, 0] < seq_length and idx > 0:
             start_idx += seq_length # Skip rest 
-            seq_length = max_seq_len
+            seq_length = 0 
             idx = start_idx
             continue
 
-        if max_seq_len <= 0:
-            if idx < len(data) and data.iloc[idx][output_feature] == 0:
-                seq_length += 1
-                idx += 1
-                continue
+        if idx < len(data) and data.iloc[idx][output_feature] == 0:
+            seq_length += 1
+            idx += 1
+            continue
+
+        if max_seq_len > 0:
+            seq_length = min(seq_length, max_seq_len)
 
         x = data.iloc[start_idx:(start_idx + seq_length)][input_features].values
         y = data.iloc[start_idx + seq_length][output_feature]

### 2024-11-22 NN/plots_latex.tex
commit

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+    \includegraphics[width=0.8\textwidth]{plots/Sig1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Sig1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}

### 2024-11-22 NN/plots_preds_latex.tex
commit

--- 2024-08-29 NN/plots_preds_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
-    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-69.68-Sig1HiddenLayer-Temp.png}
+    \caption{Prediction of Temp with Sig1HiddenLayer epochs:200 - R-Squared: 0.70}
 \end{figure}

### 2024-11-22 NN/tables/backward.tex
commit

@@
 \hline
- time, flowrate, temp, init conc & 98.54 \\
- flowrate, temp, init conc       &  0.66 \\
- time, temp, init conc           & 94.34 \\
- time, flowrate, init conc       & 98.02 \\
- time, flowrate, temp            & 95.41 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m & 82.44 \\
+ Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m             & 76.24 \\
+ SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m               & 76.24 \\
+ SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m            & 76.24 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m                     & 78.37 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m         & 75.31 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp, m                 & 77.73 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp, m                   & 76.41 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp, m            & 74.24 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp, m                  & 75.63 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), m            & 65.18 \\
+ SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp    & 61.71 \\
 \hline

### 2024-11-22 NN/tables/forward.tex
commit

@@
 \hline
- time                            & 93.84 \\
- flowrate                        & -0.79 \\
- temp                            &  0.69 \\
- init conc                       &  1.47 \\
- flowrate, time                  & 95.32 \\
- temp, time                      & 93.29 \\
- init conc, time                 & 94.95 \\
- temp, time, flowrate            & 95.21 \\
- init conc, time, flowrate       & 97.84 \\
- temp, time, flowrate, init conc & 97.39 \\
+ Pco2             &  -4.32 \\
+ Pch4             & -14.19 \\
+ rate             &  57.65 \\
+ Pco2, rate       &  60.73 \\
+ Pch4, rate       &  53.38 \\
+ Pch4, rate, Pco2 &  41.27 \\
 \hline

### 2024-11-22 NN/models.py

@@ -196,6 +196,12 @@ class Relu2HiddenLayer(Linear2HiddenLayer):
     activation1 = nn.ReLU()
     activation2 = nn.ReLU()
 
+class Sig1HiddenLayer(Linear1HiddenLayer):
+    activation1 = nn.Sigmoid()
+
+class Sig2HiddenLayer(Linear2HiddenLayer):
+    activation1 = nn.Sigmoid()
+    activation2 = nn.Sigmoid()
 # LSTM Model (Still included for comparison)
 class LSTM(nn.Module):
     def __init__(self, input_size, hidden_sizes): # in ezafeh shod va ziri hazf shod

### 2024-11-22 NN/read_data.py

@@ -1,0 +1,235 @@
+import os
+import pandas as pd
+from sklearn.model_selection import train_test_split
+
+def read_data():
+    """
+    Reads training and testing data from user-specified files or performs an automatic split.
+    Saves the processed data into a folder for future use.
+    
+    Returns:
+        X_train, X_test, y_train, y_test: Training and test datasets.
+    """
+    # Create prep_data folder if not exists
+    prep_data_dir = "prep_data"
+    os.makedirs(prep_data_dir, exist_ok=True)
+    
+    # Ask for train file
+    train_file = input("Enter the path to the training file: ").strip()
+    if not train_file or not os.path.isfile(train_file):
+        raise FileNotFoundError("The specified training file does not exist.")
+    
+    # Load train data
+    train_data = pd.read_csv(train_file)
+    
+    # Ask for test file
+    test_file = input("Enter the path to the testing file (leave empty for auto split): ").strip()
+    if test_file and os.path.isfile(test_file):
+        test_data = pd.read_csv(test_file)
+        auto_split = False
+    else:
+        test_data = None
+        auto_split = True
+    
+    # Handle feature selection
+    output_feature, input_features = select_features(train_data)
+    
+    if auto_split:
+        # Automatic split
+        data_seed = 123
+        seed = input(f"Enter data seed for splitting ({data_seed}):").strip()
+        if seed: data_seed = int(seed)
+        y = train_data[output_feature]
+        X = train_data[input_features]
+        X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=data_seed)
+    else:
+        # Separate files for train and test
+        y_train = train_data[output_feature]
+        X_train = train_data[input_features]
+        y_test = test_data[output_feature]
+        X_test = test_data[input_features]
+    
+    # Save processed parts to the folder
+    save_data(prep_data_dir, X_train, X_test, y_train, y_test)
+    
+    return X_train, X_test, y_train, y_test
+
+
+def select_features(data):
+    """
+    Guides the user to select output and input features from the dataset interactively.
+    
+    Args:
+        data (DataFrame): The dataset to select features from.
+    
+    Returns:
+        output_feature (str): The selected output feature.
+        input_features (list): The selected input features.
+    """
+    # List columns and ask for output feature
[…]

### 2024-11-22 NN/run.py

@@ -2,7 +2,6 @@ from matplotlib import pyplot as plt
 import torch
 import torch.nn as nn
 import torch.optim as optim
-from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import StandardScaler
 import pandas as pd
 import numpy as np
@@ -13,6 +12,9 @@ import os
 from latex import *
 from plot import *
 from models import *
+from read_data import read_prep_data
+import inspect
+import models
 
 list_epochs = [20, 50, 100 , 200]
 best_epochs = 100 
@@ -143,8 +145,7 @@ def fit_model(model, X_train, X_test, y_train, y_test,
 # Sensitivity Analysis Functions
 
 def weight_analysis(model_class, data, inputs, output, num_epochs, hidden_sizes):
-    y = data[output]
-    X_train, X_test, y_train, y_test = train_test_split(data[inputs], y, test_size=0.2, random_state=data_seed)
+    X_train, X_test, y_train, y_test = read_prep_data(inputs)
     input_size = X_train.shape[1]
 
     if model_class == GRNN:
@@ -165,9 +166,8 @@ def weight_analysis(model_class, data, inputs, output, num_epochs, hidden_sizes)
 
 
 def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs, hidden_sizes):
-    y = data[output]
     base_model_r2, _, _, _, _, _, run = repeat_fit_model(model_class, 
-            num_repeats, data[inputs], y, num_epochs, hidden_sizes)
+            num_repeats, num_epochs, hidden_sizes)
     sensitivities = {}
     variances = []
     _num_repeats = input("Number of repeat [10]:")
@@ -179,7 +179,7 @@ def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs
         reduced_r2_list = []
         for _ in range(_num_repeats):
             reduced_r2, _, _, _, _, _, _run = repeat_fit_model(model_class,
-                    1, data[reduced_inputs], y, num_epochs, hidden_sizes)
+                    1, num_epochs, hidden_sizes, features= reduced_inputs)
             reduced_r2_list.append(reduced_r2)
         reduced_r2_mean = np.mean(reduced_r2_list)
         sensitivity = base_model_r2 - reduced_r2_mean
@@ -192,15 +192,8 @@ def jackknife_sensitivity_analysis(model_class, data, inputs, output, num_epochs
     return sensitivity_table
 
[…]

### 2024-11-22 NN/plots_latex.tex
commit

--- 2024-08-09 NN/plots_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+    \includegraphics[width=0.8\textwidth]{plots/Sig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Sig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/Sig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Sig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{TanhReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
     \includegraphics[width=0.8\textwidth]{plots/TanhReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/Sig1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Sig1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+    \includegraphics[width=0.8\textwidth]{plots/SigReLU2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{SigReLU2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/SigReLU2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{SigReLU2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReLUSig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{ReLUSig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReLUSig2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{ReLUSig2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/TanhLinFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{TanhLinFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/ReluTanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{ReluTanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
 \end{figure}
@@
     \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{plots/FFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
+    \caption{FFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Tanh2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{Linear2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
-    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
-    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
-    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{plots/Tanh1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
-    \caption{Tanh1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
     \includegraphics[width=0.8\textwidth]{plots/RBFN-R2-vs-Num-of-Epochs-HiddenSize-10.png}

### 2024-11-22 NN/plots_preds_latex.tex
commit

--- 2024-08-29 NN/plots_preds_latex.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
-    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
+    \includegraphics[width=0.8\textwidth]{plots_preds/R2-91.77-Tanh2HiddenLayer-rate.png}
+    \caption{Prediction of rate with Tanh2HiddenLayer epochs:50 - R-Squared: 0.92}
 \end{figure}

### 2024-11-22 NN/models.py

@@ -43,31 +43,31 @@ class GRNN(nn.Module):
         return output
 
 
-class CNN(nn.Module):
-    def __init__(self, input_channels, num_classes):
-        super(CNN, self).__init__()
-        self.layer1 = nn.Sequential(
-            nn.Conv2d(input_channels, 16, kernel_size=5, stride=1, padding=2),
-            nn.BatchNorm2d(16),
-            nn.ReLU(),
-            nn.MaxPool2d(kernel_size=2, stride=2))
-        self.layer2 = nn.Sequential(
-            nn.Conv2d(16, 32, kernel_size=5, stride=1, padding=2),
-            nn.BatchNorm2d(32),
-            nn.ReLU(),
-            nn.MaxPool2d(kernel_size=2, stride=2))
-        self.fc1 = nn.Linear(32 * 7 * 7, 1000)
-        self.fc2 = nn.Linear(1000, num_classes)
-
-    def forward(self, x):
-        out = self.layer1(x)
-        out = self.layer2(out)
-        out = out.view(out.size(0), -1)
-        out = self.fc1(out)
-        out = self.fc2(out)
-        return out
-
-
+#class CNN(nn.Module):
+#    def __init__(self, input_channels, num_classes):
+#        super(CNN, self).__init__()
+#        self.layer1 = nn.Sequential(
+#            nn.Conv2d(input_channels, 16, kernel_size=5, stride=1, padding=2),
+#            nn.BatchNorm2d(16),
+#            nn.ReLU(),
+#            nn.MaxPool2d(kernel_size=2, stride=2))
+#        self.layer2 = nn.Sequential(
+#            nn.Conv2d(16, 32, kernel_size=5, stride=1, padding=2),
+#            nn.BatchNorm2d(32),
+#            nn.ReLU(),
+#            nn.MaxPool2d(kernel_size=2, stride=2))
+#        self.fc1 = nn.Linear(32 * 7 * 7, 1000)
+#        self.fc2 = nn.Linear(1000, num_classes)
+#
+#    def forward(self, x):
+#        out = self.layer1(x)
+#        out = self.layer2(out)
+#        out = out.view(out.size(0), -1)
+#        out = self.fc1(out)
+#        out = self.fc2(out)
+#        return out
+#
+#
 class Linear1HiddenLayer(nn.Module):
     activation1 = None
     def __init__(self, input_size, hidden_sizes):
[…]
